---
title: "flavonoid project"
output: html_notebook
---

# set up pathway and library packages
```{r}
setwd("C:/Users/14999/OneDrive - King's College London/genetics/")
getwd()


# Load necessary libraries
library(psych)
library(dplyr)
library(tidyr)
library(stringr)
library(survival)
library(tableone)
library(knitr)
library(ggplot2)
library(lubridate)
library(ggsurvfit)
library(forestmodel)
library(lubridate)
library(mediation)
```


# load needed dataset and select participants 
```{r}
# Load and filter psoriasis demographic data
participants.recall.over1 <- read.csv("24hr/participants.recall.over1.csv")
demographics <- read.csv("basic files/demographics.csv")
filtered.incidence <- read.csv("basic files/4907incidence.csv")
p.demographics <- demographics %>%
  filter(Participant.ID %in% filtered.incidence$Participant.ID) %>%
  mutate(group = "psoriasis") # Filter participants based on incidence data

# Load and filter non-psoriasis demographic data
demographics <- read.csv("basic files/demographics.csv")
filtered.control <- read.csv("basic files/484895control.csv")
n.demographics <- demographics %>%
  filter(Participant.ID %in% filtered.control$Participant.ID) %>%
  mutate(group = "non-psoriasis") # Filter participants based on control data

# Combine psoriasis and non-psoriasis demographic data
demographics <- rbind(p.demographics, n.demographics) %>%
  filter(Participant.ID %in% participants.recall.over1$Participant.ID)
demographics <- demographics[order(demographics$Participant.ID), ]

# Load non-psoriasis 24-hour recall data
p.24h.foods.average <- read.csv("24hr/average 24hrecall individual foods.csv") %>% 
  filter(Participant.ID %in% demographics$Participant.ID)
p.24h.foods.average[, 1:201][is.na(p.24h.foods.average[, 1:201])] <- 0

p.24h.foods.average <- p.24h.foods.average[, c(2:201, 1)]

p.24h.foods.average <- cbind(
  p.24h.foods.average[, 1:139], 
  Vegetarian.alternatives.intake = 0, 
  p.24h.foods.average[, 140:ncol(p.24h.foods.average)]
)

# Display the updated column names to confirm the change
names(p.24h.foods.average)

participants.recall.over2 <- read.csv("24hr/participants.recall.over2.csv")

# load polyphenol and flavonoid checkout dataset
flavonoid.checkout <- read.csv("C:/Users/14999/OneDrive - King's College London/Documents/flavonoid UKbiobank.csv")
new.row <- as.data.frame(matrix(0, ncol = ncol(flavonoid.checkout)))
colnames(new.row) <- colnames(flavonoid.checkout)
flavonoid.checkout <- rbind(new.row, flavonoid.checkout)
# Convert columns 9 to 223 in flavonoid.checkout to numeric
flavonoid.checkout[881, 95] <- 0
flavonoid.checkout[, 9:223] <- lapply(flavonoid.checkout[, 9:223], function(x) as.numeric(as.character(x)))

```

All data is based on the dataset which merges Phenol Explorer and USDA database (Ana's group, Yifan work).


# contribution
```{r}
library(dplyr)
library(purrr)
library(tidyr)
library(tibble)
library(stringr)

# --- 1) 定义五大类所含原始列名（按你的命名；不存在的列会被自动忽略） ---
cols <- list(
  anthocyanins = c("Cyanidin","Delphinidin","Malvidin","Pelargonidin","Petunidin","Peonidin"),
  flavanones   = c("Eriodictyol","Hesperetin","Naringenin"),
  flavonols    = c("Quercetin","Kaempferol","Myricetin","Isorhamnetin",
                   "Jaceidin","Patuletin","Spinacetin"),  # 你备注里想纳入的三个
  flavones     = c("Luteolin","Apigenin"),
  flavan3ols   = c("X....Catechin","X....Epicatechin","X....Epigallocatechin","X....Gallocatechin",
                   "X....Catechin.3.O.gallate","X....Epicatechin.3.O.gallate",
                   "X....Epigallocatechin.3.O.gallate","X....Gallocatechin.3.O.gallate",
                   "Theaflavin","Thearubigins","X02.mers","X03.mers","X04.06.mers",
                   "X07.10.mers","Polymers...10.mers.")
)

# --- 2) 工具：把单体列 -> 汇总成“每行食物 × 五大类”的 mg/100g 矩阵 ---
#     输入：flavonoid.checkout（行为食物，列为单体/聚合物）
#     输出：flavonoid_subclass_per100g（行为食物，列：5 大类）
build_subclass_matrix <- function(df, cols_map) {
  out <- lapply(cols_map, function(cand_cols) {
    keep <- intersect(cand_cols, colnames(df))
    if (length(keep) == 0) {
      rep(0, nrow(df))
    } else {
      rowSums(df[, keep, drop = FALSE], na.rm = TRUE)
    }
  })
  out <- as.data.frame(out, check.names = FALSE)
  rownames(out) <- rownames(df)
  out
}


row_map <- tribble(
  ~row, ~food, ~components,
  14L, "Black tea", list(list(col="Standard.tea.intake", portion=240, weight=1)),
  15L, "Green tea", list(list(col="Green.tea.intake", portion=240, weight=1)),
  16L, "Other tea A", list(list(col="Other.tea.intake", portion=240, weight=0.5)),
  17L, "Other tea B", list(list(col="Other.tea.intake", portion=240, weight=0.5)),

  32L, "Dark chocolate", list(list(col="Dark.chocolate.intake", portion=50, weight=1)),
  33L, "Milk chocolate", list(list(col="Milk.chocolate.intake", portion=50, weight=1)),
  40L, "Hot chocolate (all)", list(list(col="Hot.chocolate.intake", portion=240, weight=1),
                                   list(col="Low.calorie.hot.chocolate.intake", portion=240, weight=1)),
  50L, "Chocolate biscuits", list(list(col="Chocolate.biscuits.intake", portion=13.5, weight=1)),
  51L, "Mixed chocolate snacks", list(
        list(col="Chocolate.covered.biscuits.intake", portion=13.5, weight=1),
        list(col="Chocolate.covered.raisin.intake",   portion=30,   weight=1),
        list(col="Chocolate.bar.intake",              portion=50,   weight=1),
        list(col="Chocolate.sweet.intake",            portion=30,   weight=1)
  ),

  58L, "Red wine",        list(list(col="Red.wine.intake",        portion=165.76, weight=1)),
  59L, "Rose wine",       list(list(col="Rose.wine.intake",       portion=163.5,  weight=1)),
  60L, "White wine",      list(list(col="White.wine.intake",      portion=162.96, weight=1)),
  61L, "Fortified wine",  list(list(col="Fortified.wine.intake",  portion=50,     weight=1)),

  85L, "Orange juice",           list(list(col="Orange.juice.intake",          portion=250, weight=1)),
  78L, "Grapefruit juice",       list(list(col="Grapefruit.juice.intake",      portion=250, weight=1)),
  90L, "Pure fruit/veg juice",   list(list(col="Pure.fruit.vegetable.juice.intake", portion=250, weight=1)),
  89L, "Fruit smoothie",         list(list(col="Fruit.smoothie.intake",        portion=250, weight=1)),

  348L, "Stewed fruit (apples)", list(list(col="Stewed.fruit.intake", portion=80, weight=1)),
  298L, "Prunes",                list(list(col="Prune.intake",        portion=30, weight=1)),
  366L, "Dried fruit",           list(list(col="Dried.fruit.intake",  portion=30, weight=1)),
  304L, "Mixed fruit",           list(list(col="Mixed.fruit.intake",  portion=80, weight=1)),
  252L, "Apples",                list(list(col="Apple.intake",        portion=80, weight=1)),
  300L, "Bananas",               list(list(col="Banana.intake",       portion=80, weight=1)),
  354L, "Berries",               list(list(col="Berry.intake",        portion=80, weight=1)),
  346L, "Cherries",              list(list(col="Cherry.intake",       portion=80, weight=1)),
  369L, "Grapefruit",            list(list(col="Grapefruit.intake",   portion=80, weight=1)),

  # 葡萄：同一 intake 拆分黑/绿
  377L, "Grapes - black", list(list(col="Grape.intake", portion=80, weight=0.32)),
  378L, "Grapes - green", list(list(col="Grape.intake", portion=80, weight=0.68)),

  307L, "Mango",      list(list(col="Mango.intake",      portion=80, weight=1)),
  311L, "Melon",      list(list(col="Melon.intake",      portion=80, weight=1)),
  372L, "Orange",     list(list(col="Orange.intake",     portion=80, weight=1)),
  373L, "Tangerine",  list(list(col="Satsuma.intake",    portion=80, weight=1)),
  340L, "Peach/Nectarine", list(list(col="Peach.nectarine.intake", portion=80, weight=1)),
  255L, "Pear",       list(list(col="Pear.intake",       portion=80, weight=1)),
  319L, "Pineapple",  list(list(col="Pineapple.intake",  portion=80, weight=1)),
  344L, "Plum",       list(list(col="Plum.intake",       portion=40, weight=1)),
  321L, "Other fruit - pomegranate", list(list(col="Other.fruit.intake", portion=80, weight=0.5)),
  305L, "Other fruit - kiwi",        list(list(col="Other.fruit.intake", portion=80, weight=0.5)),

  578L, "Fried potatoes",          list(list(col="Fried.potatoes.intake",          portion=180, weight=1)),
  572L, "Boiled/Baked potatoes",   list(list(col="Boiled.baked.potatoes.intake",   portion=180, weight=1)),
  576L, "Mashed potatoes",         list(list(col="Mashed.potato.intake",           portion=180, weight=1)),

  614L, "Mixed vegetables",  list(list(col="Mixed.vegetable.intake", portion=80, weight=1)),
  615L, "Vegetable pieces",  list(list(col="Vegetable.pieces.intake", portion=80, weight=1)),
  623L, "Coleslaw",          list(list(col="Coleslaw.intake",         portion=80, weight=1)),
  667L, "Side salad",        list(list(col="Side.salad.intake",       portion=80, weight=1)),
  379L, "Avocado",           list(list(col="Avocado.intake",          portion=160, weight=1)),
  610L, "Green beans",       list(list(col="Green.bean.intake",       portion=80, weight=0.93)),
  587L, "Beetroot",          list(list(col="Beetroot.intake",         portion=80, weight=1)),
  505L, "Broccoli",          list(list(col="Broccoli.intake",         portion=80, weight=1)),
  565L, "Butternut squash",  list(list(col="Butternut.squash.intake", portion=80, weight=1)),
  503L, "Cabbage",           list(list(col="Cabbage.kale.intake",     portion=80, weight=0.5)),
  500L, "Kale",              list(list(col="Cabbage.kale.intake",     portion=80, weight=0.5)),
  592L, "Carrots",           list(list(col="Carrot.intake",           portion=80, weight=1)),
  499L, "Cauliflower",       list(list(col="Cauliflower.intake",      portion=80, weight=1)),
  465L, "Celery",            list(list(col="Celery.intake",           portion=26.7, weight=1)),
  559L, "Courgette",         list(list(col="Courgette.intake",        portion=80, weight=1)),
  467L, "Cucumber",          list(list(col="Cucumber.intake",         portion=32, weight=1)),
  419L, "Garlic",            list(list(col="Garlic.intake",           portion=5,  weight=1)),
  522L, "Leek",              list(list(col="Leek.intake",             portion=80, weight=1)),
  702L, "Lettuce",           list(list(col="Lettuce.intake",          portion=80, weight=1)),
  712L, "Mushroom",          list(list(col="Mushroom.intake",         portion=80, weight=1)),
  521L, "Onion",             list(list(col="Onion.intake",            portion=80, weight=1)),
  586L, "Parsnip",           list(list(col="Parsnip.intake",          portion=80, weight=1)),
  397L, "Sweet pepper",      list(list(col="Sweet.pepper.intake",     portion=80, weight=1)),
  # 菠菜：同一 intake 拆分熟/生（若你其实有两个独立列，请改成各自列并 weight=1）
  513L, "Spinach (cooked)",  list(list(col="Spinach.intake",          portion=80, weight=0.5)),
  706L, "Spinach (raw)",     list(list(col="Spinach.intake",          portion=80, weight=0.5)),
  507L, "Sprouts",           list(list(col="Sprouts.intake",          portion=80, weight=1)),
  139L, "Sweetcorn",         list(list(col="Sweetcorn.intake",        portion=80, weight=1)),
  571L, "Sweet potato",      list(list(col="Sweet.potato.intake",     portion=130, weight=1)),
  392L, "Tomato (fresh)",    list(list(col="Fresh.tomato.intake",     portion=80, weight=1)),
  390L, "Tomato (tinned)",   list(list(col="Tinned.tomato.intake",    portion=200, weight=1)),
  597L, "Turnip",            list(list(col="Turnip.swede.intake",     portion=80, weight=0.5)),
  589L, "Swede",             list(list(col="Turnip.swede.intake",     portion=80, weight=0.5)),
  695L, "Watercress",        list(list(col="Watercress.intake",       portion=80, weight=1)),
  564L, "Asparagus",         list(list(col="Other.vegetables.intake",        portion=80, weight=0.4)),
  394L, "Aubergine",         list(list(col="Other.vegetables.intake",        portion=80, weight=0.3)),
  566L, "Squash (other)",    list(list(col="Other.vegetables.intake",           portion=80, weight=0.3)),

  847L, "Olives - black",    list(list(col="Olives.intake",           portion=50, weight=0.5)),
  848L, "Olives - green",    list(list(col="Olives.intake",           portion=50, weight=0.5))
)

# 4) 构建五大类 mg/100g 矩阵（保留）
flavonoid_subclass_per100g <- build_subclass_matrix(flavonoid.checkout, cols)

# 5) 缺失列检查（可选）
missing_cols <- lapply(cols, function(v) setdiff(v, colnames(flavonoid.checkout)))

# 6) 平均版函数（新增）
mean_intake_col <- function(df, col, na_to_zero = TRUE) {
  if (!col %in% names(df)) return(NA_real_)
  v <- df[[col]]
  if (na_to_zero) v[is.na(v)] <- 0
  mean(v, na.rm = TRUE)
}

compute_row_mean_contrib <- function(row, na_to_zero = TRUE) {
  stopifnot(row >= 1, row <= nrow(flavonoid_subclass_per100g))
  vec <- as.numeric(flavonoid_subclass_per100g[row, ])
  names(vec) <- colnames(flavonoid_subclass_per100g)

  cfg <- dplyr::filter(row_map, row == !!row)
  if (nrow(cfg) == 0) return(setNames(rep(0, length(vec)), names(vec)))

  out <- setNames(rep(0, length(vec)), names(vec))
  for (comp in cfg$components[[1]]) {
    colname <- comp$col; portion <- comp$portion; weight <- comp$weight
    m_intake <- mean_intake_col(p.24h.foods.average, colname, na_to_zero = na_to_zero)
    if (is.na(m_intake)) { warning(sprintf("intake 列不存在: %s（row=%s）", colname, row)); next }
    grams_mean <- as.numeric(m_intake) * portion
    out <- out + vec * (grams_mean / 100) * weight
  }
  out
}

compute_mean_contrib_table <- function(rows, na_to_zero = TRUE) {
  rows <- as.integer(rows)
  res <- purrr::map(rows, ~{
    v <- compute_row_mean_contrib(.x, na_to_zero = na_to_zero)
    tibble(row = .x, subclass = names(v), mean_mg_day = as.numeric(v))
  }) %>% dplyr::bind_rows() %>%
    dplyr::left_join(dplyr::select(row_map, row, food), by = "row") %>%
    dplyr::relocate(food, .after = row) %>%
    dplyr::group_by(row, food) %>%
    dplyr::mutate(total_mean_mg_day = sum(mean_mg_day, na.rm = TRUE)) %>%
    dplyr::ungroup()

  list(
    per_food_by_subclass_mean = res %>% dplyr::arrange(dplyr::desc(total_mean_mg_day), food, dplyr::desc(mean_mg_day)),
    per_food_total_mean       = res %>% dplyr::distinct(row, food, total_mean_mg_day) %>% dplyr::arrange(dplyr::desc(total_mean_mg_day)),
    grand_total_mean          = res %>% dplyr::distinct(row, total_mean_mg_day) %>% dplyr::summarise(sum(total_mean_mg_day), .groups="drop") %>% dplyr::pull(1)
  )
}

# 7) 关心的行（保留）
rows_of_interest <- c(14,15,16,17,32,33,40,50,51,58,59,60,61,85,78,90,89,348,298,366,304,252,300,354,346,369,377,378,307,311,372,373,340,255,319,344,321,305,578,572,576,614,615,623,667,379,610,587,505,565,503,500,592,499,465,559,467,419,522,702,712,521,586,397,513,706,507,139,571,392,390,597,589,695,564,394,566,847,848)

# 8) 调用（替换）
out_mean <- compute_mean_contrib_table(rows_of_interest, na_to_zero = TRUE)

per_food_total_mean        <- out_mean$per_food_total_mean
per_food_by_subclass_mean  <- out_mean$per_food_by_subclass_mean
grand_total_mean           <- out_mean$grand_total_mean
```




# test loop
```{r}

### Select the variables into a separate dataset for flavonoid evaluation ###
diet.tea <- data.frame(matrix(ncol = 2, nrow = nrow(demographics)))

# Select Participant ID and group (column 20) from the baseline dataset
diet.tea[,1:2] <- demographics[, c(1,27)]

# Rename the columns to match the original variable names
names(diet.tea) <- c("Participant.ID", "group")


sum.tea.values <- function(tea.rows, flavonoid.data, diet.tea) {
  # Specify the column range from column 9 to column 223
  start.col <- 9
  end.col <- 223
  
  # Extract the data from the specified column range and replace NAs with 0
  flavonoid.columns <- flavonoid.data[, start.col:end.col]
  
  # Loop through each row in diet.tea (each participant)
  for (participant in seq_len(nrow(diet.tea))) {
    
    # Initialize an empty vector to store the sum of each column for the current participant
    summed.values <- numeric(ncol(flavonoid.columns))
    
    # Loop through each specified tea row and add its values to the summed.values vector
    for (i in seq_along(tea.rows)) {
      tea.row <- tea.rows[i]
      
      # Multiply by the corresponding p.24h.foods.average value and divide by 240 for each participant
      if (tea.row == 252) {
        # Apple (row 252)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ])  * p.24h.foods.average$Apple.intake[participant]) * 80 / 100
      } else if (tea.row == 69) {
        # Red wine (row 69)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Red.wine.intake[participant]) * 165.76 / 100
      } else if (tea.row == 354) {
        # Berry (row 354)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ])  * p.24h.foods.average$Berry.intake[participant]) * 80 / 100
      } else if (tea.row == 369) {
        # Grapefruit (row 369)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Grapefruit.intake[participant]) * 80 / 100
      } else if (tea.row == 377) {
        # Grape purple (row = 377)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Grape.intake[participant]) * 80 / 100 *0.32
      } else if (tea.row == 378) {
        # Grape green (row = 378)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Grape.intake[participant]) * 80 / 100 *0.68
      } else if (tea.row == 372) {
        # Orange intake (row 372)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Orange.intake[participant]) * 80 / 100
      } else if (tea.row == 373) {
        # Tangerine intake (row 373)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Satsuma.intake[participant]) * 80 / 100
      } else if (tea.row == 521) {
        # Onion intake (row 521)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Onion.intake[participant]) * 80 / 100
      } else if (tea.row == 397) {
        # Sweet pepper intake (row 397)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Sweet.pepper.intake[participant]) * 80 / 100
      } else if (tea.row == 33) {
        # Dark.chocolate.intake (row 33)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Dark.chocolate.intake[participant]) * 50 / 100
      } else if (tea.row == 3) {
        # Black tea (row 3)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Standard.tea.intake[participant]) * 240 / 100
      } else if (tea.row == 5) {
        # Green tea (row 5)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Green.tea.intake[participant]) * 240 / 100
      }
    }
    
    # Add the resulting summed values for this participant as a new row in the diet.tea dataframe
    # Column names will correspond to the column names in flavonoid_data
    for (i in seq_along(colnames(flavonoid.columns))) {
      col.name <- colnames(flavonoid.columns)[i]
      diet.tea[participant, col.name] <- summed.values[i]
    }
  }
  
  return(diet.tea)
}

# Define the tea rows (adjust based on the actual rows you want to sum)
tea.rows <- c(252, 69, 354, 369, 377, 378, 372, 373, 521, 397, 33, 3, 5)

# Call the function to calculate and update the diet.tea dataframe, incorporating p.24h.foods.average adjustments
diet.tea <- sum.tea.values(tea.rows, flavonoid.checkout, diet.tea)

write.csv(diet.tea, "flavonoid/test.csv", row.names = FALSE)
```



# tea
https://www.bda.uk.com/resource/fluid-water-drinks.html
https://link.springer.com/article/10.1007/s00415-023-12065-7 
tea diffuse
for tea: 1 mug/cup: 240ml 
Standard.tea.intake → Tea [Black], infusion -- row 14
Rooibos.tea.intake → Rooibos tea, brewed -- row 881 (/100*3.21)
Green.tea.intake → Tea [Green], infusion -- row 5
Herbal.tea.intake → Tea, herb, chamomile, brewed/ Peppermint, tea -- no flavonoid
Other.tea.intake
→ Tea [Oolong], infusion -- row 16
→ Tea [White], infusion -- row 17

```{r}
### Select the variables into a separate dataset for flavonoid evaluation ###
diet.tea <- data.frame(matrix(ncol = 2, nrow = nrow(demographics)))

# Select Participant ID and group (column 20) from the baseline dataset
diet.tea[,1:2] <- demographics[, c(1,27)]

# Rename the columns to match the original variable names
names(diet.tea) <- c("Participant.ID", "group")

# Define a function to sum the tea values, adjust with p.24h.foods.average, and add to diet.tea dataframe
sum.tea.values <- function(tea.rows, flavonoid.data, diet.tea) {
  # Specify the column range from column 9 to column 223
  start.col <- 9
  end.col <- 101
  
  # Extract the data from the specified column range and replace NAs with 0
  flavonoid.columns <- flavonoid.data[, start.col:end.col]
  
  # Loop through each row in diet.tea (each participant)
  for (participant in seq_len(nrow(diet.tea))) {
    
    # Initialize an empty vector to store the sum of each column for the current participant
    summed.values <- numeric(ncol(flavonoid.columns))
    
    # Loop through each specified tea row and add its values to the summed.values vector
    for (i in seq_along(tea.rows)) {
      tea.row <- tea.rows[i]
      
      # Multiply by the corresponding p.24h.foods.average value and divide by 240 for each participant
      if (tea.row == 14) {
        # Black tea (row 14)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Standard.tea.intake[participant]) * 240 / 100
      } else if (tea.row == 881) {
        # Rooibos tea (row 881)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Rooibos.tea.intake[participant]) * 240 / 100
      } else if (tea.row == 5) {
        # Green tea (row 5)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Green.tea.intake[participant]) * 240 / 100
      } else if (tea.row == 16) {
        # Other tea (row 16)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Other.tea.intake[participant]) * 240 / 100 /2
      } else if (tea.row == 17) {
        # Other tea (row 17)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[tea.row, ]) * p.24h.foods.average$Other.tea.intake[participant]) * 240 / 100 /2
      }
    }
    
    # Add the resulting summed values for this participant as a new row in the diet.tea dataframe
    # Column names will correspond to the column names in flavonoid_data
    for (i in seq_along(colnames(flavonoid.columns))) {
      col.name <- colnames(flavonoid.columns)[i]
      diet.tea[participant, col.name] <- summed.values[i]
    }
  }
  
  return(diet.tea)
}

# Define the tea rows (adjust based on the actual rows you want to sum)
tea.rows <- c(14, 881, 5, 16, 17)

# Call the function to calculate and update the diet.tea dataframe, incorporating p.24h.foods.average adjustments
diet.tea <- sum.tea.values(tea.rows, flavonoid.checkout, diet.tea)

write.csv(diet.tea, "flavonoid/diet.tea.csv", row.names = FALSE)
```

tableone to describe
```{r}
# anthocyanins
diet.tea$anthocyanins.tea <- diet.tea$Cyanidin + diet.tea$Delphinidin + diet.tea$Malvidin + diet.tea$Pelargonidin + diet.tea$Petunidin + diet.tea$Peonidin

# flavanones 
diet.tea$flavanones.tea <- diet.tea$Eriodictyol + diet.tea$Hesperetin + diet.tea$Naringenin

# flavan-3-ols # add for Epigallocatechin Gallocatechin Catechin.3.O.gallate Epicatechin.3.O.gallate Epigallocatechin.3.O.gallate
diet.tea$flavan.3.ols.tea <- diet.tea$X....Catechin + diet.tea$X....Epicatechin + diet.tea$X....Epigallocatechin + diet.tea$X....Gallocatechin + diet.tea$X....Catechin.3.O.gallate + diet.tea$X....Epicatechin.3.O.gallate + diet.tea$X....Gallocatechin.3.O.gallate +  diet.tea$X....Epigallocatechin.3.O.gallate

# flavonols # add for jaceidin, patuletin, spinacetin
diet.tea$flavonols.tea <- diet.tea$Quercetin + diet.tea$Kaempferol + diet.tea$Myricetin + diet.tea$Isorhamnetin

# flavones
diet.tea$flavones.tea <- diet.tea$Luteolin + diet.tea$Apigenin

# polymers (including proanthocyanidins [excluding monomers], theaflavins, and thearubigins), proanthocyanidins (dimers, trimers, 4–6mers, 7–10mers, polymers, and monomers). 
diet.tea$polymers.tea <-  diet.tea$X02.mers + diet.tea$X03.mers + diet.tea$X04.06.mers + diet.tea$X07.10.mers + diet.tea$Polymers...10.mers.

# Proanthocyanidins
diet.tea$proanthocyanidins.tea <- diet.tea$Theaflavin + diet.tea$Thearubigins

# total flavonoid
diet.tea$total.flavonoid.tea <- diet.tea$anthocyanins.tea + diet.tea$flavanones.tea + diet.tea$flavan.3.ols.tea + diet.tea$flavonols.tea + diet.tea$flavones + diet.tea$polymers.tea + diet.tea$proanthocyanidins.tea

# Set the 'group' column as a factor with specified levels: 'psoriasis' and 'non-psoriasis'
diet.tea$group <- factor(diet.tea$group, levels = c("psoriasis", "non-psoriasis"))

# Create a descriptive table for the tea variables (columns 3 to 217) stratified by the 'group'
vars <- names(diet.tea)[96:103]  # Selecting the variable names from column 3 to 217
description.tea <- CreateTableOne(data = diet.tea,
                                  vars = vars,  # Variable names extracted above
                                  strata = "group")  # Stratified by 'group' column

# Print the description table without quotes, without spaces, and without printing to the console
print(description.tea, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
description.tea

# Save the descriptive table results to a CSV file
write.csv(print(description.tea), "flavonoid/tearesult.csv")
```


# chocolate
1 bar = 50g
row 32 and 33 is revised from USDA###
Chocolate.bar.intake → Candies, chocolate covered, caramel with nuts -- row 51
Dark.chocolate.intake → Chocolate, dark -- row 42
Milk.chocolate.intake → Chocolate, milk -- row 41
White.chocolate.intake → no flavonoid 
https://www.bda.uk.com/resource/fluid-water-drinks.html
for chocolate drink: 1 mug/cup: 240ml 
Hot.chocolate.intake → Chocolate milk, beverage -- row 40
Low.calorie.hot.chocolate.intake → Chocolate milk, beverage -- row 40
https://www.sainsburys.co.uk/gol-ui/groceries/food-cupboard/biscuits-and-crackers/biscuits/chocolate-biscuits/c:1019467
1 biscuit = 13.5g
Chocolate.biscuits.intake → Biscuits, half coated with chocolate -- row 50
Chocolate.covered.biscuits.intake → Candies, chocolate covered, caramel with nuts -- row 51
1 handful = 30g
Chocolate.covered.raisin.intake → Candies, chocolate covered, caramel with nuts -- row 51
Chocolate.sweet.intake → Candies, chocolate covered, caramel with nuts -- row 51

```{r}
rm(diet.coffee)
### Select the variables into a separate dataset for flavonoid evaluation ###
diet.chocolate <- data.frame(matrix(ncol = 2, nrow = nrow(demographics)))

# Select Participant ID and group (column 20) from the baseline dataset
diet.chocolate[,1:2] <- demographics[, c(1,27)]

# Rename the columns to match the original variable names
names(diet.chocolate) <- c("Participant.ID", "group")

# Define a function to sum the chocolate values, adjust with p.24h.foods.average, and add to diet.chocolate dataframe
sum.chocolate.values <- function(chocolate.rows, flavonoid.data, diet.chocolate) {
  # Specify the column range from column 9 to column 223
  start.col <- 9
  end.col <- 101
  
  # Extract the data from the specified column range and replace NAs with 0
  flavonoid.columns <- flavonoid.data[, start.col:end.col]
  
  # Loop through each row in diet.chocolate (each participant)
  for (participant in seq_len(nrow(diet.chocolate))) {
    
    # Initialize an empty vector to store the sum of each column for the current participant
    summed.values <- numeric(ncol(flavonoid.columns))
    
    # Loop through each specified chocolate row and add its values to the summed.values vector
    for (i in seq_along(chocolate.rows)) {
      chocolate.row <- chocolate.rows[i]
      
      # Multiply by the corresponding p.24h.foods.average value and divide by 240 for each participant
      if (chocolate.row == 41) {
    # Milk.chocolate.intake (row 41)
    summed.values <- summed.values +
       (as.numeric(flavonoid.columns[chocolate.row, ]) * p.24h.foods.average$Milk.chocolate.intake[participant]) * 50 / 100
    } else if (chocolate.row == 42) {
        # Dark.chocolate.intake (row 42)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[chocolate.row, ]) * p.24h.foods.average$Dark.chocolate.intake[participant]) * 50 / 100
      } else if (chocolate.row == 40) {
        # (Low) Hot.chocolate.intake (row 40)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[chocolate.row, ]) * p.24h.foods.average$Hot.chocolate.intake[participant]) * 240 / 100 + (as.numeric(flavonoid.columns[chocolate.row, ]) * p.24h.foods.average$Low.calorie.hot.chocolate.intake[participant]) * 240 / 100
      } else if (chocolate.row == 50) {
    # Chocolate.biscuits.intake(row 50)
    summed.values <- summed.values + 
      (as.numeric(flavonoid.columns[chocolate.row, ]) * p.24h.foods.average$Chocolate.biscuits.intake[participant]) * 13.5 / 100
    } else if (chocolate.row == 51) {
    # Chocolate.covered.raisin.intake and Chocolate.covered biscuits intake, chocolate bar, Chocolate.sweet.intake (row 51)
    summed.values <- summed.values + 
      (as.numeric(flavonoid.columns[chocolate.row, ]) * p.24h.foods.average$Chocolate.covered.biscuits.intake[participant]) *13.5 / 100 + (as.numeric(flavonoid.columns[chocolate.row, ]) * p.24h.foods.average$Chocolate.covered.raisin.intake[participant]) * 30 / 100 + (as.numeric(flavonoid.columns[chocolate.row, ]) * p.24h.foods.average$Chocolate.bar.intake[participant]) * 50 / 100 + (as.numeric(flavonoid.columns[chocolate.row, ]) * p.24h.foods.average$Chocolate.sweet.intake[participant]) * 30 / 100
    }
    }
    
    # Add the resulting summed values for this participant as a new row in the diet.chocolate dataframe
    # Column names will correspond to the column names in flavonoid_data
    for (i in seq_along(colnames(flavonoid.columns))) {
      col.name <- colnames(flavonoid.columns)[i]
      diet.chocolate[participant, col.name] <- summed.values[i]
    }
  }
  
  return(diet.chocolate)
}

# Define the chocolate rows (adjust based on the actual rows you want to sum)
chocolate.rows <- c(41, 42, 40, 50, 51)

# Call the function to calculate and update the diet.chocolate dataframe, incorporating p.24h.foods.average adjustments
diet.chocolate <- sum.chocolate.values(chocolate.rows, flavonoid.checkout, diet.chocolate)
diet.chocolate$X....Epicatechin[is.na(diet.chocolate$X....Epicatechin)] <- 0
write.csv(diet.chocolate, "flavonoid/diet.chocolate.csv", row.names = FALSE)
```

tableone to describe
```{r}
# anthocyanins
diet.chocolate$anthocyanins.chocolate <- diet.chocolate$Cyanidin + diet.chocolate$Delphinidin + diet.chocolate$Malvidin + diet.chocolate$Pelargonidin + diet.chocolate$Petunidin + diet.chocolate$Peonidin

# flavanones 
diet.chocolate$flavanones.chocolate <- diet.chocolate$Eriodictyol + diet.chocolate$Hesperetin + diet.chocolate$Naringenin

# flavan-3-ols # add for Epigallocatechin Gallocatechin Catechin.3.O.gallate Epicatechin.3.O.gallate Epigallocatechin.3.O.gallate
diet.chocolate$flavan.3.ols.chocolate <- diet.chocolate$X....Catechin + diet.chocolate$X....Epicatechin + diet.chocolate$X....Epigallocatechin + diet.chocolate$X....Gallocatechin + diet.chocolate$X....Catechin.3.O.gallate + diet.chocolate$X....Epicatechin.3.O.gallate + diet.chocolate$X....Gallocatechin.3.O.gallate +  diet.chocolate$X....Epigallocatechin.3.O.gallate

# flavonols # add for jaceidin, patuletin, spinacetin
diet.chocolate$flavonols.chocolate <- diet.chocolate$Quercetin + diet.chocolate$Kaempferol + diet.chocolate$Myricetin + diet.chocolate$Isorhamnetin

# flavones
diet.chocolate$flavones.chocolate <- diet.chocolate$Luteolin + diet.chocolate$Apigenin

# polymers (including proanthocyanidins [excluding monomers], theaflavins, and thearubigins), proanthocyanidins (dimers, trimers, 4–6mers, 7–10mers, polymers, and monomers). 
diet.chocolate$polymers.chocolate <-  diet.chocolate$X02.mers + diet.chocolate$X03.mers + diet.chocolate$X04.06.mers + diet.chocolate$X07.10.mers + diet.chocolate$Polymers...10.mers.

# Proanthocyanidins
diet.chocolate$proanthocyanidins.chocolate <- diet.chocolate$Theaflavin + diet.chocolate$Thearubigins

# total flavonoid
diet.chocolate$total.flavonoid.chocolate <- diet.chocolate$anthocyanins.chocolate + diet.chocolate$flavanones.chocolate + diet.chocolate$flavan.3.ols.chocolate + diet.chocolate$flavonols.chocolate + diet.chocolate$flavones + diet.chocolate$polymers.chocolate + diet.chocolate$proanthocyanidins.chocolate

# Set the 'group' column as a factor with specified levels: 'psoriasis' and 'non-psoriasis'
diet.chocolate$group <- factor(diet.chocolate$group, levels = c("psoriasis", "non-psoriasis"))

# Create a descriptive table for the tea variables (columns 3 to 217) stratified by the 'group'
vars <- names(diet.chocolate)[96:103]  # Selecting the variable names from column 3 to 217
description.chocolate <- CreateTableOne(data = diet.chocolate,
                                  vars = vars,  # Variable names extracted above
                                  strata = "group")  # Stratified by 'group' column

# Print the description table without quotes, without spaces, and without printing to the console
print(description.chocolate, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
description.chocolate

# Save the descriptive table results to a CSV file
write.csv(print(description.chocolate), "flavonoid/chocolateresult.csv")
```

# alcoholic drink
all wine glass size is use weighted average size
1 glass red wine = 165.76 ml; 1 glass rose wine = 163.50 ml; 1 glass white wine = 162.96 ml
Red.wine.intake → Wine [Red] -- row 58
Rose.wine.intake → Wine [Rosé] -- row 59
White.wine.intake → Wine [White] -- row 60
https://www.gov.uk/weights-measures-and-packaging-the-law/specified-quantities
a sherry/port = 50ml
Fortified.wine.intake → Sherry -- row 61
a measure = 25ml
Spirits.intake → Scotch Whisky -- no flavonoid
a unit = 125ml
Other.alcohol.intake -- no flavonoid
1 pint --> 568ml
Beer.cider.intake → Beer [Regular] -- row 68

```{r}
rm(diet.chocolate)
### Select the variables into a separate dataset for flavonoid evaluation ###
diet.alcohol <- data.frame(matrix(ncol = 2, nrow = nrow(demographics)))

# Select Participant ID and group (column 20) from the baseline dataset
diet.alcohol[,1:2] <- demographics[, c(1,27)]

# Rename the columns to match the original variable names
names(diet.alcohol) <- c("Participant.ID", "group")

# Define a function to sum the alcohol values, adjust with p.24h.foods.average, and add to diet.alcohol dataframe
sum.alcohol.values <- function(alcohol.rows, flavonoid.data, diet.alcohol) {
  # Specify the column range from column 9 to column 223
  start.col <- 9
  end.col <- 101
  
  # Extract the data from the specified column range and replace NAs with 0
  flavonoid.columns <- flavonoid.data[, start.col:end.col]
  
  # Loop through each row in diet.alcohol (each participant)
  for (participant in seq_len(nrow(diet.alcohol))) {
    
    # Initialize an empty vector to store the sum of each column for the current participant
    summed.values <- numeric(ncol(flavonoid.columns))
    
    # Loop through each specified alcohol row and add its values to the summed.values vector
    for (i in seq_along(alcohol.rows)) {
      alcohol.row <- alcohol.rows[i]
      
      # Multiply by the corresponding p.24h.foods.average value and divide by 240 for each participant
      if (alcohol.row == 58) {
        # Red.wine.intake (row 58)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[alcohol.row, ]) * p.24h.foods.average$Red.wine.intake[participant]) * 165.76 / 100
      } else if (alcohol.row == 59) {
        # Rose.wine.intake (row 59)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[alcohol.row, ]) * p.24h.foods.average$Rose.wine.intake[participant]) * 163.50 / 100
      } else if (alcohol.row == 60) {
        # White.wine.intake (row 60)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[alcohol.row, ]) * p.24h.foods.average$White.wine.intake[participant]) * 162.96 / 100
      } else if (alcohol.row == 61) {
        # Fortified.wine.intake (row 61)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[alcohol.row, ]) * p.24h.foods.average$Fortified.wine.intake[participant]) * 50 / 100
      } else if (alcohol.row == 68) {
        # Beer.cider.intake (row 68)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[alcohol.row, ]) * p.24h.foods.average$Beer.cider.intake[participant]) * 568 / 100
      } 
    }
    
    # Add the resulting summed values for this participant as a new row in the diet.alcohol dataframe
    # Column names will correspond to the column names in flavonoid_data
    for (i in seq_along(colnames(flavonoid.columns))) {
      col.name <- colnames(flavonoid.columns)[i]
      diet.alcohol[participant, col.name] <- summed.values[i]
    }
  }
  
  return(diet.alcohol)
}

# Define the alcohol rows (adjust based on the actual rows you want to sum)
alcohol.rows <- c(58, 59, 60, 61, 68)

# Call the function to calculate and update the diet.alcohol dataframe, incorporating p.24h.foods.average adjustments
diet.alcohol <- sum.alcohol.values(alcohol.rows, flavonoid.checkout, diet.alcohol)

write.csv(diet.alcohol, "flavonoid/diet.alcohol.csv", row.names = FALSE)
```

tableone to describe
```{r}
# anthocyanins
diet.alcohol$anthocyanins.alcohol <- diet.alcohol$Cyanidin + diet.alcohol$Delphinidin + diet.alcohol$Malvidin + diet.alcohol$Pelargonidin + diet.alcohol$Petunidin + diet.alcohol$Peonidin

# flavanones 
diet.alcohol$flavanones.alcohol <- diet.alcohol$Eriodictyol + diet.alcohol$Hesperetin + diet.alcohol$Naringenin

# flavan-3-ols # add for Epigallocatechin Gallocatechin Catechin.3.O.gallate Epicatechin.3.O.gallate Epigallocatechin.3.O.gallate
diet.alcohol$flavan.3.ols.alcohol <- diet.alcohol$X....Catechin + diet.alcohol$X....Epicatechin + diet.alcohol$X....Epigallocatechin + diet.alcohol$X....Gallocatechin + diet.alcohol$X....Catechin.3.O.gallate + diet.alcohol$X....Epicatechin.3.O.gallate + diet.alcohol$X....Gallocatechin.3.O.gallate +  diet.alcohol$X....Epigallocatechin.3.O.gallate

# flavonols # add for jaceidin, patuletin, spinacetin
diet.alcohol$flavonols.alcohol <- diet.alcohol$Quercetin + diet.alcohol$Kaempferol + diet.alcohol$Myricetin + diet.alcohol$Isorhamnetin

# flavones
diet.alcohol$flavones.alcohol <- diet.alcohol$Luteolin + diet.alcohol$Apigenin

# polymers (including proanthocyanidins [excluding monomers], theaflavins, and thearubigins), proanthocyanidins (dimers, trimers, 4–6mers, 7–10mers, polymers, and monomers). 
diet.alcohol$polymers.alcohol <-  diet.alcohol$X02.mers + diet.alcohol$X03.mers + diet.alcohol$X04.06.mers + diet.alcohol$X07.10.mers + diet.alcohol$Polymers...10.mers.

# Proanthocyanidins
diet.alcohol$proanthocyanidins.alcohol <- diet.alcohol$Theaflavin + diet.alcohol$Thearubigins

# total flavonoid
diet.alcohol$total.flavonoid.alcohol <- diet.alcohol$anthocyanins.alcohol + diet.alcohol$flavanones.alcohol + diet.alcohol$flavan.3.ols.alcohol + diet.alcohol$flavonols.alcohol + diet.alcohol$flavones + diet.alcohol$polymers.alcohol + diet.alcohol$proanthocyanidins.alcohol

# Set the 'group' column as a factor with specified levels: 'psoriasis' and 'non-psoriasis'
diet.alcohol$group <- factor(diet.alcohol$group, levels = c("psoriasis", "non-psoriasis"))

# Create a descriptive table for the tea variables (columns 3 to 217) stratified by the 'group'
vars <- names(diet.alcohol)[96:103]  # Selecting the variable names from column 3 to 217
description.alcohol <- CreateTableOne(data = diet.alcohol,
                                  vars = vars,  # Variable names extracted above
                                  strata = "group")  # Stratified by 'group' column

# Print the description table without quotes, without spaces, and without printing to the console
print(description.alcohol, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
description.alcohol

# Save the descriptive table results to a CSV file
write.csv(print(description.alcohol), "flavonoid/alcoholresult.ap.csv")
```

# other include drinks -- juice
1 glass/carton = 250ml
Orange.juice.intake → Orange juice, raw -- row 85
Grapefruit.juice.intake → Grapefruit, pure juice -- row 78
Pure.fruit.vegetable.juice.intake → 
Fruit juice, freshly squeezed orange, apple, pear, ginger -- row 90
Fruit.smoothie.intake → Fruit smoothie, banana & strawberry -- row 89
https://www.mordorintelligence.com/industry-reports/smoothies-market
https://store.mintel.com/report/uk-fruit-juice-juice-drinks-and-smoothies-market-report-2023
Dairy.smoothie.intake → no flavonoid
```{r}
rm(diet.alcohol)
### Select the variables into a separate dataset for flavonoid evaluation ###
diet.juice <- data.frame(matrix(ncol = 2, nrow = nrow(demographics)))

# Select Participant ID and group (column 20) from the baseline dataset
diet.juice[, 1:2] <- demographics[, c(1,27)]

# Rename the columns to match the original variable names
names(diet.juice) <- c("Participant.ID", "group")

# Define a function to sum the juice values, adjust with p.24h.foods.average, and add to diet.juice dataframe
sum.juice.values <- function(juice.rows, flavonoid.data, diet.juice) {
  # Specify the column range from column 9 to column 223
  start.col <- 9
  end.col <- 101
  
  # Extract the data from the specified column range and replace NAs with 0
  flavonoid.columns <- flavonoid.data[, start.col:end.col]
  
  # Loop through each row in diet.juice (each participant)
  for (participant in seq_len(nrow(diet.juice))) {
    
    # Initialize an empty vector to store the sum of each column for the current participant
    summed.values <- numeric(ncol(flavonoid.columns))
    
    # Loop through each specified juice row and add its values to the summed.values vector
    for (i in seq_along(juice.rows)) {
      juice.row <- juice.rows[i]
      
      # Multiply by the corresponding p.24h.foods.average value and divide by 240 for each participant
      if (juice.row == 85) {
        # Orange.juice.intake (row 85)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[juice.row, ]) * p.24h.foods.average$Orange.juice.intake[participant]) * 250 / 100
      } else if (juice.row == 78) {
        # Grapefruit.juice.intake (row 78)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[juice.row, ]) * p.24h.foods.average$Grapefruit.juice.intake[participant]) * 250 / 100
      } else if (juice.row == 90) {
        # Pure.fruit.vegetable.juice.intake (row 90)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[juice.row, ]) * p.24h.foods.average$Pure.fruit.vegetable.juice.intake[participant]) * 250 / 100
      } else if (juice.row == 88) {
        # Fruit.smoothie.intake (row 88)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[juice.row, ]) * p.24h.foods.average$Fruit.smoothie.intake[participant]) * 250 / 100
      }
    }
    
    # Add the resulting summed values for this participant as a new row in the diet.juice dataframe
    # Column names will correspond to the column names in flavonoid_data
    for (i in seq_along(colnames(flavonoid.columns))) {
      col.name <- colnames(flavonoid.columns)[i]
      diet.juice[participant, col.name] <- summed.values[i]
    }
  }
  
  return(diet.juice)
}

# Define the juice rows (adjust based on the actual rows you want to sum)
juice.rows <- c(85, 78, 90, 88)

# Call the function to calculate and update the diet.juice dataframe, incorporating p.24h.foods.average adjustments
diet.juice <- sum.juice.values(juice.rows, flavonoid.checkout, diet.juice)

write.csv(diet.juice, "flavonoid/diet.juice.csv", row.names = FALSE)
```

tableone to describe
```{r}
# anthocyanins
diet.juice$anthocyanins.juice <- diet.juice$Cyanidin + diet.juice$Delphinidin + diet.juice$Malvidin + diet.juice$Pelargonidin + diet.juice$Petunidin + diet.juice$Peonidin

# flavanones 
diet.juice$flavanones.juice <- diet.juice$Eriodictyol + diet.juice$Hesperetin + diet.juice$Naringenin

# flavan-3-ols # add for Epigallocatechin Gallocatechin Catechin.3.O.gallate Epicatechin.3.O.gallate Epigallocatechin.3.O.gallate
diet.juice$flavan.3.ols.juice <- diet.juice$X....Catechin + diet.juice$X....Epicatechin + diet.juice$X....Epigallocatechin + diet.juice$X....Gallocatechin + diet.juice$X....Catechin.3.O.gallate + diet.juice$X....Epicatechin.3.O.gallate + diet.juice$X....Gallocatechin.3.O.gallate +  diet.juice$X....Epigallocatechin.3.O.gallate

# flavonols # add for jaceidin, patuletin, spinacetin
diet.juice$flavonols.juice <- diet.juice$Quercetin + diet.juice$Kaempferol + diet.juice$Myricetin + diet.juice$Isorhamnetin

# flavones
diet.juice$flavones.juice <- diet.juice$Luteolin + diet.juice$Apigenin

# polymers (including proanthocyanidins [excluding monomers], theaflavins, and thearubigins), proanthocyanidins (dimers, trimers, 4–6mers, 7–10mers, polymers, and monomers). 
diet.juice$polymers.juice <-  diet.juice$X02.mers + diet.juice$X03.mers + diet.juice$X04.06.mers + diet.juice$X07.10.mers + diet.juice$Polymers...10.mers.

# Proanthocyanidins
diet.juice$proanthocyanidins.juice <- diet.juice$Theaflavin + diet.juice$Thearubigins

# total flavonoid
diet.juice$total.flavonoid.juice <- diet.juice$anthocyanins.juice + diet.juice$flavanones.juice + diet.juice$flavan.3.ols.juice + diet.juice$flavonols.juice + diet.juice$flavones + diet.juice$polymers.juice + diet.juice$proanthocyanidins.juice

# Set the 'group' column as a factor with specified levels: 'psoriasis' and 'non-psoriasis'
diet.juice$group <- factor(diet.juice$group, levels = c("psoriasis", "non-psoriasis"))

# Create a descriptive table for the tea variables (columns 3 to 217) stratified by the 'group'
vars <- names(diet.juice)[96:103]  # Selecting the variable names from column 3 to 217
description.juice <- CreateTableOne(data = diet.juice,
                                  vars = vars,  # Variable names extracted above
                                  strata = "group")  # Stratified by 'group' column

# Print the description table without quotes, without spaces, and without printing to the console
print(description.juice, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
description.juice

# Save the descriptive table results to a CSV file
write.csv(print(description.juice), "flavonoid/juiceresult.csv")
```

# cereal
   Dried fruit added to cereal 100800 136,429 in total, 134,057 yes, 2,372 varied
    → fruit and fibre -- 101 (Dried fruit e.g. raisins 30g)
   Milk added to cereal 100890 246,475 in total, 245,241 yes, 1,234 varied 
    → no polyphenol and flavonoid not consider
https://www.bda.uk.com/resource/food-facts-portion-sizes.html
a bowl = all are uncooked -- so use the portion size to calculate
breakfast cereals = 30g
porridge oats = 40g
Porridge intake → Cereals, oats, regular and quick and instant, not fortified, dry -- row 106
Muesli intake → Breakfast cereal, muesli -- row 92
Oat crunch intake → Cereals, oats, regular and quick and instant, not fortified, dry -- row 106
Plain cereal intake → no flavonoid
Bran cereal intake → Breakfast cereals, bran -- row 93
Whole-wheat cereal intake → Cereals ready-to-eat, WEETABIX WHOLE WHEAT CEREAL -- row 104

    through british nutrition Full portion size list.
Sliced bread intake -- (a sliced = 35g) 
Baguette intake -- (a baguette/ciabatta/panini/sub = 140g)
Bap intake -- (1 big bap/stotty/pitta = 45g)
Bread roll intake -- (1 roll/bap/bun/bagel = 60g)
 → white: no flavonoid -- 53/74*0.9
 → mixed: 50:50 white and whole 
 → wholemeal: Bread, common wheat, whole grain flour -- row 120 48/64*0.9 
 → seeded: Seeded bread, brown -- row 202
 → others: Flour mix, gluten free -- row 167  (coefficient = 0.6)

Naan bread intake → Naan bread -- row 884 (1 naan = 140g)
Garlic bread intake → Garlic bread -- row 164 (a sliced = 35g)
Crispbread intake → crisp bread, seeded -- row 166 (1 cracker/crispbread/cake = 8g)
Oatcakes intake →	Oat, rolled -- row 134 (1 oatcake = 12g)
other bread  → Crumpets, fresh -- 153 (1 slice/wrap/stick/item = 60g)(50g to 65g) 

https://www.gov.uk/government/publications/school-food-standards-resources-for-schools/portion-sizes-and-food-groups
White pasta intake → Pasta -- row 217 (1 serving = 180g)
Wholemeal pasta intake → Pasta, whole grain -- row 135 (1 serving = 180g)
White rice intake → no flavonoid
Brown rice intake → Brown rice, boiled -- row 196 (1 serving = 180g)
Sushi intake → no flavonoid
Snackpot intake → Savoury rice, incl meat & veg varieties, eg. Batchelors, as sold -- row 180 (1 pot = 65g)
Couscous intake → Couscous, cooked -- row 128 (1 serving = 150g)
Other grain intake → Quinoa & Wholegrain Rice -- row 203 (1 serving = 180g)

## preprocess the bread part
```{r}
rm(diet.juice)
appendixfood <- read.csv("24hr/appendixtofoods.csv") %>%
  filter(Participant.ID %in% demographics$Participant.ID)
# Replace "half" with 0.5, "6+" with 6, and convert to numeric, replacing NAs with 0
appendixfood <- appendixfood %>%
  mutate(across(contains("intake"), ~ gsub("half", "0.5", .))) %>%
  mutate(across(contains("intake"), ~ gsub("6\\+", "6", .))) %>%
  mutate(across(contains("intake"), ~ ifelse(is.na(.), "0", .))) %>%   # Replace NA with "0"
  mutate(across(contains("intake"), as.numeric))  # Convert to numeric

# Get all column names for intake related to bread types
sliced_intake_columns <- paste0("Sliced.bread.intake...Instance.", 0:4)
baguette_intake_columns <- paste0("Baguette.intake...Instance.", 0:4)
bap_intake_columns <- paste0("Bap.intake...Instance.", 0:4)
bread_roll_intake_columns <- paste0("Bread.roll.intake...Instance.", 0:4)

# Define the correct type columns for each bread type
sliced_type_columns <- paste0("Type.of.sliced.bread.eaten...Instance.", 0:4)
baguette_type_columns <- paste0("Type.of.baguette.eaten...Instance.", 0:4)  # Corrected this
bap_type_columns <- paste0("Type.of.large.bap.eaten...Instance.", 0:4)
bread_roll_type_columns <- paste0("Type.of.bread.roll.eaten...Instance.", 0:4)


# Replace all NA values in intake columns with 0
appendixfood <- appendixfood %>%
  mutate(across(contains("intake"), ~ ifelse(is.na(.), 0, .)))

# Function to calculate mean intake by type (wholemeal, white, mixed, seeded, others)
calc_mean_by_type <- function(data_row, type, type_columns, intake_columns) {
  # For each column, check if the type is present and return the intake value, otherwise return 0
  intake_values <- mapply(function(type_col, intake_col) {
    ifelse(grepl(type, data_row[[type_col]]), data_row[[intake_col]], 0)
  }, type_columns, intake_columns)
  
  # Calculate the mean of the intake values
  mean(intake_values)
}

appendixfood <- appendixfood %>%
  rowwise() %>%
  
  # Sliced Bread
  mutate(sliced_wholemeal.mean = calc_mean_by_type(cur_data(), "wholemeal", sliced_type_columns, sliced_intake_columns),
         sliced_white.mean = calc_mean_by_type(cur_data(), "white", sliced_type_columns, sliced_intake_columns),
         sliced_mixed.mean = calc_mean_by_type(cur_data(), "mixed", sliced_type_columns, sliced_intake_columns),
         sliced_seeded.mean = calc_mean_by_type(cur_data(), "seeded", sliced_type_columns, sliced_intake_columns),
         sliced_others.mean = calc_mean_by_type(cur_data(), "others", sliced_type_columns, sliced_intake_columns)) %>%
  
  # Baguette
  mutate(baguette_wholemeal.mean = calc_mean_by_type(cur_data(), "wholemeal", baguette_type_columns, baguette_intake_columns),
         baguette_white.mean = calc_mean_by_type(cur_data(), "white", baguette_type_columns, baguette_intake_columns),
         baguette_mixed.mean = calc_mean_by_type(cur_data(), "mixed", baguette_type_columns, baguette_intake_columns),
         baguette_seeded.mean = calc_mean_by_type(cur_data(), "seeded", baguette_type_columns, baguette_intake_columns),
         baguette_others.mean = calc_mean_by_type(cur_data(), "others", baguette_type_columns, baguette_intake_columns)) %>%
  
  # Bap
  mutate(bap_wholemeal.mean = calc_mean_by_type(cur_data(), "wholemeal", bap_type_columns, bap_intake_columns),
         bap_white.mean = calc_mean_by_type(cur_data(), "white", bap_type_columns, bap_intake_columns),
         bap_mixed.mean = calc_mean_by_type(cur_data(), "mixed", bap_type_columns, bap_intake_columns),
         bap_seeded.mean = calc_mean_by_type(cur_data(), "seeded", bap_type_columns, bap_intake_columns),
         bap_others.mean = calc_mean_by_type(cur_data(), "others", bap_type_columns, bap_intake_columns)) %>%
  
  # Bread Roll
  mutate(bread_roll_wholemeal.mean = calc_mean_by_type(cur_data(), "wholemeal", bread_roll_type_columns, bread_roll_intake_columns),
         bread_roll_white.mean = calc_mean_by_type(cur_data(), "white", bread_roll_type_columns, bread_roll_intake_columns),
         bread_roll_mixed.mean = calc_mean_by_type(cur_data(), "mixed", bread_roll_type_columns, bread_roll_intake_columns),
         bread_roll_seeded.mean = calc_mean_by_type(cur_data(), "seeded", bread_roll_type_columns, bread_roll_intake_columns),
         bread_roll_others.mean = calc_mean_by_type(cur_data(), "others", bread_roll_type_columns, bread_roll_intake_columns)) %>%
  
  ungroup()

# Save the bread data
appendix <- appendixfood[,c(1, 87:106)]
write.csv(appendix, "flavonoid/processed bread data.csv", row.names = FALSE)
```

do the flavonoid and polyphenol for cereal
```{r}
appendix <- read.csv("flavonoid/processed bread data.csv")
### Select the variables into a separate dataset for flavonoid evaluation ###
diet.cereal <- data.frame(matrix(ncol = 2, nrow = nrow(demographics)))

# Select Participant ID and group (column 20) from the baseline dataset
diet.cereal[,1:2] <- demographics[, c(1,27)]

# Rename the columns to match the original variable names
names(diet.cereal) <- c("Participant.ID", "group")

# Define a function to sum the cereal values, adjust with p.24h.foods.average, and add to diet.cereal dataframe
sum.cereal.values <- function(cereal.rows, flavonoid.data, diet.cereal) {
  # Specify the column range from column 9 to column 223
  start.col <- 9
  end.col <- 101
  
  # Extract the data from the specified column range and replace NAs with 0
  flavonoid.columns <- flavonoid.data[, start.col:end.col]
  
  # Loop through each row in diet.cereal (each participant)
  for (participant in seq_len(nrow(diet.cereal))) {
    
    # Initialize an empty vector to store the sum of each column for the current participant
    summed.values <- numeric(ncol(flavonoid.columns))
    
    # Loop through each specified cereal row and add its values to the summed.values vector
    for (i in seq_along(cereal.rows)) {
      cereal.row <- cereal.rows[i]
      
      # Multiply by the corresponding p.24h.foods.average value and divide by 240 for each participant
      if (cereal.row == 106) {
        # Porridge intake and Oat crunch intake (row 106)
        summed.values <- summed.values + 
      (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Porridge.intake[participant]) *40 /100 +
       (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Oat.crunch.intake[participant]) * 30 / 100
      } else if (cereal.row == 92) {
        # Muesli.intake (row 92)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Muesli.intake[participant]) * 30 / 100
      } else if (cereal.row == 93) {
        # Bran.cereal.intake (row 93)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Bran.cereal.intake[participant]) * 30 / 100
      } else if (cereal.row == 104) {
        # Whole.wheat.cereal.intake (row 104)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Whole.wheat.cereal.intake[participant]) * 30 / 100
      } else if (cereal.row == 120) {
        # Sliced.bread, baguette, bap, bread roll -- wholemeal (row 120)
        summed.values <- summed.values + ((as.numeric(flavonoid.columns[cereal.row, ]) * appendix$sliced_wholemeal.mean[participant]) * 35 / 100 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$baguette_wholemeal.mean[participant]) * 140 / 100 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$bap_wholemeal.mean[participant]) * 45 / 100 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$bread_roll_wholemeal.mean[participant]) * 60 / 100 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$sliced_mixed.mean[participant]) * 35 / 100 *0.5 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$baguette_mixed.mean[participant]) * 140 / 100 *0.5 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$bap_mixed.mean[participant]) * 45 / 100 *0.5 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$bread_roll_mixed.mean[participant]) * 60 / 100 *0.5)* 48/64*0.9 
      } else if (cereal.row == 202) {
        # Sliced.bread, baguette, bap, bread roll -- seeded (row 202)
         summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$sliced_seeded.mean[participant]) * 35 / 100 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$baguette_seeded.mean[participant]) * 140 / 100 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$bap_seeded.mean[participant]) * 45 / 100 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$bread_roll_seeded.mean[participant]) * 60 / 100
      } else if (cereal.row == 167) {
        # Sliced.bread, baguette, bap, bread roll -- others (row 167)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$sliced_others.mean[participant]) * 35 / 100 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$baguette_others.mean[participant]) * 140 / 100 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$bap_others.mean[participant]) * 45 / 100 + (as.numeric(flavonoid.columns[cereal.row, ]) * appendix$bread_roll_others.mean[participant]) * 60 / 100
      } else if (cereal.row == 884) {
        # Naan bread intake (row 884)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Naan.bread.intake[participant]) * 140 / 100 
      } else if (cereal.row == 164) {
        # Garlic bread intake (row 164)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Garlic.bread.intake[participant]) * 35 / 100 
      } else if (cereal.row == 166) {
        # Crispbread intake (row 166)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Crispbread.intake[participant]) * 8 / 100 
      } else if (cereal.row == 134) {
        # Oatcakes intake (row 134)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Oatcakes.intake[participant]) * 12 / 100 
      } else if (cereal.row == 153) {
        # Other bread intake -- tortilla wraps,corn (row 153)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Other.bread.intake[participant]) * 60 / 100
      } else if (cereal.row == 217) {
        # White pasta intake (row 217)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$White.pasta.intake[participant]) * 180 / 100
      } else if (cereal.row == 135) {
        # Wholemeal pasta intake (row 135)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Wholemeal.pasta.intake[participant]) * 180 / 100
      } else if (cereal.row == 196) {
        # Brown rice intake (row 196)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Brown.rice.intake[participant]) * 180 / 100
      } else if (cereal.row == 180) {
        # Snackpot intake (row 180)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Snackpot.intake[participant]) * 65 / 100
      } else if (cereal.row == 128) {
        # Couscous intake (row 128)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Couscous.intake[participant]) * 150 / 100
      } else if (cereal.row == 203) {
        # Other grain intake (row 203)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[cereal.row, ]) * p.24h.foods.average$Other.grain.intake[participant]) * 180 / 100
      }
    }
    
    # Add the resulting summed values for this participant as a new row in the diet.cereal dataframe
    # Column names will correspond to the column names in flavonoid_data
    for (i in seq_along(colnames(flavonoid.columns))) {
      col.name <- colnames(flavonoid.columns)[i]
      diet.cereal[participant, col.name] <- summed.values[i]
    }
  }
  
  return(diet.cereal)
}

# Define the cereal rows (adjust based on the actual rows you want to sum)
cereal.rows <- c(106, 92, 93, 104, 120, 202, 167, 884, 164, 166, 133, 153, 217, 135, 196, 180, 128)

# Call the function to calculate and update the diet.cereal dataframe, incorporating p.24h.foods.average adjustments
diet.cereal <- sum.cereal.values(cereal.rows, flavonoid.checkout, diet.cereal)

write.csv(diet.cereal, "flavonoid/diet.cereal.csv", row.names = FALSE)
```

tableone to describe
```{r}
# anthocyanins
diet.cereal$anthocyanins.cereal <- diet.cereal$Cyanidin + diet.cereal$Delphinidin + diet.cereal$Malvidin + diet.cereal$Pelargonidin + diet.cereal$Petunidin + diet.cereal$Peonidin

# flavanones 
diet.cereal$flavanones.cereal <- diet.cereal$Eriodictyol + diet.cereal$Hesperetin + diet.cereal$Naringenin

# flavan-3-ols # add for Epigallocatechin Gallocatechin Catechin.3.O.gallate Epicatechin.3.O.gallate Epigallocatechin.3.O.gallate
diet.cereal$flavan.3.ols.cereal <- diet.cereal$X....Catechin + diet.cereal$X....Epicatechin + diet.cereal$X....Epigallocatechin + diet.cereal$X....Gallocatechin + diet.cereal$X....Catechin.3.O.gallate + diet.cereal$X....Epicatechin.3.O.gallate + diet.cereal$X....Gallocatechin.3.O.gallate +  diet.cereal$X....Epigallocatechin.3.O.gallate

# flavonols # add for jaceidin, patuletin, spinacetin
diet.cereal$flavonols.cereal <- diet.cereal$Quercetin + diet.cereal$Kaempferol + diet.cereal$Myricetin + diet.cereal$Isorhamnetin

# flavones
diet.cereal$flavones.cereal <- diet.cereal$Luteolin + diet.cereal$Apigenin

# polymers (including proanthocyanidins [excluding monomers], theaflavins, and thearubigins), proanthocyanidins (dimers, trimers, 4–6mers, 7–10mers, polymers, and monomers). 
diet.cereal$polymers.cereal <-  diet.cereal$X02.mers + diet.cereal$X03.mers + diet.cereal$X04.06.mers + diet.cereal$X07.10.mers + diet.cereal$Polymers...10.mers.

# Proanthocyanidins
diet.cereal$proanthocyanidins.cereal <- diet.cereal$Theaflavin + diet.cereal$Thearubigins

# total flavonoid
diet.cereal$total.flavonoid.cereal <- diet.cereal$anthocyanins.cereal + diet.cereal$flavanones.cereal + diet.cereal$flavan.3.ols.cereal + diet.cereal$flavonols.cereal + diet.cereal$flavones + diet.cereal$polymers.cereal + diet.cereal$proanthocyanidins.cereal

# Set the 'group' column as a factor with specified levels: 'psoriasis' and 'non-psoriasis'
diet.cereal$group <- factor(diet.cereal$group, levels = c("psoriasis", "non-psoriasis"))

# Create a descriptive table for the tea variables (columns 3 to 217) stratified by the 'group'
vars <- names(diet.cereal)[96:103]  # Selecting the variable names from column 3 to 217
description.cereal <- CreateTableOne(data = diet.cereal,
                                  vars = vars,  # Variable names extracted above
                                  strata = "group")  # Stratified by 'group' column

# Print the description table without quotes, without spaces, and without printing to the console
print(description.cereal, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
description.cereal


# Save the descriptive table results to a CSV file
write.csv(print(description.cereal), "flavonoid/cerealresult.csv")
```



# fruit
Stewed fruit intake 80g
 → Apples, cooking, stewed with sugar, flesh only -- row 348
Prune intake → Plum, prune -- row 298 1handful 30g
Dried fruit intake → Dried mixed fruit -- row 366 30g
Mixed fruit intake → Fruit salad, (peach and pear and apricot and pineapple and cherry), canned, heavy syrup, solids and liquids -- row 304 80g
Apple intake → Apple [Dessert], eating apple, whole -- row 252 80g
Banana intake → Banana, raw -- row 300 80g
Berry intake 
→ Mixed berry -- row 354 80g
Cherry intake → Sweet cherry, raw -- row 346 1handful 80g
Grapefruit intake → Grapefruit, raw -- row 369 1serving 80g
https://www.fruitnet.com/fresh-produce-journal/when-why-and-where-uk-eats-its-grapes/135392.article
Grape intake 80g
 → Grape [Black] -- row 377 32%
 → Grape [Green] -- row 378 68%
Mango intake → Mango -- row 307 80g
Melon intake → Melons, cantaloupe, raw -- row 311 1serving 80g
Orange intake → Orange [Blond] -- row 372 80g
Satsuma intake → Tangerine -- row 373 80g
Peach/Nectarine intake → Peach, whole -- row 340 80g
Pear intake → Pear, whole -- row 255 80g
Pineapple intake → Pineapple, raw -- row 319 80g
Plum intake → Plum, fresh -- row 344 40g
Other fruit intake 80g
 → Pomegranate -- row 321
 → Kiwi -- row 305


```{r}
rm(diet.vegan)
### Select the variables into a separate dataset for flavonoid evaluation ###
diet.fruit <- data.frame(matrix(ncol = 2, nrow = nrow(demographics)))

# Select Participant ID and group (column 20) from the baseline dataset
diet.fruit[,1:2] <- demographics[, c(1,27)]

# Rename the columns to match the original variable names
names(diet.fruit) <- c("Participant.ID", "group")

# Define a function to sum the fruit values, adjust with p.24h.foods.average, and add to diet.fruit dataframe
sum.fruit.values <- function(fruit.rows, flavonoid.data, diet.fruit) {
  # Specify the column range from column 9 to column 223
  start.col <- 9
  end.col <- 101
  
  # Extract the data from the specified column range and replace NAs with 0
  flavonoid.columns <- flavonoid.data[, start.col:end.col]
  
  # Loop through each row in diet.fruit (each participant)
  for (participant in seq_len(nrow(diet.fruit))) {
    
    # Initialize an empty vector to store the sum of each column for the current participant
    summed.values <- numeric(ncol(flavonoid.columns))
    
    # Loop through each specified fruit row and add its values to the summed.values vector
    for (i in seq_along(fruit.rows)) {
      fruit.row <- fruit.rows[i]
      
      # Multiply by the corresponding p.24h.foods.average value and divide by 240 for each participant
      if (fruit.row == 348) {
        # Stewed fruit intake - Apples (row 348)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Stewed.fruit.intake[participant]) * 80 / 100
      } else if (fruit.row == 298) {
        # Prune intake (row 298)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Prune.intake[participant]) * 30 / 100
      } else if (fruit.row == 366) {
        # Dried fruit intake (row 366)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Dried.fruit.intake[participant]) * 30 / 100
      } else if (fruit.row == 304) {
        # Mixed fruit intake (row 304)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Mixed.fruit.intake[participant]) * 80 / 100
      } else if (fruit.row == 252) {
        # Apple intake (row 252)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Apple.intake[participant]) * 80 / 100
      } else if (fruit.row == 300) {
        # Banana intake (row 300)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Banana.intake[participant]) * 80 / 100
      } else if (fruit.row == 354) {
        # berry intake (row 354)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Berry.intake[participant]) * 80 / 100
      } else if (fruit.row == 346) {
        # Cherry intake (row 346)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Cherry.intake[participant]) * 80 / 100
      } else if (fruit.row == 369) {
        # Grapefruit intake (row 369)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Grapefruit.intake[participant]) * 80 / 100
      } else if (fruit.row == 377) {
        # Grape intake - black (row 377)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Grape.intake[participant]) * 80 / 100 *0.32
      } else if (fruit.row == 378) {
        # Grape intake - green (row 378)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Grape.intake[participant]) * 80 / 100 *0.68
      } else if (fruit.row == 307) {
        # Mango intake (row 307)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Mango.intake[participant]) * 80 / 100
      } else if (fruit.row == 311) {
        # Melon intake (row 311)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Melon.intake[participant]) * 80 / 100
      } else if (fruit.row == 372) {
        # Orange intake (row 372)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Orange.intake[participant]) * 80 / 100
      } else if (fruit.row == 373) {
        # Tangerine intake (row 373)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Satsuma.intake[participant]) * 80 / 100
      } else if (fruit.row == 340) {
        # Peach intake (row 340)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Peach.nectarine.intake[participant]) * 80 / 100
      } else if (fruit.row == 255) {
        # Pear intake (row 255)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Pear.intake[participant]) * 80 / 100
      } else if (fruit.row == 319) {
        # Pineapple intake (row 319)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Pineapple.intake[participant]) * 80 / 100
      } else if (fruit.row == 344) {
        # Plum intake (row 344)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Plum.intake[participant]) * 40 / 100
      } else if (fruit.row == 321) {
        # Other fruit intake - pomegranate (row 321)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Other.fruit.intake[participant]) * 80 / 100 *0.5
      } else if (fruit.row == 305) {
        # Other fruit intake - kiwi (row 305)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[fruit.row, ]) * p.24h.foods.average$Other.fruit.intake[participant]) * 80 / 100 *0.5
      }
    }
    
    # Add the resulting summed values for this participant as a new row in the diet.fruit dataframe
    # Column names will correspond to the column names in flavonoid_data
    for (i in seq_along(colnames(flavonoid.columns))) {
      col.name <- colnames(flavonoid.columns)[i]
      diet.fruit[participant, col.name] <- summed.values[i]
    }
  }
  
  return(diet.fruit)
}

# Define the fruit rows (adjust based on the actual rows you want to sum)
fruit.rows <- c(348, 298, 366, 304, 252, 300, 354, 346, 369, 377, 378, 307, 311, 372, 373, 340, 255, 319, 344, 321, 305)

# Call the function to calculate and update the diet.fruit dataframe, incorporating p.24h.foods.average adjustments
diet.fruit <- sum.fruit.values(fruit.rows, flavonoid.checkout, diet.fruit)

write.csv(diet.fruit, "flavonoid/diet.fruit.csv", row.names = FALSE)
```

tableone to describe
```{r}
# anthocyanins
diet.fruit$anthocyanins.fruit <- diet.fruit$Cyanidin + diet.fruit$Delphinidin + diet.fruit$Malvidin + diet.fruit$Pelargonidin + diet.fruit$Petunidin + diet.fruit$Peonidin

# flavanones 
diet.fruit$flavanones.fruit <- diet.fruit$Eriodictyol + diet.fruit$Hesperetin + diet.fruit$Naringenin

# flavan-3-ols # add for Epigallocatechin Gallocatechin Catechin.3.O.gallate Epicatechin.3.O.gallate Epigallocatechin.3.O.gallate
diet.fruit$flavan.3.ols.fruit <- diet.fruit$X....Catechin + diet.fruit$X....Epicatechin + diet.fruit$X....Epigallocatechin + diet.fruit$X....Gallocatechin + diet.fruit$X....Catechin.3.O.gallate + diet.fruit$X....Epicatechin.3.O.gallate + diet.fruit$X....Gallocatechin.3.O.gallate +  diet.fruit$X....Epigallocatechin.3.O.gallate

# flavonols # add for jaceidin, patuletin, spinacetin
diet.fruit$flavonols.fruit <- diet.fruit$Quercetin + diet.fruit$Kaempferol + diet.fruit$Myricetin + diet.fruit$Isorhamnetin

# flavones
diet.fruit$flavones.fruit <- diet.fruit$Luteolin + diet.fruit$Apigenin

# polymers (including proanthocyanidins [excluding monomers], theaflavins, and thearubigins), proanthocyanidins (dimers, trimers, 4–6mers, 7–10mers, polymers, and monomers). 
diet.fruit$polymers.fruit <-  diet.fruit$X02.mers + diet.fruit$X03.mers + diet.fruit$X04.06.mers + diet.fruit$X07.10.mers + diet.fruit$Polymers...10.mers.

# Proanthocyanidins
diet.fruit$proanthocyanidins.fruit <- diet.fruit$Theaflavin + diet.fruit$Thearubigins

# total flavonoid
diet.fruit$total.flavonoid.fruit <- diet.fruit$anthocyanins.fruit + diet.fruit$flavanones.fruit + diet.fruit$flavan.3.ols.fruit + diet.fruit$flavonols.fruit + diet.fruit$flavones + diet.fruit$polymers.fruit + diet.fruit$proanthocyanidins.fruit

# Set the 'group' column as a factor with specified levels: 'psoriasis' and 'non-psoriasis'
diet.fruit$group <- factor(diet.fruit$group, levels = c("psoriasis", "non-psoriasis"))

# Create a descriptive table for the tea variables (columns 3 to 217) stratified by the 'group'
vars <- names(diet.fruit)[96:103]  # Selecting the variable names from column 3 to 217
description.fruit <- CreateTableOne(data = diet.fruit,
                                  vars = vars,  # Variable names extracted above
                                  strata = "group")  # Stratified by 'group' column

# Print the description table without quotes, without spaces, and without printing to the console
print(description.fruit, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
description.fruit

# Save the descriptive table results to a CSV file
write.csv(print(description.fruit), "flavonoid/fruitresult.csv")
```


# vegetables
Fried potatoes intake → potato, fried -- row 578 1 serving 180g
Boiled/baked potatoes intake → New potatoes, in skins, boiled in unsalted water -- row 572 1 serving 180g
Mashed potato intake → Old potatoes, mashed with butter -- row 576 1 serving 180g
Mixed vegetable intake → Mixed vegetables, frozen, boiled in salted water -- row 614 1 serving 80g
Vegetable pieces intake → Mixed vegetables, stir-fry type, frozen, fried in blenden oil -- row 615 1 serving 80g
Coleslaw intake → coleslaw -- row 623 1 serving 80g
Side salad intake → Salad, mixed, with olive oil dressing -- row 667 1 serving 80g
Avocado intake → Avocado, raw -- row 379 1 medium 160g
Green bean intake → Green beans, raw -- row 610 1 serving 80g  boiling 0.93
Beetroot intake → Beetroot, boiled in salted water -- row 587 1 serving 80g
Broccoli intake → Broccoli, green, boiled in salted water -- row 505 1 serving 80g
Butternut squash intake → Squash, butternut, baked -- row 565 1 serving 80g
Cabbage/kale intake  --- not find proportion, assume 50:50 1 serving 80g
→ Cabbage, boiled in unsalted water, average -- row 503
→ Curly kale, boiled in salted water -- row 500
Carrot intake → Carrots, boiled in unsalted water -- row 592 1 serving 80g
Cauliflower intake → Cauliflower, boiled in un salted water -- row 499 1 serving 80g
Celery intake → Celery stalks, fresh, raw -- row 465 1 stick 26.7g
Courgette intake → Courgette, boiled in unsalted water -- row 559 1 serving 80g
Cucumber intake → Cucumber, raw -- row 467 1 inch 32g
Garlic intake → Garlic, fresh, raw -- row 419 1 clove 5g
Leek intake → Leeks, boiled in salted water -- row 522 1 serving 80g
Lettuce intake → Lettuce [Green], raw -- row 702 1 serving 80g
Mushroom intake → •	Mushrooms, fried -- row 712 1 serving 80g
Onion intake → Onions, boiled in unsalted water -- row 521 1 serving 80g
Parsnip intake → Parsnip, boiled in unsalted water -- row 586 1 serving 80g
Sweet pepper intake → Peppers, mixed, stir fried in olive oil -- row 397 1 pepper 80g
Spinach intake 1 serving 80g
→ Spinach, boiled in salted water -- row 513
→ Spinach, raw -- row 706
Sprouts intake → Brussels sprouts, boiled in unsalted water -- row 507 1 serving 80g
Sweetcorn intake → Corn, sweet, yellow, steamed -- row 139 1 serving 80g
Sweet potato intake → Sweet potato, baked -- row 571 1 serving  130g (range between 100 to 150)
Fresh tomato intake → Tomatoes, whole, raw -- row 392 1 medium 80g
Tinned tomato intake → Tomatoes, red, ripe, canned, packed in tomato juice -- row 390  1 serving 200g
Turnip/swede intake --- not find proportion, assume 50:50 1 serving 80g
→ Turnip, boiled in unsalted water -- row 597
→ Swede, boiled in unsalted water -- row 589
Watercress intake → Watercress, raw -- row 695 1 serving 80g
https://www.bda.uk.com/food-health/your-health/sustainable-diets/seasonal-fruit-and-veg-a-handy-guide.html
https://www.waitrose.com/ecom/recipe/aubergine-and-butternut-squash-bake
https://www.diabetes.org.uk/guide-to-diabetes/enjoy-food/cooking-for-people-with-diabetes/seasonal-cooking/winter-fruit-and-veg
Other vegetables intake  1 serving 80g
→ Asparagus, boiled in salted water -- row 564   40%
→ Aubergine, fried in blended oil -- row 394    30%
→ Squash, Spaghetti, baked -- row 566    30%

```{r}
rm(diet.fruit)
### Select the variables into a separate dataset for flavonoid evaluation ###
diet.vegetable <- data.frame(matrix(ncol = 2, nrow = nrow(demographics)))

# Select Participant ID and group (column 20) from the baseline dataset
diet.vegetable[,1:2] <- demographics[, c(1,27)]

# Rename the columns to match the original variable names
names(diet.vegetable) <- c("Participant.ID", "group")

# Define a function to sum the vegetable values, adjust with p.24h.foods.average, and add to diet.vegetable dataframe
sum.vegetable.values <- function(vegetable.rows, flavonoid.data, diet.vegetable) {
  # Specify the column range from column 9 to column 223
  start.col <- 9
  end.col <- 101
  
  # Extract the data from the specified column range and replace NAs with 0
  flavonoid.columns <- flavonoid.data[, start.col:end.col]
  
  # Loop through each row in diet.vegetable (each participant)
  for (participant in seq_len(nrow(diet.vegetable))) {
    
    # Initialize an empty vector to store the sum of each column for the current participant
    summed.values <- numeric(ncol(flavonoid.columns))
    
    # Loop through each specified vegetable row and add its values to the summed.values vector
    for (i in seq_along(vegetable.rows)) {
      vegetable.row <- vegetable.rows[i]
      
      # Multiply by the corresponding p.24h.foods.average value and divide by 240 for each participant
      if (vegetable.row == 578) {
        # Fried potatoes intake (row 578)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Fried.potatoes.intake[participant]) * 180 / 100
      } else if (vegetable.row == 572) {
        # Boiled/baked potatoes intake (row 572)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Boiled.baked.potatoes.intake[participant]) * 180 / 100
      } else if (vegetable.row == 576) {
        # Mashed potatoes intake (row 576)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Mashed.potato.intake[participant]) * 180 / 100
      } else if (vegetable.row == 614) {
        # Mixed vegetable intake (row 614)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Mixed.vegetable.intake[participant]) * 80 / 100
      } else if (vegetable.row == 615) {
        # Vegetable pieces intake (row 615)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Vegetable.pieces.intake[participant]) * 80 / 100
      } else if (vegetable.row == 623) {
        # Coleslaw intake (row 623)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Coleslaw.intake[participant]) * 80 / 100
      } else if (vegetable.row == 667) {
        # Side salad intake (row 667)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Side.salad.intake[participant]) * 80 / 100
      } else if (vegetable.row == 379) {
        # Avocado intake (row 379)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Avocado.intake[participant]) * 160 / 100
      } else if (vegetable.row == 610) {
        # Green bean intake (row 610)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Green.bean.intake[participant]) * 80 / 100 * 0.93
      } else if (vegetable.row == 587) {
        # Beetroot intake (row 587)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Beetroot.intake[participant]) * 80 / 100
      } else if (vegetable.row == 505) {
        # Broccoli intake (row 505)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Broccoli.intake[participant]) * 80 / 100
      } else if (vegetable.row == 565) {
        # Butternut squash intake (row 565)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Butternut.squash.intake[participant]) * 80 / 100
      } else if (vegetable.row == 503) {
        # Cabbage intake (row 503)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Cabbage.kale.intake[participant]) * 80 / 100 *0.5
      } else if (vegetable.row == 500) {
        # Kale intake (row 500)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Cabbage.kale.intake[participant]) * 80 / 100 *0.5
      } else if (vegetable.row == 592) {
        # Carrot intake (row 592)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Carrot.intake[participant]) * 80 / 100
      } else if (vegetable.row == 499) {
        # Cauliflower intake (row 499)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Cauliflower.intake[participant]) * 80 / 100
      } else if (vegetable.row == 465) {
        # Celery intake (row 465)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Celery.intake[participant]) * 26.7 / 100
      } else if (vegetable.row == 559) {
        # Courgette intake (row 559)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Courgette.intake[participant]) * 80 / 100
      } else if (vegetable.row == 467) {
        # Cucumber intake (row 467)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Cucumber.intake[participant]) * 32 / 100
      } else if (vegetable.row == 419) {
        # Garlic intake (row 419)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Garlic.intake[participant]) * 5 / 100
      } else if (vegetable.row == 522) {
        # Leek intake (row 522)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Leek.intake[participant]) * 80 / 100
      } else if (vegetable.row == 702) {
        # Lettuce intake (row 702)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Lettuce.intake[participant]) * 80 / 100
      } else if (vegetable.row == 712) {
        # Mushroom intake (row 712)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Mushroom.intake[participant]) * 80 / 100
      } else if (vegetable.row == 521) {
        # Onion intake (row 521)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Onion.intake[participant]) * 80 / 100
      } else if (vegetable.row == 586) {
        # Parsnip intake (row 586)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Parsnip.intake[participant]) * 80 / 100
      } else if (vegetable.row == 397) {
        # Sweet pepper intake (row 397)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Sweet.pepper.intake[participant]) * 80 / 100
      } else if (vegetable.row == 513) {
        # Spinach intake - cooked (row 513)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Spinach.intake[participant]) * 80 / 100 *0.5
      } else if (vegetable.row == 706) {
        # Spinach intake - raw (row 706)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Spinach.intake[participant]) * 80 / 100 *0.5
      } else if (vegetable.row == 507) {
        # Sprouts intake (row 507)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Sprouts.intake[participant]) * 80 / 100
      } else if (vegetable.row == 139) {
        # Sweetcorn intake (row 139)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Sweetcorn.intake[participant]) * 80 / 100
      } else if (vegetable.row == 571) {
        # Sweet potato intake (row 571)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Sweet.potato.intake[participant]) * 130 / 100
      } else if (vegetable.row == 392) {
        # Fresh tomato intake (row 392)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Fresh.tomato.intake[participant]) * 80 / 100
      } else if (vegetable.row == 390) {
        # Tinned tomato intake (row 390)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Tinned.tomato.intake[participant]) * 200 / 100
      } else if (vegetable.row == 597) {
        # Turnip intake (row 597)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Turnip.swede.intake[participant]) * 80 / 100 *0.5
      } else if (vegetable.row == 589) {
        # Swede intake (row 589)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Turnip.swede.intake[participant]) * 80 / 100 *0.5
      } else if (vegetable.row == 695) {
        # Watercress intake (row 695)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Turnip.swede.intake[participant]) * 80 / 100
      } else if (vegetable.row == 564) {
        # Other vegetables intake - asparagus (row 564)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Other.vegetables.intake[participant]) * 80 / 100 *0.4
      } else if (vegetable.row == 394) {
        # Other vegetables intake - aubergine (row 394)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Other.vegetables.intake[participant]) * 80 / 100 *0.3
      } else if (vegetable.row == 566) {
        # Other vegetables intake - squash (row 565)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Other.vegetables.intake[participant]) * 80 / 100 *0.3
      } else if (vegetable.row == 847) {
        # Olives Intake - Black (row 847)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Olives.intake[participant]) * 50 / 100 *0.5
      } else if (vegetable.row == 848) {
        # Olives Intake - Green (row 848)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[vegetable.row, ]) * p.24h.foods.average$Olives.intake[participant]) * 50 / 100 *0.5
      }
    }
    
    # Add the resulting summed values for this participant as a new row in the diet.vegetable dataframe
    # Column names will correspond to the column names in flavonoid_data
    for (i in seq_along(colnames(flavonoid.columns))) {
      col.name <- colnames(flavonoid.columns)[i]
      diet.vegetable[participant, col.name] <- summed.values[i]
    }
  }
  
  return(diet.vegetable)
}

# Define the vegetable rows (adjust based on the actual rows you want to sum)
vegetable.rows <- c(578, 572, 576, 614, 615, 623, 667, 379, 610, 587, 505, 565, 503, 500, 592, 499, 465, 559, 467, 419, 522, 702, 712, 521, 586, 397, 513, 706, 507, 139, 571, 392, 390, 597, 589, 695, 564, 394, 566, 847, 848)

# Call the function to calculate and update the diet.vegetable dataframe, incorporating p.24h.foods.average adjustments
diet.vegetable <- sum.vegetable.values(vegetable.rows, flavonoid.checkout, diet.vegetable)

write.csv(diet.vegetable, "flavonoid/diet.vegetable.csv", row.names = FALSE)

```

tableone to describe
```{r}
# anthocyanins
diet.vegetable$anthocyanins.vegetable <- diet.vegetable$Cyanidin + diet.vegetable$Delphinidin + diet.vegetable$Malvidin + diet.vegetable$Pelargonidin + diet.vegetable$Petunidin + diet.vegetable$Peonidin

# flavanones 
diet.vegetable$flavanones.vegetable <- diet.vegetable$Eriodictyol + diet.vegetable$Hesperetin + diet.vegetable$Naringenin

# flavan-3-ols # add for Epigallocatechin Gallocatechin Catechin.3.O.gallate Epicatechin.3.O.gallate Epigallocatechin.3.O.gallate
diet.vegetable$flavan.3.ols.vegetable <- diet.vegetable$X....Catechin + diet.vegetable$X....Epicatechin + diet.vegetable$X....Epigallocatechin + diet.vegetable$X....Gallocatechin + diet.vegetable$X....Catechin.3.O.gallate + diet.vegetable$X....Epicatechin.3.O.gallate + diet.vegetable$X....Epigallocatechin.3.O.gallate

# flavonols # add for jaceidin, patuletin, spinacetin
diet.vegetable$flavonols.vegetable <- diet.vegetable$Quercetin + diet.vegetable$Kaempferol + diet.vegetable$Myricetin + diet.vegetable$Isorhamnetin

# flavones
diet.vegetable$flavones.vegetable <- diet.vegetable$Luteolin + diet.vegetable$Apigenin

# polymers (including proanthocyanidins [excluding monomers], theaflavins, and thearubigins), proanthocyanidins (dimers, trimers, 4–6mers, 7–10mers, polymers, and monomers). 
diet.vegetable$polymers.vegetable <- diet.vegetable$Theaflavin + diet.vegetable$Thearubigins + diet.vegetable$X02.mers + diet.vegetable$X03.mers + diet.vegetable$X04.06.mers + diet.vegetable$X07.10.mers + diet.vegetable$Polymers...10.mers.

# Proanthocyanidins
diet.vegetable$proanthocyanidins.vegetable <- diet.vegetable$X....Catechin + diet.vegetable$X....Epicatechin + diet.vegetable$X....Epigallocatechin + diet.vegetable$X....Gallocatechin + diet.vegetable$X....Catechin.3.O.gallate + diet.vegetable$X....Epicatechin.3.O.gallate + diet.vegetable$X....Epigallocatechin.3.O.gallate + diet.vegetable$X02.mers + diet.vegetable$X03.mers + diet.vegetable$X04.06.mers + diet.vegetable$X07.10.mers + diet.vegetable$Polymers...10.mers.

diet.vegetable$total.flavonoid.vegetable <- diet.vegetable$anthocyanins + diet.vegetable$flavanones + diet.vegetable$flavan.3.ols + diet.vegetable$flavonols + diet.vegetable$flavones + diet.vegetable$polymers

diet.vegetable <- merge(diet.vegetable,dietaryscorewithquartile[, c(1,10)], by = "Participant.ID")# Set the 'group'
# Set the 'group' column as a factor with specified levels: 'psoriasis' and 'non-psoriasis'
diet.vegetable$group <- factor(diet.vegetable$group, levels = c("psoriasis", "non-psoriasis"))

# Create a descriptive table for the vegetable variables (columns 3 to 217) stratified by the 'group'
vars <- names(diet.vegetable)[96:103]  # Selecting the variable names from column 3 to 217
description.vegetable <- CreateTableOne(data = diet.vegetable,
                                  vars = vars,  # Variable names extracted above
                                  strata = "group")  # Stratified by 'group' column

# Print the description table without quotes, without spaces, and without printing to the console
print(description.vegetable, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
description.vegetable

# Save the descriptive table results to a CSV file
write.csv(print(description.vegetable), "flavonoid/vegetableresult.csv")
```



# legumes
Baked bean intake → Beans, baked, canned, plain or vegetarian -- no flavonoid
https://assets.kpmg.com/content/dam/kpmg/uk/pdf/2024/07/uk-consumer-pulse-snapshot-july-2024.pdf
https://www.ons.gov.uk/economy/nationalaccounts/satelliteaccounts/bulletins/consumertrends/previousReleases
https://link.springer.com/chapter/10.1007/978-3-030-12763-3_2
Pulses intake 1 serving 150g
→ Beans, kidney, all types, mature seeds, cooked, boiled, without salt -- row 433 20%
→ Chickpeas (garbanzo beans, bengal gram), mature seeds, cooked, boiled, without salt -- row 439 30%
→ Lima beans, Butter beans, mature seeds, cooked, boiled, drained, without salt -- row 458 10%
→ Lentils, red, split, dried, boiled in unsalted water – row 527 25%
→ Cannellini beans, dried, cooked in unsalted water – row 544 10%
→ Beans, pinto,mature seeds, raw – row 541 5%
Broad bean intake → Broad beans, frozen, boiled in unsalted water -- row 626 1 serving 150g
Pea intake → Peas, boiled in unsalted water -- row 529 1 serving 80g

```{r}
rm(diet.snack)
### Select the variables into a separate dataset for flavonoid evaluation ###
diet.legume <- data.frame(matrix(ncol = 2, nrow = nrow(demographics)))

# Select Participant ID and group (column 20) from the baseline dataset
diet.legume[,1:2] <- demographics[, c(1,27)]

# Rename the columns to match the original variable names
names(diet.legume) <- c("Participant.ID", "group")

# Define a function to sum the legume values, adjust with p.24h.foods.average, and add to diet.legume dataframe
sum.legume.values <- function(legume.rows, flavonoid.data, diet.legume) {
  # Specify the column range from column 9 to column 223
  start.col <- 9
  end.col <- 101
  
  # Extract the data from the specified column range and replace NAs with 0
  flavonoid.columns <- flavonoid.data[, start.col:end.col]
  
  # Loop through each row in diet.legume (each participant)
  for (participant in seq_len(nrow(diet.legume))) {
    
    # Initialize an empty vector to store the sum of each column for the current participant
    summed.values <- numeric(ncol(flavonoid.columns))
    
    # Loop through each specified legume row and add its values to the summed.values vector
    for (i in seq_along(legume.rows)) {
      legume.row <- legume.rows[i]
      
      # Multiply by the corresponding p.24h.foods.average value and divide by 240 for each participant
      if (legume.row == 433) {
        # Pulse intake -Beans, kidney, all types, mature seeds, cooked, boiled, without salt (row 433)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[legume.row, ]) * p.24h.foods.average$Pulses.intake[participant]) * 150 / 100 *0.20
      } else if (legume.row == 439) {
        # Pulse intake -Chickpeas (garbanzo beans, bengal gram), mature seeds, cooked, boiled, without salt (row 439)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[legume.row, ]) * p.24h.foods.average$Pulses.intake[participant]) * 150 / 100 *0.30
      } else if (legume.row == 458) {
        # Pulse intake -Lima beans, Butter beans, mature seeds, cooked, boiled, drained, without salt (row 458)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[legume.row, ]) * p.24h.foods.average$Pulses.intake[participant]) * 150 / 100 *0.10
      } else if (legume.row == 527) {
        # Pulse intake -Lentils, red, split, dried, boiled in unsalted water (row 527)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[legume.row, ]) * p.24h.foods.average$Pulses.intake[participant]) * 150 / 100 *0.25
      } else if (legume.row == 544) {
        # Pulse intake -Cannellini beans, dried, cooked in unsalted water (row 544)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[legume.row, ]) * p.24h.foods.average$Pulses.intake[participant]) * 150 / 100 *0.10
      } else if (legume.row == 541) {
        # Pulse intake -Beans, pinto, dried, boiled in unsalted water (row 541)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[legume.row, ]) * p.24h.foods.average$Pulses.intake[participant]) * 150 / 100 *0.05
      } else if (legume.row == 626) {
        # Broad bean intake (row 626)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[legume.row, ]) * p.24h.foods.average$Broad.bean.intake[participant]) * 150 / 100
      } else if (legume.row == 529) {
        # Pea intake (row 529)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[legume.row, ]) * p.24h.foods.average$Pea.intake[participant]) * 80 / 100
      }
    }
    
    # Add the resulting summed values for this participant as a new row in the diet.legume dataframe
    # Column names will correspond to the column names in flavonoid_data
    for (i in seq_along(colnames(flavonoid.columns))) {
      col.name <- colnames(flavonoid.columns)[i]
      diet.legume[participant, col.name] <- summed.values[i]
    }
  }
  
  return(diet.legume)
}

# Define the legume rows (adjust based on the actual rows you want to sum)
legume.rows <- c(433, 439, 458, 527, 544, 541, 626, 529)

# Call the function to calculate and update the diet.legume dataframe, incorporating p.24h.foods.average adjustments
diet.legume <- sum.legume.values(legume.rows, flavonoid.checkout, diet.legume)

write.csv(diet.legume, "flavonoid/diet.legume.csv", row.names = FALSE)
```

tableone to describe
```{r}
# anthocyanins
diet.legume$anthocyanins.legume <- diet.legume$Cyanidin + diet.legume$Delphinidin + diet.legume$Malvidin + diet.legume$Pelargonidin + diet.legume$Petunidin + diet.legume$Peonidin

# flavanones 
diet.legume$flavanones.legume <- diet.legume$Eriodictyol + diet.legume$Hesperetin + diet.legume$Naringenin

# flavan-3-ols # add for Epigallocatechin Gallocatechin Catechin.3.O.gallate Epicatechin.3.O.gallate Epigallocatechin.3.O.gallate
diet.legume$flavan.3.ols.legume <- diet.legume$X....Catechin + diet.legume$X....Epicatechin + diet.legume$X....Epigallocatechin + diet.legume$X....Gallocatechin + diet.legume$X....Catechin.3.O.gallate + diet.legume$X....Epicatechin.3.O.gallate + diet.legume$X....Gallocatechin.3.O.gallate +  diet.legume$X....Epigallocatechin.3.O.gallate

# flavonols # add for jaceidin, patuletin, spinacetin
diet.legume$flavonols.legume <- diet.legume$Quercetin + diet.legume$Kaempferol + diet.legume$Myricetin + diet.legume$Isorhamnetin

# flavones
diet.legume$flavones.legume <- diet.legume$Luteolin + diet.legume$Apigenin

# polymers (including proanthocyanidins [excluding monomers], theaflavins, and thearubigins), proanthocyanidins (dimers, trimers, 4–6mers, 7–10mers, polymers, and monomers). 
diet.legume$polymers.legume <-  diet.legume$X02.mers + diet.legume$X03.mers + diet.legume$X04.06.mers + diet.legume$X07.10.mers + diet.legume$Polymers...10.mers.

# Proanthocyanidins
diet.legume$proanthocyanidins.legume <- diet.legume$Theaflavin + diet.legume$Thearubigins

# total flavonoid
diet.legume$total.flavonoid.legume <- diet.legume$anthocyanins.legume + diet.legume$flavanones.legume + diet.legume$flavan.3.ols.legume + diet.legume$flavonols.legume + diet.legume$flavones + diet.legume$polymers.legume + diet.legume$proanthocyanidins.legume

# Set the 'group' column as a factor with specified levels: 'psoriasis' and 'non-psoriasis'
diet.legume$group <- factor(diet.legume$group, levels = c("psoriasis", "non-psoriasis"))

# Create a descriptive table for the tea variables (columns 3 to 217) stratified by the 'group'
vars <- names(diet.legume)[96:103]  # Selecting the variable names from column 3 to 217
description.legume <- CreateTableOne(data = diet.legume,
                                  vars = vars,  # Variable names extracted above
                                  strata = "group")  # Stratified by 'group' column

# Print the description table without quotes, without spaces, and without printing to the console
print(description.legume, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
description.legume

# Save the descriptive table results to a CSV file
write.csv(print(description.legume), "flavonoid/legumeresult.csv")

```

# nuts
Salted Peanuts Intake → Peanut, dehulled, roasted -- no flavonoid 
Unsalted Peanuts Intake → Peanut, dehulled, roasted -- no flavonoid 
https://inc.nutfruit.org/wp-content/uploads/2023/05/Statistical-Yearbook-2022-2023.pdf
Salted Nuts Intake / Unsalted Nuts Intake 1 handful 30g
•	Almonds, dry roasted, without salt added 26.59% -- row 791
•	Brazil Nuts 4.89% -- no flavonoid
•	Nuts, cashew nuts, dry roasted, without salt added 30.17% -- row 794
•	Hazelnuts 12.40% -- row 796
•	Macadamia 0.50% -- row 811
•	Pecan 3.58% -- row 805
•	Pine nuts 1.38% -- no flavonoid
•	Nuts, pistachio nuts, dry roasted, without salt added 6.05% -- row 799
•	Walnuts 14.44% -- row 809


Seeds Intake → Mixed seeds -- row 840 1 handful 20g
```{r}
rm(diet.legume)
### Select the variables into a separate dataset for flavonoid evaluation ###
diet.nut <- data.frame(matrix(ncol = 2, nrow = nrow(demographics)))

# Select Participant ID and group (column 20) from the baseline dataset
diet.nut[,1:2] <- demographics[, c(1,27)]

# Rename the columns to match the original variable names
names(diet.nut) <- c("Participant.ID", "group")

# Define a function to sum the nut values, adjust with p.24h.foods.average, and add to diet.nut dataframe
sum.nut.values <- function(nut.rows, flavonoid.data, diet.nut) {
  # Specify the column range from column 9 to column 223
  start.col <- 9
  end.col <- 101
  
  # Extract the data from the specified column range and replace NAs with 0
  flavonoid.columns <- flavonoid.data[, start.col:end.col]
  
  # Loop through each row in diet.nut (each participant)
  for (participant in seq_len(nrow(diet.nut))) {
    
    # Initialize an empty vector to store the sum of each column for the current participant
    summed.values <- numeric(ncol(flavonoid.columns))
    
    # Loop through each specified nut row and add its values to the summed.values vector
    for (i in seq_along(nut.rows)) {
      nut.row <- nut.rows[i]
      
      # Multiply by the corresponding p.24h.foods.average value and divide by 240 for each participant
      if (nut.row == 791) {
        # (UN)Salted Nuts Intake -- Almonds (row 791)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Salted.nuts.intake[participant]) * 30 / 100 *0.2659 + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Unsalted.nuts.intake[participant]) * 30 / 100 *0.2659
      } else if (nut.row == 794) {
        # (UN)Salted Nuts Intake -- Cashew (row 794)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Salted.nuts.intake[participant]) * 30 / 100 *0.3017 + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Unsalted.nuts.intake[participant]) * 30 / 100 *0.3017
      } else if (nut.row == 796) {
        # (UN)Salted Nuts Intake -- Hazelnuts (row 796)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Salted.nuts.intake[participant]) * 30 / 100 *0.1240 + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Unsalted.nuts.intake[participant]) * 30 / 100 *0.1240
      } else if (nut.row == 811) {
        # (UN)Salted Nuts Intake --	Macadamia (row 811)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Salted.nuts.intake[participant]) * 30 / 100 *0.005 + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Unsalted.nuts.intake[participant]) * 30 / 100 *0.005
      } else if (nut.row == 805) {
        # (UN)Salted Nuts Intake --	Pecan (row 805)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Salted.nuts.intake[participant]) * 30 / 100 *0.0358 + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Unsalted.nuts.intake[participant]) * 30 / 100 *0.0358
      } else if (nut.row == 799) {
        # (UN)Salted Nuts Intake --	Pistachios (row 799)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Salted.nuts.intake[participant]) * 30 / 100 *0.0605 + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Unsalted.nuts.intake[participant]) * 30 / 100 *0.0605
      } else if (nut.row == 809) {
        # (UN)Salted Nuts Intake --	Walnuts (row 809)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Salted.nuts.intake[participant]) * 30 / 100 *0.1444 + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Unsalted.nuts.intake[participant]) * 30 / 100 *0.1444
      } else if (nut.row == 840) {
        # Seeds Intake (row 840)
        summed.values <- summed.values + (as.numeric(flavonoid.columns[nut.row, ]) * p.24h.foods.average$Seeds.intake[participant]) * 20 / 100
      }
    }
    
    # Add the resulting summed values for this participant as a new row in the diet.nut dataframe
    # Column names will correspond to the column names in flavonoid_data
    for (i in seq_along(colnames(flavonoid.columns))) {
      col.name <- colnames(flavonoid.columns)[i]
      diet.nut[participant, col.name] <- summed.values[i]
    }
  }
  
  return(diet.nut)
}

# Define the nut rows (adjust based on the actual rows you want to sum)
nut.rows <- c(791, 794, 796, 811, 805, 799, 809, 840)

# Call the function to calculate and update the diet.nut dataframe, incorporating p.24h.foods.average adjustments
diet.nut <- sum.nut.values(nut.rows, flavonoid.checkout, diet.nut)

write.csv(diet.nut, "flavonoid/diet.nut.csv", row.names = FALSE)

```

tableone to describe
```{r}
# anthocyanins
diet.nut$anthocyanins.nut <- diet.nut$Cyanidin + diet.nut$Delphinidin + diet.nut$Malvidin + diet.nut$Pelargonidin + diet.nut$Petunidin + diet.nut$Peonidin

# flavanones 
diet.nut$flavanones.nut <- diet.nut$Eriodictyol + diet.nut$Hesperetin + diet.nut$Naringenin

# flavan-3-ols # add for Epigallocatechin Gallocatechin Catechin.3.O.gallate Epicatechin.3.O.gallate Epigallocatechin.3.O.gallate
diet.nut$flavan.3.ols.nut <- diet.nut$X....Catechin + diet.nut$X....Epicatechin + diet.nut$X....Epigallocatechin + diet.nut$X....Gallocatechin + diet.nut$X....Catechin.3.O.gallate + diet.nut$X....Epicatechin.3.O.gallate + diet.nut$X....Gallocatechin.3.O.gallate +  diet.nut$X....Epigallocatechin.3.O.gallate

# flavonols # add for jaceidin, patuletin, spinacetin
diet.nut$flavonols.nut <- diet.nut$Quercetin + diet.nut$Kaempferol + diet.nut$Myricetin + diet.nut$Isorhamnetin

# flavones
diet.nut$flavones.nut <- diet.nut$Luteolin + diet.nut$Apigenin

# polymers (including proanthocyanidins [excluding monomers], theaflavins, and thearubigins), proanthocyanidins (dimers, trimers, 4–6mers, 7–10mers, polymers, and monomers). 
diet.nut$polymers.nut <-  diet.nut$X02.mers + diet.nut$X03.mers + diet.nut$X04.06.mers + diet.nut$X07.10.mers + diet.nut$Polymers...10.mers.

# Proanthocyanidins
diet.nut$proanthocyanidins.nut <- diet.nut$Theaflavin + diet.nut$Thearubigins

# total flavonoid
diet.nut$total.flavonoid.nut <- diet.nut$anthocyanins.nut + diet.nut$flavanones.nut + diet.nut$flavan.3.ols.nut + diet.nut$flavonols.nut + diet.nut$flavones + diet.nut$polymers.nut + diet.nut$proanthocyanidins.nut

# Set the 'group' column as a factor with specified levels: 'psoriasis' and 'non-psoriasis'
diet.nut$group <- factor(diet.nut$group, levels = c("psoriasis", "non-psoriasis"))

# Create a descriptive table for the tea variables (columns 3 to 217) stratified by the 'group'
vars <- names(diet.nut)[96:103]  # Selecting the variable names from column 3 to 217
description.nut <- CreateTableOne(data = diet.nut,
                                  vars = vars,  # Variable names extracted above
                                  strata = "group")  # Stratified by 'group' column

# Print the description table without quotes, without spaces, and without printing to the console
print(description.nut, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
description.nut

# Save the descriptive table results to a CSV file
write.csv(print(description.nut), "flavonoid/nutresult.csv")
```



# final polyphenol
```{r}
diet.tea <- read.csv("flavonoid/diet.tea.csv")
#diet.coffee <- read.csv("flavonoid/diet.coffee.csv")
diet.chocolate <- read.csv("flavonoid/diet.chocolate.csv")
diet.alcohol <- read.csv("flavonoid/diet.alcohol.csv")
diet.juice <- read.csv("flavonoid/diet.juice.csv")
diet.cereal <- read.csv("flavonoid/diet.cereal.csv")
#diet.vegan <- read.csv("flavonoid/diet.vegan.csv")
diet.fruit <- read.csv("flavonoid/diet.fruit.csv")
diet.vegetable <- read.csv("flavonoid/diet.vegetable.csv")
diet.legume <- read.csv("flavonoid/diet.legume.csv")
#diet.snack <- read.csv("flavonoid/diet.snack.csv")
diet.nut <- read.csv("flavonoid/diet.nut.csv")
#diet.k <- read.csv("flavonoid/necessary.csv")

# Create a new dataset by keeping the first two columns from one of the datasets
final.polyphenol <- diet.tea  # Copy the structure of dataset1

# Keep the first two columns as they are from 'dataset1'
final.polyphenol[, 1:2] <- diet.tea[, 1:2]

diet.tea[, 3:95] <- replace(diet.tea[, 3:95], is.na(diet.tea[, 3:95]), 0)
diet.chocolate[, 3:95] <- replace(diet.chocolate[, 3:95], is.na(diet.chocolate[, 3:95]), 0)
diet.alcohol[, 3:95] <- replace(diet.alcohol[, 3:95], is.na(diet.alcohol[, 3:95]), 0)
diet.juice[, 3:95] <- replace(diet.juice[, 3:95], is.na(diet.juice[, 3:95]), 0)
diet.fruit[, 3:95] <- replace(diet.fruit[, 3:95], is.na(diet.fruit[, 3:95]), 0)
diet.vegetable[, 3:95] <- replace(diet.vegetable[, 3:95], is.na(diet.vegetable[, 3:95]), 0)
#diet.snack[, 3:95] <- replace(diet.snack[, 3:95], is.na(diet.snack[, 3:95]), 0)
#diet.coffee[, 3:95] <- replace(diet.coffee[, 3:95], is.na(diet.coffee[, 3:95]), 0)
diet.cereal[, 3:95] <- replace(diet.cereal[, 3:95], is.na(diet.cereal[, 3:95]), 0)
#diet.vegan[, 3:95] <- replace(diet.vegan[, 3:95], is.na(diet.vegan[, 3:95]), 0)
diet.legume[, 3:95] <- replace(diet.legume[, 3:95], is.na(diet.legume[, 3:95]), 0)
diet.nut[, 3:95] <- replace(diet.nut[, 3:95], is.na(diet.nut[, 3:95]), 0)
  
# Add the values of corresponding cells in columns 3 to 217 of both datasets
final.polyphenol[, 3:95] <- diet.tea[, 3:95] + 
                             diet.chocolate[, 3:95] + 
                             diet.alcohol[, 3:95] + 
                             diet.juice[, 3:95] + 
                             diet.fruit[, 3:95] + 
                             diet.vegetable[, 3:95] #+ 
                             #diet.snack[, 3:95] +
#diet.coffee[, 3:95] + 
diet.cereal[, 3:95] + 
#diet.vegan[, 3:95] + 
diet.legume[, 3:95] +
diet.nut[, 3:95]

#final.polyphenol[, 3:95] <- diet.k[, 3:95]

# The result is stored in 'summed_dataset', with columns 3 to 217 containing the summed values
write.csv(final.polyphenol, "flavonoid/final.polyphenol.csv", row.names = FALSE)
```

tableone to describe
```{r}
# anthocyanins
final.polyphenol$anthocyanins1 <- final.polyphenol$Cyanidin + final.polyphenol$Delphinidin + final.polyphenol$Malvidin + final.polyphenol$Pelargonidin + final.polyphenol$Petunidin + final.polyphenol$Peonidin

# flavanones 
final.polyphenol$flavanones1 <- final.polyphenol$Eriodictyol + final.polyphenol$Hesperetin + final.polyphenol$Naringenin

# flavan-3-ols # add for Epigallocatechin Gallocatechin Catechin.3.O.gallate Epicatechin.3.O.gallate Epigallocatechin.3.O.gallate
final.polyphenol$flavan.3.ols1 <- final.polyphenol$X....Catechin + final.polyphenol$X....Epicatechin 
#+ final.polyphenol$X....Epigallocatechin + final.polyphenol$X....Gallocatechin + final.polyphenol$X....Catechin.3.O.gallate + final.polyphenol$X....Epicatechin.3.O.gallate + final.polyphenol$X....Gallocatechin.3.O.gallate +  final.polyphenol$X....Epigallocatechin.3.O.gallate


# flavonols # add for jaceidin, patuletin, spinacetin
final.polyphenol$flavonols1 <- final.polyphenol$Quercetin + final.polyphenol$Kaempferol + final.polyphenol$Myricetin + final.polyphenol$Isorhamnetin

# flavones
final.polyphenol$flavones1 <- final.polyphenol$Luteolin + final.polyphenol$Apigenin

# polymers (including proanthocyanidins [excluding monomers], theaflavins, and thearubigins), proanthocyanidins (dimers, trimers, 4–6mers, 7–10mers, polymers, and monomers). 
final.polyphenol$polymers1 <-  final.polyphenol$X02.mers + final.polyphenol$X03.mers + final.polyphenol$X04.06.mers + final.polyphenol$X07.10.mers + final.polyphenol$Polymers...10.mers.

# Proanthocyanidins
final.polyphenol$proanthocyanidins1 <- final.polyphenol$Theaflavin + final.polyphenol$Thearubigins

# total flavonoid
final.polyphenol$total.flavonoid1 <- final.polyphenol$anthocyanins1 + final.polyphenol$flavanones1 + final.polyphenol$flavan.3.ols1 + final.polyphenol$flavonols1 + final.polyphenol$flavones1 + final.polyphenol$polymers1 + final.polyphenol$proanthocyanidins1

# Set the 'group' column as a factor with specified levels: 'psoriasis' and 'non-psoriasis'
final.polyphenol$group <- factor(final.polyphenol$group, levels = c("psoriasis", "non-psoriasis"))

# Create a descriptive table for the tea variables (columns 3 to 217) stratified by the 'group'
vars <- names(final.polyphenol)[96:103]  # Selecting the variable names from column 3 to 217
description.polyphenol <- CreateTableOne(data = final.polyphenol,
                                  vars = vars,  # Variable names extracted above
                                  strata = "group")  # Stratified by 'group' column

# Print the description table without quotes, without spaces, and without printing to the console
print(description.polyphenol, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
description.polyphenol

# Save the descriptive table results to a CSV file
write.csv(print(description.polyphenol), "flavonoid/polyphenolresult.csv")
```

# filter the items and calculate flavonoid and polyphenol
anthocyanins (cyanidin, delphinidin, malvidin, pelargonidin, petunidin, and peonidin),
flavanones (eriodictyol, hesperetin, and naringenin), 
flavan-3-ols (catechins and epicatechins), # Epigallocatechin Gallocatechin
flavonols (quercetin, kaempferol, myricetin, and isohamnetin), 
flavones (luteolin and apigenin), 
polymers (including proanthocyanidins [excluding monomers], theaflavins, and thearubigins), proanthocyanidins (dimers, trimers, 4–6mers, 7–10mers, polymers, and monomers). 
Total flavonoid intakes were calculated by summing the 6 component subclasses (flavanones, anthocyanins, flavan-3-ols, flavonols, flavones, and polymers).
phenolic acid: Gallic Acid, Protocatechuic Acid, Vanillic Acid, Syringic Acid, Ellagic Acid, Caffeic Acid, p-Coumaric Acid, Ferulic Acid, Chlorogenic Acids, Sinapic Acid, and Rosmarinic Acid. 
stilbenes: Resveratrol
Lignans: Matairesinol, Secoisolariciresinol

```{r}
### Select the variables into a separate dataset for flavonoid evaluation ###
selected.polyphenol <- data.frame(matrix(ncol = 2, nrow = nrow(diet.tea)))

# Select Participant ID and group (column 20) from the baseline dataset
selected.polyphenol[,1:2] <- diet.tea[, c(1,2)]

# Rename the columns to match the original variable names
names(selected.polyphenol) <- c("Participant.ID", "group")


# anthocyanins
selected.polyphenol$anthocyanins <- final.polyphenol$anthocyanins1

# flavanones 
selected.polyphenol$flavanones <- final.polyphenol$flavanones1

# flavonols # add for jaceidin, patuletin, spinacetin
selected.polyphenol$flavonols <- final.polyphenol$flavonols1

# flavones
selected.polyphenol$flavones <- final.polyphenol$flavones1

# flavan-3-ols # add for Epigallocatechin Gallocatechin Catechin.3.O.gallate Epicatechin.3.O.gallate Epigallocatechin.3.O.gallate
selected.polyphenol$flavan.3.ols <- final.polyphenol$flavan.3.ols1 + final.polyphenol$polymers1 + final.polyphenol$proanthocyanidins1


# total flavonoid
selected.polyphenol$total.flavonoid <- selected.polyphenol$anthocyanins + selected.polyphenol$flavanones + selected.polyphenol$flavan.3.ols + selected.polyphenol$flavonols + selected.polyphenol$flavones


# The result is stored in 'summed_dataset', with columns 3 to 217 containing the summed values
write.csv(selected.polyphenol, "flavonoid/selected.polyphenol.csv", row.names = FALSE)
```

tableone to describe
```{r}
selected.polyphenol <- read.csv("flavonoid/selected.polyphenol.csv")
#selected.polyphenol <- selected.polyphenol %>% filter(Participant.ID %in% polyphenolwithst$Participant.ID)
# Set the 'group' column as a factor with specified levels: 'psoriasis' and 'non-psoriasis'
selected.polyphenol$group <- factor(selected.polyphenol$group, levels = c("psoriasis", "non-psoriasis"))

# Create a descriptive table for the fruit variables (columns 3 to 217) stratified by the 'group'
vars <- names(selected.polyphenol)[3:8]  # Selecting the variable names from column 3 to 217
description.polyphenol <- CreateTableOne(data = selected.polyphenol,
                                  vars = vars,  # Variable names extracted above
                                  strata = "group")  # Stratified by 'group' column

# Print the description table without quotes, without spaces, and without printing to the console
print(description.polyphenol, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
description.polyphenol

# Save the descriptive table results to a CSV file
write.csv(print(description.polyphenol), "flavonoid/selectedpolyphenolresult.csv")
```

```{r}
# Step 1: 准确指定 flavonoid 子类列名
flavonoid_columns <- names(diet.nut)[96:103]  # 只需从任意一个 dataset 取名字即可

# Step 2: 重新构建数据源列表，只保留需要的列（ID + flavonoids）
source_list <- list(
  nut = diet.nut[, c("Participant.ID", flavonoid_columns)],
  tea = diet.tea[, c("Participant.ID", flavonoid_columns)],
  chocolate = diet.chocolate[, c("Participant.ID", flavonoid_columns)],
  alcohol = diet.alcohol[, c("Participant.ID", flavonoid_columns)],
  juice = diet.juice[, c("Participant.ID", flavonoid_columns)],
  cereal = diet.cereal[, c("Participant.ID", flavonoid_columns)],
  fruit = diet.fruit[, c("Participant.ID", flavonoid_columns)],
  vegetable = diet.vegetable[, c("Participant.ID", flavonoid_columns)],
  legume = diet.legume[, c("Participant.ID", flavonoid_columns)]
)

# Step 3: 提取 quartile 信息
quartile_info <- final.polyphenol[, c("Participant.ID", "quartile_total.flavonoid")]

# Step 4: 初始化
final_long_data <- data.frame()

# Step 5: 循环每个食物来源，合并 quartile，并转成长格式
for (source_name in names(source_list)) {
  df <- source_list[[source_name]]
  
  # 合并 quartile
  df <- merge(df, quartile_info, by = "Participant.ID")
  
  # 添加食物来源标签
  df$Source <- source_name
  
  # 长格式转换
  temp_long <- tidyr::pivot_longer(df,
                                   cols = all_of(flavonoid_columns),
                                   names_to = "SubType",
                                   values_to = "Amount")
  
  # 合并进总表
  final_long_data <- rbind(final_long_data, temp_long)
}

q3_q4_diff <- final_long_data %>%
  group_by(Source, SubType, quartile_total.flavonoid) %>%
  summarise(mean = mean(Amount, na.rm = TRUE), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = quartile_total.flavonoid,
                     values_from = mean,
                     names_prefix = "Q") %>%
  mutate(diff = Q4 - Q3) %>%
  arrange(desc(diff))

write.csv(q3_q4_diff, "q3_q4_diff.csv")
```

# prepare for survival time and event 

```{r}
endtime <- read.csv("C:/Users/14999/OneDrive - King's College London/genetics/check the name of different sets.csv")
# Step 1: Convert ISO datetime strings to Date format (keep only the date)
endtime <- endtime %>%
  mutate(across(starts_with("When.diet.questionnaire.completed"),
                ~ as.Date(.x, format = "%Y-%m-%dT%H:%M:%OSZ")))

# Step 2: Calculate the latest (most recent) non-NA date across the 5 time points
endtime$Latest_Diet_Date <- apply(endtime[, c("When.diet.questionnaire.completed...Instance.0",
                                              "When.diet.questionnaire.completed...Instance.1",
                                              "When.diet.questionnaire.completed...Instance.2",
                                              "When.diet.questionnaire.completed...Instance.3",
                                              "When.diet.questionnaire.completed...Instance.4")],
                                   1, function(row) {
                                     if (all(is.na(row) | row == "")) {
                                       return(NA)
                                     } else {
                                       return(max(row, na.rm = TRUE))
                                     }
                                   })
endtime$Date.of.death...Instance.0 <- as.Date(endtime$Date.of.death...Instance.0, format = "%d/%m/%Y")

polyphenol <- read.csv("C:/Users/14999/OneDrive - King's College London/genetics/flavonoid/selected.polyphenol.csv")
#polyphenol <- polyphenol[, c(1,2,3,6,7,24,42,65,76,90,104,111,158,213)]

# Convert the 'group' column to a factor with specified levels
polyphenol$group <- factor(polyphenol$group, levels = c("non-psoriasis", "psoriasis"))

# Add a new column 'event' indicating the presence of psoriasis (1) or not (0)
polyphenol <- polyphenol %>%
  mutate(event = ifelse(group == "psoriasis", 1, 0))

# Load data related to psoriasis incidence and format date columns
# Load data related to psoriasis incidence and format date columns
filtered.incidence <- read.csv("basic files/4907incidence.csv")
filtered.incidence <- merge(filtered.incidence, endtime, by = "Participant.ID")
filtered.incidence$Date.L40.first.reported..psoriasis. <- as.Date(filtered.incidence$Date.L40.first.reported..psoriasis., format = "%Y-%m-%d")

# Calculate survival time from the date of attending assessment centre to the first reported psoriasis date
filtered.incidence <- filtered.incidence %>%
  mutate(
    end_time = pmin(Date.L40.first.reported..psoriasis., Date.of.death...Instance.0, na.rm = TRUE),
    survival.time = interval(Latest_Diet_Date, end_time) / years(1)
  ) %>%
  filter(survival.time >  0)

# Load control group data and merge with non-psoriasis baseline characteristics
filtered.control <- read.csv("basic files/484895control.csv")
filtered.control <- merge(filtered.control, endtime, by = "Participant.ID")


# Calculate survival time for control participants from the date of attending assessment centre
filtered.control <- filtered.control %>%
  mutate(
    end_time = pmin(as.Date("2023-10-12"), Date.of.death...Instance.0, na.rm = TRUE),
    survival.time = interval(Latest_Diet_Date, end_time) / years(1)
  ) %>%
  filter(survival.time > 0)

# Combine survival times from both incidence and control groups into one dataset
survivaltime <- rbind(filtered.incidence[,c(1,23)], filtered.control[,c(1,22)])

# Merge dietary scores dataset with survival times based on 'Participant.ID'
polyphenolwithst <- merge(polyphenol, survivaltime, by = "Participant.ID")

# Display the column names of the final dataset
names(polyphenolwithst)

#polyphenolwithst <- polyphenolwithst %>% filter(Participant.ID %in% participants.recall.over2$Participant.ID)

table(polyphenolwithst$group)
participants.recall.over2 <- read.csv("24hr/participants.recall.over2.csv")

#polyphenolwithst <- polyphenolwithst %>% filter(Participant.ID %in% participants.recall.over2$Participant.ID)

```

# prepare for necessary covariates
```{r}
# Load demographic data for participants with psoriasis
p.baseline <- read.csv("basic files/demographics.csv") %>%
  filter(Participant.ID %in% polyphenolwithst$Participant.ID)
p.baseline <- p.baseline[, c(1,2,3, 6, 16)]

white <- c("White", "British", "Irish", "Any other white background")
mixed <- c("White and Black Caribbean", "White and Black African", "White and Asian", "Mixed", "Any other mixed background")
asian <- c("Indian", "Chinese", "Pakistani", "Bangladeshi", "Asian or Asian British", "Any other Asian background")
black <- c("Caribbean", "African", "Black or Black British", "Any other Black background")
other.ethnic.group <- "Other ethnic group"
missing <- c("Do not know", "Prefer not to answer", "")

p.baseline <- p.baseline %>%
  mutate(
    Ethnic.background = case_when(
      p.baseline$Ethnic.background...Instance.0 %in% white ~ "White",
      p.baseline$Ethnic.background...Instance.0 %in% mixed ~ "Mixed",
      p.baseline$Ethnic.background...Instance.0 %in% asian ~ "Asian",
      p.baseline$Ethnic.background...Instance.0 %in% black ~ "Black",
      p.baseline$Ethnic.background...Instance.0 %in% other.ethnic.group ~ "Other ethnic group",
      p.baseline$Ethnic.background...Instance.0 %in% missing ~ "Missing"
  ))

education <- read.csv("basic files/education.csv") %>%
  filter(Participant.ID %in% polyphenolwithst$Participant.ID)

qual_order <- c(
  "College or University degree",
  "Other professional qualifications eg: nursing, teaching",
  "A levels/AS levels or equivalent",
  "NVQ or HND or HNC or equivalent",
  "CSEs or equivalent",
  "O levels/GCSEs or equivalent",
  "Prefer not to answer",
  "None of the above",
  NA
)

# 处理数据：按优先级保留每个ID的最高学历
education_top <- education %>%
  mutate(priority = match(Qualifications, qual_order)) %>%
  group_by(Participant.ID) %>%
  slice_min(priority, with_ties = FALSE) %>%
  ungroup()


#Low: CSEs or equivalent, O levels/GCSEs or equivalent; 
low <- c("CSEs or equivalent", "O levels/GCSEs or equivalent")
#Medium: A levels/AS levels or equivalent, NVQ or HND or HNC or equivalent; 
medium <- c("A levels/AS levels or equivalent", "NVQ or HND or HNC or equivalent")
#High: College or University degree, other professional qualifications eg: nursing, teaching; 
high <- c("College or University degree", "Other professional qualifications eg: nursing, teaching")
#unknown/missing/prefer not to say
missing <- c(NA, "None of the above", "Prefer not to answer")
education_top <- education_top %>%
  mutate(
    Qualification = case_when(
      education_top$Qualifications %in% low ~ "low",
      education_top$Qualifications %in% medium ~ "medium",
      education_top$Qualifications %in% high ~ "high",
      education_top$Qualifications %in% missing ~ "missing"
  ))
p.baseline <- merge(p.baseline, education_top[, c(1,5)], by = "Participant.ID")

# Load lifestyle data for participants with and without psoriasis
p.lifestyle <- read.csv("basic files/healthandlifestyle.csv") %>%
  filter(Participant.ID %in% polyphenolwithst$Participant.ID)
p.lifestyle <- p.lifestyle[, c(1, 12, 71:72, 85, 87, 88)]

# Rename the BMI column to a simpler name
names(p.lifestyle)[names(p.lifestyle) == "Body.mass.index..BMI....Instance.0.participant...p21001_i0."] <- "BMI"

covariatebasic <- merge(p.baseline, p.lifestyle, by = "Participant.ID")

p.comorbid <- read.csv("basic files/comorbidity.number.csv")%>%
  filter(Participant.ID %in% polyphenolwithst$Participant.ID)
AQI <- read.csv("basic files/AQI.csv")%>%
  filter(Participant.ID %in% polyphenolwithst$Participant.ID)
PRS <- read.csv("basic files/PRS.csv") %>%
  filter(Participant.ID %in% polyphenolwithst$Participant.ID)

need <- merge(p.comorbid[, c(1, 155, 156)], AQI[, c(1,9)], by = "Participant.ID")
covariate <- merge(covariatebasic, need, by = "Participant.ID")
covariateothers <- merge(endtime[, c(3,9)], PRS[, c(1:15)], by = "Participant.ID")
covariate <- merge(covariate, covariateothers, by = "Participant.ID")

p.24h.foods.average <- read.csv("24hr/average 24hrecall individual foods.csv") %>% 
  filter(Participant.ID %in% polyphenolwithst$Participant.ID)
p.24h.nutrients.average <- read.csv("24hr/average 24hrecall nutrients.csv") %>% 
  filter(Participant.ID %in% polyphenolwithst$Participant.ID)
PDIscore <- read.csv("diet indices/PDIscore.csv")
nutrient <- merge(p.24h.nutrients.average[, c(1, 2, 14, 17, 20, 44)], PDIscore[,c(21, 18, 19)], by = "Participant.ID")

p.24h.foods.average$SSB <- rowSums(p.24h.foods.average[c(4, 5, 22, 24)], na.rm = TRUE)
p.24h.foods.average$cheese <- rowSums(p.24h.foods.average[c(106:116)], na.rm = TRUE)
p.24h.foods.average$egg <- rowSums(p.24h.foods.average[c(117:121)], na.rm = TRUE)
p.24h.foods.average$meat <- rowSums(p.24h.foods.average[c(122:125, 128:131)], na.rm = TRUE)
p.24h.foods.average$fish <- rowSums(p.24h.foods.average[c(132:140)], na.rm = TRUE)
p.24h.foods.average$wholegrain <- rowSums(p.24h.foods.average[c(33:35, 38:39, 48, 99, 101, 104)], na.rm = TRUE)
p.24h.foods.average$coffee <- rowSums(p.24h.foods.average[c(11:15)], na.rm = TRUE)
p.24h.foods.average$tea  <- rowSums(p.24h.foods.average[c(16:20)], na.rm = TRUE)
p.24h.foods.average$fruit.juice <- rowSums(p.24h.foods.average[c(6:9)], na.rm = TRUE)
p.24h.foods.average$fruit  <- rowSums(p.24h.foods.average[c(183:201)], na.rm = TRUE)
p.24h.foods.average$chocolate  <- rowSums(p.24h.foods.average[, c("Chocolate.bar.intake",
                                                 "White.chocolate.intake",
                                                 "Milk.chocolate.intake",
                                                 "Dark.chocolate.intake",
                                                 "Chocolate.covered.raisin.intake",
                                                 "Chocolate.sweet.intake",
                                                 "Chocolate.covered.biscuits.intake",
                                                 "Chocolate.biscuits.intake")], na.rm = TRUE)
p.24h.foods.average$vegetable  <- rowSums(p.24h.foods.average[c(150:154, 156:171, 173:182)], na.rm = TRUE)
p.24h.foods.average$wine  <- rowSums(p.24h.foods.average[c(26:31)], na.rm = TRUE)
p.24h.foods.average$nut  <- rowSums(p.24h.foods.average[c(85:89)], na.rm = TRUE)
p.24h.foods.average$legume  <- rowSums(p.24h.foods.average[c(145:146, 155, 172)], na.rm = TRUE)

#p.24h.foods.average$snk <- rowSums(p.24h.foods.average[c(50:71, 78:79, 82:84, 90:92, 94)], na.rm = TRUE)

covariate <- merge(covariate, nutrient, by = "Participant.ID")
covariate <- merge(covariate, p.24h.foods.average[, c(1, 202:216)], by = "Participant.ID")
polyphenolwithhealth <- merge(polyphenolwithst, covariate, by = "Participant.ID")

# Convert IPAQ activity group to a factor with specified levels, excluding blank entries
polyphenolwithhealth$IPAQ.activity.group...Instance.0 <- factor(polyphenolwithhealth$IPAQ.activity.group...Instance.0, levels = c("low", "moderate", "high", ""))

# Step 1: Replace "" and "Prefer not to answer" with "Missing"
polyphenolwithhealth$Smoking.status...Instance.0[
  polyphenolwithhealth$Smoking.status...Instance.0 %in% c("", "Prefer not to answer")
] <- "Missing"

# Step 2: Set factor levels, including "Missing"
polyphenolwithhealth$Smoking.status...Instance.0 <- factor(
  polyphenolwithhealth$Smoking.status...Instance.0,
  levels = c("Never", "Previous", "Current", "Missing")
)

# Step 1: Replace "" and "Prefer not to answer" with "Missing"
polyphenolwithhealth$Alcohol.drinker.status...Instance.0[
  polyphenolwithhealth$Alcohol.drinker.status...Instance.0 %in% c("", "Prefer not to answer")
] <- "Missing"

# Step 2: Set factor levels, including "Missing"
polyphenolwithhealth$Alcohol.drinker.status...Instance.0 <- factor(
  polyphenolwithhealth$Alcohol.drinker.status...Instance.0,
  levels = c("Never", "Previous", "Current", "Missing")
)

# Step 1: Replace "" and "Prefer not to answer" with "Missing"
polyphenolwithhealth$Alcohol.intake.frequency....Instance.0[
  polyphenolwithhealth$Alcohol.intake.frequency....Instance.0 %in% c("", "Prefer not to answer")
] <- "Missing"

# Step 2: Set factor levels, including "Missing"
polyphenolwithhealth$Alcohol.drinker.status...Instance.0 <- factor(polyphenolwithhealth$Alcohol.intake.frequency....Instance.0, levels = c("Never", "Special occasions only", "One to three times a month", "Once or twice a week", "Three or four times a week", "Daily or almost daily", "Missing"))


# Convert MET minutes
polyphenolwithhealth$Summed.MET.minutes.per.week.for.all.activity...Instance.0 <- 
  as.numeric(polyphenolwithhealth$Summed.MET.minutes.per.week.for.all.activity...Instance.0)

# 计算唯一分位点
valid_MET <- polyphenolwithhealth$Summed.MET.minutes.per.week.for.all.activity...Instance.0
quantile_breaks <- unique(quantile(valid_MET, probs = seq(0, 1, 0.2), na.rm = TRUE))

# 使用 cut() 划分分组（对非缺失值）
MET_quintiles <- cut(
  valid_MET,
  breaks = quantile_breaks,
  include.lowest = TRUE,
  labels = paste0("Q", 1:5)
)

# 将 NA 值替换为 "Missing"
MET_quintiles <- as.character(MET_quintiles)  # 先转为字符，才能加入 "Missing"
MET_quintiles[is.na(MET_quintiles)] <- "Missing"
polyphenolwithhealth$MET.Quintiles <- factor(MET_quintiles, levels = c(paste0("Q", 1:5), "Missing"))


# Step 1: Create BMI category for non-missing values
polyphenolwithhealth$BMI.Category <- cut(
  polyphenolwithhealth$BMI,
  breaks = c(-Inf, 24.9, 29.9, Inf),
  labels = c("<24.9", "25.0–29.9", "≥30"),
  include.lowest = TRUE
)

# Step 2: Convert to character to allow adding "Missing"
polyphenolwithhealth$BMI.Category <- as.character(polyphenolwithhealth$BMI.Category)

# Step 3: Replace NA with "Missing"
polyphenolwithhealth$BMI.Category[is.na(polyphenolwithhealth$BMI.Category)] <- "Missing"

# Step 4: Convert back to factor and set desired level order
polyphenolwithhealth$BMI.Category <- factor(
  polyphenolwithhealth$BMI.Category,
  levels = c("<24.9", "25.0–29.9", "≥30", "Missing")
)

prs_cut <- cut(
  polyphenolwithhealth$Standard.PRS.for.psoriasis..PSO.,
  breaks = quantile(polyphenolwithhealth$Standard.PRS.for.psoriasis..PSO., probs = c(0, 1/3, 2/3, 1), na.rm = TRUE),
  include.lowest = TRUE,
  labels = c("Low", "Medium", "High")
)

prs_cut <- as.character(prs_cut)
prs_cut[is.na(prs_cut)] <- "Missing"

polyphenolwithhealth$PRS.tertile <- factor(prs_cut, levels = c("Low", "Medium", "High", "Missing"))

age_cut <- cut(
  polyphenolwithhealth$Age.at.recruitment,
  breaks = c(40, 50, 60, 70),  # adjust if needed
  include.lowest = TRUE,
  right = FALSE,
  labels = c("40–49", "50–59", "60–69")
)

age_cut <- as.character(age_cut)

polyphenolwithhealth$Age.group <- factor(age_cut, levels = c("40–49", "50–59", "60–69"))

imd_cut <- cut(
  as.numeric(polyphenolwithhealth$Townsend.deprivation.index.at.recruitment),
  breaks = quantile(polyphenolwithhealth$Townsend.deprivation.index.at.recruitment, probs = seq(0, 1, 0.25), na.rm = TRUE),
  include.lowest = TRUE,
  labels = c("Q1", "Q2", "Q3", "Q4")
)

imd_cut <- as.character(imd_cut)
imd_cut[is.na(imd_cut)] <- "Missing"

polyphenolwithhealth$IMD.quartile <- factor(imd_cut, levels = c("Q1", "Q2", "Q3", "Q4", "Missing"))

# Convert back to factor with desired order
polyphenolwithhealth$AQI.Category <- factor(polyphenolwithhealth$AQI, levels = c("1", "2", "Missing"))

# Categorize and convert to a factor with ordered levels
polyphenolwithhealth <- polyphenolwithhealth %>%
  mutate(
    alcohol.category = case_when(
      Alcohol < 1  ~ "<1 g/day",
      Alcohol >= 1 & Alcohol < 8 ~ "1–7 g/day",
      Alcohol >= 8 & Alcohol < 16 ~ "8–15 g/day",
      Alcohol >= 16 ~ "16+ g/day"
    ),
    alcohol.category = factor(
      alcohol.category,
      levels = c("<1 g/day", "1–7 g/day", "8–15 g/day", "16+ g/day")
    )
  )

polyphenolwithhealth <- polyphenolwithhealth %>%
  mutate(
    level.questionnaires = factor(
      if_else(Number.of.diet.questionnaires.completed == 1, 
              "level1", 
              "level2"),
      levels = c("level1", "level2")
    ),
    
    multimorbidity = factor(
      case_when(
        multimorbidity == 0 ~ "level0",
        multimorbidity == 1 ~ "level1",
        multimorbidity >= 2 ~ "level2"
      ),
      levels = c("level0", "level1", "level2")
    )
  )

polyphenolwithhealth[, 11:70][polyphenolwithhealth[, 11:70] == ""] <- NA


#polyphenolwithhealth <- merge(polyphenolwithhealth, p.24h.foods.average[, c(1, 16, 24, 26, 187, 189, 75, 8, 18, 23, 200, 9)], by = "Participant.ID")
#polyphenolwithhealth[, 74:84][is.na(polyphenolwithhealth[, 74:84])] <- 0
polyphenolwithhealth <- polyphenolwithhealth %>% filter(Participant.ID %in% participants.recall.over2$Participant.ID)
```


model 1 (PRS tertile)
Sex
Age
Ethnic background
MET Quintiles
smoking status
alcohol category
multimorbidity
IMD
Sodium
Free.sugar
processed meat

model 2.2
AQI

model 3
BMI

coxph(Survival.Obj ~ polyphenolwithhealth[,i] + Sex + Age.group + Ethnic.background + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + Z.Combined.IMD + Sodium + Free.sugar + meat + PRS.tertile + Genetic.kinship.to.other.participants + Genetic.principal.components...Array.1 + Genetic.principal.components...Array.2 + Genetic.principal.components...Array.3 + Genetic.principal.components...Array.4 + Genetic.principal.components...Array.5 + Genetic.principal.components...Array.6 + Genetic.principal.components...Array.7 + Genetic.principal.components...Array.8 + Genetic.principal.components...Array.9 + Genetic.principal.components...Array.10, data = polyphenolwithhealth)

# cut according to knowledge
```{r}
df <- polyphenolwithhealth

# 定义每个变量的 cut4（mg/day）
specs4 <- list(
  anthocyanins    = list(breaks = c(-Inf, 0.5, 25, 70, Inf),
                         labels = c("<0.5","0.5–<25","25–<70","≥70")),
  `flavan.3.ols`  = list(breaks = c(-Inf, 200, 500, 900, Inf),
                         labels = c("<200","200–<500","500–<900","≥900")),
  flavanones      = list(breaks = c(-Inf, 2, 20, 45, Inf),
                         labels = c("<2","2–<20","20–<45","≥45")),
  flavonols       = list(breaks = c(-Inf, 25, 40, 55, Inf),
                         labels = c("<25","25–<40","40–<55","≥55")),
  flavones        = list(breaks = c(-Inf, 0.5, 1.5, 3, Inf),
                         labels = c("<0.5","0.5–<1.5","1.5–<3","≥3")),
  total.flavonoid = list(breaks = c(-Inf, 400, 800, 1100, Inf),
                         labels = c("<450","450–<800","800–<1100","≥1100"))
)

# 批量创建 _cat4 和 _ord4
for(nm in names(specs4)){
  br  <- specs4[[nm]]$breaks
  lab <- specs4[[nm]]$labels
  cat_var <- paste0(nm, "_cat4")
  ord_var <- paste0(nm, "_ord4")
  
  # 创建分类变量
  df[[cat_var]] <- cut(df[[nm]], breaks = br, right = FALSE, labels = lab)
  # 创建有序变量
  df[[ord_var]] <- as.numeric(df[[cat_var]])
}

# 输出：先显示所有 *_cat4，再显示所有 *_ord4
cat_vars <- grep("_cat4$", names(df), value = TRUE)
ord_vars <- grep("_ord4$", names(df), value = TRUE)

# 查看所有 cat4 变量
cat_table <- df %>%
  dplyr::select(all_of(cat_vars))

# 查看所有 ord4 变量
ord_table <- df %>%
  dplyr::select(all_of(ord_vars))

# 打印结果
cat_table %>% head()  # 显示前几行分类标签
ord_table %>% head()  # 显示前几行有序变量（1–4）

# 更新回主数据对象

dietaryscorewithquartile <- df

```
# key food
```{r}
df <- p.24h.foods.average %>%
  # Step 1: 提取原始变量
  dplyr::select(
    Participant.ID,
    Pure.fruit.vegetable.juice.intake,
    Olives.intake,
    Broccoli.intake,
    Celery.intake,
    Side.salad.intake,
    Red.wine.intake
  ) %>% 
  # Step 2: 用原始 intake 计算 foodA 和 foodB（先将 NA 视为 0）
  mutate(
    foodA_raw = rowSums(across(
      c(
        Pure.fruit.vegetable.juice.intake,
        Olives.intake,
        Broccoli.intake,
        Celery.intake,
        Side.salad.intake,
        Red.wine.intake
      ), ~ replace_na(.x, 0)
    )),
    
    foodB_raw = rowSums(across(
      c(
        Pure.fruit.vegetable.juice.intake,
        Olives.intake,
        Broccoli.intake,
        Celery.intake,
        Side.salad.intake
      ), ~ replace_na(.x, 0)
    ))
  ) %>%
  # Step 3: 对每个原始变量进行分类（NA → 0）
  mutate(across(
    .cols = c(
      Pure.fruit.vegetable.juice.intake,
      Olives.intake,
      Broccoli.intake,
      Celery.intake,
      Side.salad.intake,
      Red.wine.intake
    ),
    .fns = ~ case_when(
      is.na(.x) | .x == 0 ~ 0,
      .x > 0 & .x <= 1 ~ 1,
      .x > 1 ~ 2
    ),
    .names = "{.col}_cat"
  )) %>%
  # Step 4: foodA_raw / foodB_raw 的分类
  mutate(
    foodA_cat = case_when(
      foodA_raw == 0 ~ 0,
      foodA_raw > 0 & foodA_raw <= 1 ~ 1,
      foodA_raw > 1 ~ 2
    ),
    foodB_cat = case_when(
      foodB_raw == 0 ~ 0,
      foodB_raw > 0 & foodB_raw <= 1 ~ 1,
      foodB_raw > 1 ~ 2
    )
  ) %>%
  # Step 5: 保留 ID
  filter(Participant.ID %in% polyphenolwithhealth$Participant.ID)


dietaryscorewithquartile <- merge(polyphenolwithhealth, df[, c(1, 10:17)], by = "Participant.ID")
```



# RCS
```{r}
library(rms)

#==== 0) Data ====
df <- polyphenolwithhealth

# Complete-case (or use your own imputation pipeline)
df <- df %>% drop_na(survival.time, event, flavones)
#df$flavones <- log1p(df$flavones)
#df$flavanones <- log1p(df$flavanones)

#==== 1) rms setup ====
dd <- datadist(df)
options(datadist = "dd")
# Choose knots (Harrell often uses 4–5 knots). Example: 4 knots at 5/35/65/95%
kn_5 <- quantile(df$flavones, probs = c(0.05, 0.275, 0.50, 0.725, 0.95), na.rm = TRUE)

#==== 2) Fit Cox with RCS ====
fit_rcs <- cph(
  Surv(survival.time, event) ~ 
    rcs(flavones, knots = kn_5)  + Sex + Age.group + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Qualification + Energy + Free.sugar + meat + wholegrain + BMI.Category,
  data = df, x = TRUE, y = TRUE
)

#==== 3) Test overall & nonlinearity ====
# anova: 'Nonlinear' line gives the non-linear part p-value
anova(fit_rcs)

#==== 4) Plot HR curve (reference at a chosen value, e.g., 20th percentile) ====
ref_val <- as.numeric(quantile(df$flavones, 0.20, na.rm = TRUE))

# 2) 取得样条在全范围上的线性预测 (log-HR 尺度)
pred_lin <- Predict(fit_rcs, flavones, conf.int = 0.95)  # 不要传 ref=

# 3) 在参考点的线性预测
ref_lin  <- Predict(fit_rcs, flavones = ref_val, conf.int = 0.95)

# 4) 把曲线以参考点居中，并转为 HR
pred_df <- as.data.frame(pred_lin)
ref_y   <- as.numeric(ref_lin$yhat)

pred_df <- pred_df %>%
  mutate(HR   = exp(yhat  - ref_y),
         HRlo = exp(lower - ref_y),
         HRhi = exp(upper - ref_y))

# 5) 画图
# 创建 knots 数据框，用于在曲线上标点
knot_df <- data.frame(flavones = kn_5) %>%
  rowwise() %>%
  mutate(
    flavones_nearest = pred_df$flavones[which.min(abs(pred_df$flavones - flavones))],
    HR   = pred_df$HR[which.min(abs(pred_df$flavones - flavones))],
    HRlo = pred_df$HRlo[which.min(abs(pred_df$flavones - flavones))],
    HRhi = pred_df$HRhi[which.min(abs(pred_df$flavones - flavones))]
  ) %>%
  ungroup()

pA_overall   <- 0.012
pA_nonlinear <- 0.006

# 小工具：格式化 P 值显示
fmt_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "<0.001" else sprintf("%.3f", p)
}

label_A <- bquote(italic(P)[overall] == .(fmt_p(pA_overall)) ~ "," ~ 
                  italic(P)[nonlinear] == .(fmt_p(pA_nonlinear)))
label_A_str <- as.character(as.expression(label_A))

# 2️⃣ 绘图：曲线上显示 knot 点
res_A <- ggplot(pred_df, aes(x = flavones, y = HR)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = HRlo, ymax = HRhi), alpha = 0.2) +
  geom_vline(xintercept = ref_val, linetype = 2, color = "grey50") +
  geom_point(data = knot_df, aes(x = flavones_nearest, y = HR),
             color = "red", size = 2.5) +
  geom_text(data = knot_df,
            aes(x = flavones_nearest, y = HR,
                label = paste0("K", 1:nrow(knot_df))),
            vjust = -1, color = "red", size = 3.2) +
  labs(x = "Flavone intake (mg/day)",
       y = "Hazard Ratio") +
  theme_classic(base_size = 13) +
  annotate("text", x = Inf, y = Inf, 
           label = label_A_str,
           hjust = 1.05, vjust = 1.5, size = 4, parse = TRUE)






library(dplyr)
library(rms)
library(survival)
library(ggplot2)

#===========================
# 0. 数据准备
#===========================
df2 <- polyphenolwithhealth %>% 
  drop_na(survival.time, event, flavones, PRS.tertile)

#===========================
# 1. rms setup
#===========================
dd <- datadist(df)
options(datadist = "dd")
# 共用 knots
kn <- quantile(df2$flavones, probs = c(0.05, 0.275, 0.50, 0.725, 0.95))

# reference point
ref_val <- quantile(df2$flavones, 0.20, na.rm = TRUE)


#===========================
# 2. Function to fit spline for each PRS group
#===========================
fit_spline_group <- function(data_sub) {

  fit <- cph(
    Surv(survival.time, event) ~ 
      rcs(flavones, knots = kn) +
      Sex + Age.group + MET.Quintiles + Smoking.status...Instance.0 +
      alcohol.category + multimorbidity + IMD.quartile +
      Qualification + Energy + Free.sugar + meat + wholegrain + BMI.Category,
    data = data_sub,
    x = TRUE, y = TRUE
  )
  
  # Predict HR curve
  pred_lin <- Predict(fit, flavones, conf.int = 0.95)
  pred_df  <- as.data.frame(pred_lin)
  
  # reference correction
  ref_hat <- Predict(fit, flavones = ref_val)$yhat
  
  pred_df <- pred_df %>%
    mutate(
      HR   = exp(yhat - ref_hat),
      HRlo = exp(lower - ref_hat),
      HRhi = exp(upper - ref_hat)
    )
  
  pred_df
}

#===========================
# 3. Run spline for each PRS-level
#===========================
spl_low  <- fit_spline_group(df2 %>% filter(PRS.tertile == "Low"))
spl_mid  <- fit_spline_group(df2 %>% filter(PRS.tertile == "Medium"))
spl_high <- fit_spline_group(df2 %>% filter(PRS.tertile == "High"))

#===========================
# 4. Combine into one dataset
#===========================
df_plot <- bind_rows(
  spl_low  %>% mutate(PRS = "Low PRS"),
  spl_mid  %>% mutate(PRS = "Medium PRS"),
  spl_high %>% mutate(PRS = "High PRS")
)


#===========================
# 5. Make P-value labels using bquote (你的要求)
#===========================

make_label <- function(overall, nonlinear) {
  as.character(
    as.expression(
      bquote(italic(P)[overall] == .(overall) ~ "," ~ italic(P)[nonlinear] == .(nonlinear))
    )
  )
}

label_low    <- make_label(0.86, 0.73)
label_medium <- make_label(0.27, 0.16)
label_high   <- make_label(0.003, 0.002)


#===========================
# 6. Plot (三条 PRS spline)
#===========================
df_plot$PRS <- factor(df_plot$PRS, levels = c("High PRS", "Medium PRS", "Low PRS"))
ggplot(df_plot, aes(x = flavones, y = HR, color = PRS)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = HRlo, ymax = HRhi, fill = PRS),
            alpha = 0.1, color = NA,
            show.legend = FALSE) +
  geom_vline(xintercept = ref_val, linetype = 2, color = "grey50") +
  theme_classic(base_size = 14) +
  scale_color_manual(values = c("#0072B2", "#009E73", "#D55E00")) +
  scale_fill_manual(values   = c("#0072B2", "#009E73", "#D55E00")) +
  
  # ==== y 轴限制 ====
  coord_cartesian(ylim = c(0, 5)) +
  
  labs(
    x = "Flavone intake (mg/day)",
    y = "Hazard Ratio",
    color = "PRS tertile"
  ) +

  # --- Annotations with more spacing ---
  annotate("text",
           x = Inf, y = Inf,
           label = as.character(as.expression(
             bquote("Low PRS:" ~ 
                    italic(P)[overall] == 0.88 ~ "," ~ 
                    italic(P)[nonlinear] == 0.75)
           )),
           hjust = 1.05, vjust = 4.5,
           parse = TRUE, size = 3) +

  annotate("text",
           x = Inf, y = Inf,
           label = as.character(as.expression(
             bquote("Medium PRS:" ~ 
                    italic(P)[overall] == 0.24 ~ "," ~ 
                    italic(P)[nonlinear] == 0.14)
           )),
           hjust = 1.05, vjust = 3.0,
           parse = TRUE, size = 3) +

  annotate("text",
           x = Inf, y = Inf,
           label = as.character(as.expression(
             bquote("High PRS:" ~ 
                    italic(P)[overall] == 0.004 ~ "," ~ 
                    italic(P)[nonlinear] == 0.002)
           )),
           hjust = 1.05, vjust = 1.5,
           parse = TRUE, size = 3)
```
# RCS for food
```{r}
#==== 0) Data ====
df1 <- merge(df[, c(1, 8, 9)], polyphenolwithhealth, by = "Participant.ID")

# Complete-case (or use your own imputation pipeline)
df1 <- df1 %>% drop_na(survival.time, event, foodB_raw)
#df$foodB_raw <- log1p(df$foodB_raw)
#df$flavanones <- log1p(df$flavanones)

#==== 1) rms setup ====
dd <- datadist(df1)
options(datadist = "dd")
# Choose knots (Harrell often uses 4–5 knots). Example: 4 knots at 5/35/65/95%
kn_5 <- quantile(df$foodB_raw, probs = c(0.05, 0.275, 0.50, 0.725, 0.95), na.rm = TRUE)

#==== 2) Fit Cox with RCS ====
fit_rcs <- cph(
  Surv(survival.time, event) ~ 
    rcs(foodB_raw, knots = kn_5)  + Sex + Age.group + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Qualification + Energy + Free.sugar + meat + wholegrain + BMI.Category,
  data = df1, x = TRUE, y = TRUE
)

#==== 3) Test overall & nonlinearity ====
# anova: 'Nonlinear' line gives the non-linear part p-value
anova(fit_rcs)

#==== 4) Plot HR curve (reference at a chosen value, e.g., 20th percentile) ====
ref_val <- as.numeric(quantile(df$foodB_raw, 0.20, na.rm = TRUE))

# 2) 取得样条在全范围上的线性预测 (log-HR 尺度)
pred_lin <- Predict(fit_rcs, foodB_raw, conf.int = 0.95)  # 不要传 ref=

# 3) 在参考点的线性预测
ref_lin  <- Predict(fit_rcs, foodB_raw = ref_val, conf.int = 0.95)

# 4) 把曲线以参考点居中，并转为 HR
pred_df <- as.data.frame(pred_lin)
ref_y   <- as.numeric(ref_lin$yhat)

pred_df <- pred_df %>%
  mutate(HR   = exp(yhat  - ref_y),
         HRlo = exp(lower - ref_y),
         HRhi = exp(upper - ref_y))

# 5) 画图
# 创建 knots 数据框，用于在曲线上标点
knot_df <- data.frame(foodB_raw = kn_5) %>%
  rowwise() %>%
  mutate(
    foodB_raw_nearest = pred_df$foodB_raw[which.min(abs(pred_df$foodB_raw - foodB_raw))],
    HR   = pred_df$HR[which.min(abs(pred_df$foodB_raw - foodB_raw))],
    HRlo = pred_df$HRlo[which.min(abs(pred_df$foodB_raw - foodB_raw))],
    HRhi = pred_df$HRhi[which.min(abs(pred_df$foodB_raw - foodB_raw))]
  ) %>%
  ungroup()

pA_overall   <- 0.023
pA_nonlinear <- 0.012

# 小工具：格式化 P 值显示
fmt_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "<0.001" else sprintf("%.3f", p)
}

label_A <- bquote(italic(P)[overall] == .(fmt_p(pA_overall)) ~ "," ~ 
                    italic(P)[nonlinear] == .(fmt_p(pA_nonlinear)))
label_A_str <- as.character(as.expression(label_A))

# 2️⃣ 绘图：曲线上显示 knot 点
res_A <- ggplot(pred_df, aes(x = foodB_raw, y = HR)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = HRlo, ymax = HRhi), alpha = 0.2) +
  geom_vline(xintercept = ref_val, linetype = 2, color = "grey50") +
  geom_point(data = knot_df, aes(x = foodB_raw_nearest, y = HR),
             color = "red", size = 2.5) +
  geom_text(data = knot_df,
            aes(x = foodB_raw_nearest, y = HR,
                label = paste0("K", 1:nrow(knot_df))),
            vjust = -1, color = "red", size = 3.2) +
  labs(x = "Food intake (servings/d)",
       y = "Hazard Ratio") +
  theme_classic(base_size = 13) + 
  labs(title = "B. Flavone-rich food") +
  annotate("text", x = Inf, y = Inf, 
           label = label_A_str,
           hjust = 1.05, vjust = 1.5, size = 4, parse = TRUE)



df1 <- merge(df[, c(1, 8, 9)], polyphenolwithhealth, by = "Participant.ID")

# Complete-case (or use your own imputation pipeline)
df1 <- df1 %>% drop_na(survival.time, event, foodA_raw)
#df$foodA_raw <- log1p(df$foodA_raw)
#df$flavanones <- log1p(df$flavanones)

#==== 1) rms setup ====
dd <- datadist(df1)
options(datadist = "dd")
# Choose knots (Harrell often uses 4–5 knots). Example: 4 knots at 5/35/65/95%
kn_5 <- quantile(df$foodA_raw, probs = c(0.05, 0.275, 0.50, 0.725, 0.95), na.rm = TRUE)

#==== 2) Fit Cox with RCS ====
fit_rcs <- cph(
  Surv(survival.time, event) ~ 
    rcs(foodA_raw, knots = kn_5)  + Sex + Age.group + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Qualification + Energy + Free.sugar + meat + wholegrain + BMI.Category,
  data = df1, x = TRUE, y = TRUE
)

#==== 3) Test overall & nonlinearity ====
# anova: 'Nonlinear' line gives the non-linear part p-value
anova(fit_rcs)

#==== 4) Plot HR curve (reference at a chosen value, e.g., 20th percentile) ====
ref_val <- as.numeric(quantile(df$foodA_raw, 0.20, na.rm = TRUE))

# 2) 取得样条在全范围上的线性预测 (log-HR 尺度)
pred_lin <- Predict(fit_rcs, foodA_raw, conf.int = 0.95)  # 不要传 ref=

# 3) 在参考点的线性预测
ref_lin  <- Predict(fit_rcs, foodA_raw = ref_val, conf.int = 0.95)

# 4) 把曲线以参考点居中，并转为 HR
pred_df <- as.data.frame(pred_lin)
ref_y   <- as.numeric(ref_lin$yhat)

pred_df <- pred_df %>%
  mutate(HR   = exp(yhat  - ref_y),
         HRlo = exp(lower - ref_y),
         HRhi = exp(upper - ref_y))

# 5) 画图
# 创建 knots 数据框，用于在曲线上标点
knot_df <- data.frame(foodA_raw = kn_5) %>%
  rowwise() %>%
  mutate(
    foodA_raw_nearest = pred_df$foodA_raw[which.min(abs(pred_df$foodA_raw - foodA_raw))],
    HR   = pred_df$HR[which.min(abs(pred_df$foodA_raw - foodA_raw))],
    HRlo = pred_df$HRlo[which.min(abs(pred_df$foodA_raw - foodA_raw))],
    HRhi = pred_df$HRhi[which.min(abs(pred_df$foodA_raw - foodA_raw))]
  ) %>%
  ungroup()

pA_overall   <- 0.14
pA_nonlinear <- 0.08

# 小工具：格式化 P 值显示
fmt_p <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) "<0.001" else sprintf("%.3f", p)
}

label_A <- bquote(italic(P)[overall] == .(fmt_p(pA_overall)) ~ "," ~ 
                    italic(P)[nonlinear] == .(fmt_p(pA_nonlinear)))
label_A_str <- as.character(as.expression(label_A))

# 2️⃣ 绘图：曲线上显示 knot 点
res_B <- ggplot(pred_df, aes(x = foodA_raw, y = HR)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = HRlo, ymax = HRhi), alpha = 0.2) +
  geom_vline(xintercept = ref_val, linetype = 2, color = "grey50") +
  geom_point(data = knot_df, aes(x = foodA_raw_nearest, y = HR),
             color = "red", size = 2.5) +
  geom_text(data = knot_df,
            aes(x = foodA_raw_nearest, y = HR,
                label = paste0("K", 1:nrow(knot_df))),
            vjust = -1, color = "red", size = 3.2) +
  labs(x = "Food intake (servings/d)",
       y = "Hazard Ratio") +
  theme_classic(base_size = 13) + 
  labs(title = "A. Flavone-rich food and wine") +
  annotate("text", x = Inf, y = Inf, 
           label = label_A_str,
           hjust = 1.05, vjust = 1.5, size = 4, parse = TRUE)

library(cowplot)

combined_plot <- plot_grid(
  res_B, res_A,
  ncol = 2,           # 两列
  rel_widths = c(2,2) # 比例可调
)

combined_plot


```



# forest plot
```{r}
# Load the data
table3 <- read.csv("diet quality output/table2.csv")  # Replace with your correct file name
table3$Person.years <- round(table3$Person.years, 0)
table3$Person.years <- ifelse(is.na(table3$Person.years), "", table3$Person.years)

# Prepare three empty columns for the plot (Model1, Model2, and Model3)
table3 <- table3 %>%
  mutate( 'Flavonoid subclass (mg/d)' = Flavonoid.subclass..mg.d.,
         'Cases/Total (Incidence %)' = Case.total..incidence...,
         'Person years' = Person.years,
    `Model 1;HR (95% CI)` = Model.1..HR..95..CI.,
    `Model 2;HR (95% CI)` = Model.2..HR..95..CI.,
    `Model 3;HR (95% CI)` = Model.3..HR..95..CI.)
# Modify the `p value` column


parse_ci <- function(ci_vec) {
  strcapture(
    pattern = "^\\s*([0-9.+-eE]+)\\s*\\(\\s*([0-9.+-eE]+)\\s*-\\s*([0-9.+-eE]+)\\s*\\)\\s*$",
    x = ci_vec,
    proto = list(HR = double(), lower = double(), upper = double())
  )
}

table3 <- cbind(table3, parse_ci(table3$`Model 1;HR (95% CI)`), parse_ci(table3$`Model 2;HR (95% CI)`), parse_ci(table3$`Model 3;HR (95% CI)`))

names(table3) <- make.unique(names(table3))
names(table3)

table3$`Model1` <- paste(rep(" ", 22), collapse = " ")
table3$`Model2` <- paste(rep(" ", 22), collapse = " ")
table3$`Model3` <- paste(rep(" ", 22), collapse = " ")

table3 <- table3 %>%
  mutate(
    HR    = as.numeric(HR),
    lower = as.numeric(lower),
    upper = as.numeric(upper),
    HR.1    = as.numeric(HR.1),
    lower.1 = as.numeric(lower.1),
    upper.1 = as.numeric(upper.1),
    HR.2    = as.numeric(HR.2),
    lower.2 = as.numeric(lower.2),
    upper.2 = as.numeric(upper.2))

library(knitr)
library(forestploter)
library(grid)
# Forest plot
plot3 <- forest(
  table3[, c(7, 8, 9, 10, 22, 11, 23, 12, 24 )],  # Select relevant columns for the plot
  est = list(table3$HR, table3$HR.1, table3$HR.2),  # HR values for Model 1, Model 2, and Model 3
  lower = list(table3$lower, table3$lower.1, table3$lower.2),  # Lower bounds for the confidence intervals
  upper = list(table3$upper, table3$upper.1, table3$upper.2),
  ci_column = c(5, 7, 9),  # Positions for the three models
  ref.line = 1  # Reference line at 1
)

# Customize the plot appearance
tm <- forest_theme(
  base_size = 10,  # Text size
  ci_pch = 15,  # Shape of CI points
  ci_col = "#762a83",  # CI color
  ci_fill = "blue",  # CI fill color
  ci_alpha = 0.8,  # Transparency of CI
  ci_lty = 1,  # Line type for CI
  ci_lwd = 1.5,  # Line width for CI
  ci_Theight = 0.2,  # Height of CI lines
  refline_gp = gpar(col = "grey20", lwd = 1, lty = "dashed")  # Graphical parameters for reference line
)


# Apply theme to the plot and set axis limits
plot3 <- forest(
  table3[, c(7, 8, 9, 10, 22, 11, 23, 12, 24 )],  # Select relevant columns for the plot
  est = list(table3$HR, table3$HR.1, table3$HR.2),  # HR values for Model 1, Model 2, and Model 3
  lower = list(table3$lower, table3$lower.1, table3$lower.2),  # Lower bounds for the confidence intervals
  upper = list(table3$upper, table3$upper.1, table3$upper.2),
  ci_column = c(5, 7, 9),  # Positions for the three models
  ref_line = 1,  # Reference line at 1
  xlim = c(0.50, 1.50),  # X-axis limits
  ticks_at = c(0.55, 0.70, 0.85, 1, 1.15, 1.30, 1.45),  # Tick marks on X-axis
  theme = tm  # Apply the theme
)


plot3

ggsave(filename = "figure2.tiff",
       plot = plot3,
       dpi = 900,
       width = 15,
       height = 9)















# Load the data
table3 <- read.csv("diet quality output/table3.csv")  # Replace with your correct file name
table3$Person.years <- round(table3$Person.years, 0)
table3$Person.years <- ifelse(is.na(table3$Person.years), "", table3$Person.years)

# Prepare three empty columns for the plot (Model1, Model2, and Model3)
table3 <- table3 %>%
  mutate( #'Flavonoid subclass (mg/d)' = Flavonoid.subclass..mg.d.,
    'Flavone food' = Food,
         'Cases/Total (Incidence %)' = Case.total..incidence...,
         'Person years' = Person.years,
    `Model 1;HR (95% CI)` = Model.1..HR..95..CI.,
    `Model 2;HR (95% CI)` = Model.2..HR..95..CI.,
    `Model 3;HR (95% CI)` = Model.3..HR..95..CI.)
# Modify the `p value` column


parse_ci <- function(ci_vec) {
  strcapture(
    pattern = "^\\s*([0-9.+-eE]+)\\s*\\(\\s*([0-9.+-eE]+)\\s*-\\s*([0-9.+-eE]+)\\s*\\)\\s*$",
    x = ci_vec,
    proto = list(HR = double(), lower = double(), upper = double())
  )
}

table3 <- cbind(table3, parse_ci(table3$`Model 1;HR (95% CI)`), parse_ci(table3$`Model 2;HR (95% CI)`), parse_ci(table3$`Model 3;HR (95% CI)`))

names(table3) <- make.unique(names(table3))
names(table3)

table3$`Model1` <- paste(rep(" ", 22), collapse = " ")
table3$`Model2` <- paste(rep(" ", 22), collapse = " ")
table3$`Model3` <- paste(rep(" ", 22), collapse = " ")

table3 <- table3 %>%
  mutate(
    HR    = as.numeric(HR),
    lower = as.numeric(lower),
    upper = as.numeric(upper),
    HR.1    = as.numeric(HR.1),
    lower.1 = as.numeric(lower.1),
    upper.1 = as.numeric(upper.1),
    HR.2    = as.numeric(HR.2),
    lower.2 = as.numeric(lower.2),
    upper.2 = as.numeric(upper.2))

library(knitr)
library(forestploter)
library(grid)
# Forest plot
plot3 <- forest(
  table3[, c(7, 8, 9, 10, 22, 11, 23, 12, 24 )],  # Select relevant columns for the plot
  est = list(table3$HR, table3$HR.1, table3$HR.2),  # HR values for Model 1, Model 2, and Model 3
  lower = list(table3$lower, table3$lower.1, table3$lower.2),  # Lower bounds for the confidence intervals
  upper = list(table3$upper, table3$upper.1, table3$upper.2),
  ci_column = c(5, 7, 9),  # Positions for the three models
  ref.line = 1  # Reference line at 1
)

# Customize the plot appearance
tm <- forest_theme(
  base_size = 10,  # Text size
  ci_pch = 15,  # Shape of CI points
  ci_col = "#762a83",  # CI color
  ci_fill = "blue",  # CI fill color
  ci_alpha = 0.8,  # Transparency of CI
  ci_lty = 1,  # Line type for CI
  ci_lwd = 1.5,  # Line width for CI
  ci_Theight = 0.2,  # Height of CI lines
  refline_gp = gpar(col = "grey20", lwd = 1, lty = "dashed")  # Graphical parameters for reference line
)


# Apply theme to the plot and set axis limits
plot3 <- forest(
  table3[, c(7, 8, 9, 10, 22, 11, 23, 12, 24 )],  # Select relevant columns for the plot
  est = list(table3$HR, table3$HR.1, table3$HR.2),  # HR values for Model 1, Model 2, and Model 3
  lower = list(table3$lower, table3$lower.1, table3$lower.2),  # Lower bounds for the confidence intervals
  upper = list(table3$upper, table3$upper.1, table3$upper.2),
  ci_column = c(5, 7, 9),  # Positions for the three models
  ref_line = 1,  # Reference line at 1
  xlim = c(0.50, 1.50),  # X-axis limits
  ticks_at = c(0.55, 0.70, 0.85, 1, 1.15, 1.30, 1.45),  # Tick marks on X-axis
  theme = tm  # Apply the theme
)


plot3

ggsave(filename = "figure3.tiff",
       plot = plot3,
       dpi = 900,
       width = 15,
       height = 10)


#1500 900
```

# KM
```{r}
library(dplyr)
library(survival)
library(survminer)
library(ggplot2)
library(cowplot)

# ============================================================
# 1. Create correct flavone factor (quartile 1–4)
# ============================================================
dietaryscorewithquartile$flavone <- factor(
  dietaryscorewithquartile$flavones_ord4,
  levels = c(1, 2, 3, 4),
  labels = c("Q1", "Q2", "Q3", "Q4")
)

# ============================================================
# 2. Fit Cox model (x=TRUE & model=TRUE required)
# ============================================================
model.uni <- coxph(
  Survival.Obj ~ flavone + Sex + Age.group + MET.Quintiles +
    Smoking.status...Instance.0 + alcohol.category + multimorbidity +
    IMD.quartile + Qualification + Energy + Free.sugar + meat +
    wholegrain + BMI.Category,
  data = dietaryscorewithquartile,
  ties = "efron",
  x = TRUE, model = TRUE
)

# ============================================================
# 3. Mode function for factor covariates
# ============================================================
mode_ <- function(x) {
  names(which.max(table(x)))
}

# ============================================================
# 4. Build reference covariate row
# ============================================================
ref_row <- data.frame(
  Sex                                 = mode_(dietaryscorewithquartile$Sex),
  Age.group                           = mode_(dietaryscorewithquartile$Age.group),
  MET.Quintiles                       = mode_(dietaryscorewithquartile$MET.Quintiles),
  Smoking.status...Instance.0         = mode_(dietaryscorewithquartile$Smoking.status...Instance.0),
  alcohol.category                    = mode_(dietaryscorewithquartile$alcohol.category),
  multimorbidity                      = mode_(dietaryscorewithquartile$multimorbidity),
  IMD.quartile                        = mode_(dietaryscorewithquartile$IMD.quartile),
  Qualification                       = mode_(dietaryscorewithquartile$Qualification),

  # For numeric covariates, use median (mode makes no sense)
  Energy                              = median(dietaryscorewithquartile$Energy, na.rm = TRUE),
  Free.sugar                          = median(dietaryscorewithquartile$Free.sugar, na.rm = TRUE),
  meat                                = median(dietaryscorewithquartile$meat, na.rm = TRUE),
  wholegrain                          = median(dietaryscorewithquartile$wholegrain, na.rm = TRUE),

  BMI.Category                        = mode_(dietaryscorewithquartile$BMI.Category)
)

# ============================================================
# 5. Create 4 copies (one for each flavone quartile)
# ============================================================
# replicate returns a list of data frames
nd_list <- replicate(4, ref_row, simplify = FALSE)

# row-bind into a clean data.frame
newdata <- do.call(rbind, nd_list)

# add flavone column
newdata$flavone <- factor(c("Q1","Q2","Q3","Q4"),
                          levels = c("Q1","Q2","Q3","Q4"))

# ----------------------------
# 6. Match factor levels with model
# ----------------------------
for (v in names(model.uni$xlevels)) {
  if (v %in% names(newdata)) {
    newdata[[v]] <- factor(newdata[[v]],
                           levels = model.uni$xlevels[[v]])
  }
}

print(newdata)   # now shows a true data.frame

# ----------------------------
# 7. Predict adjusted survival
# ----------------------------
max_time <- max(dietaryscorewithquartile$survival.time, na.rm=TRUE)

sf_adj <- survfit(
  model.uni,
  newdata = newdata,
  se.fit = TRUE,
  conf.type = "log",
  # 指定真实的时间序列
  time = seq(0, max_time, by = 0.1)
)
# Inspect survival object
print(sf_adj)


# Plot adjusted curves with CI ribbons
p_adj <- ggsurvplot(
  sf_adj,
  data = newdata,
  conf.int = TRUE,
  #legend.title = "flavone",
  #legend = "none",
  palette = "Dark2",
  ggtheme = theme_classic(base_size = 12),
  xlab = "Time (years)", 
  ylab = "Survival probability",
  ylim = c(0.976, 1.00)      # ← 调整纵轴范围（建议 0.9~1）
)

p_adj$plot <- p_adj$plot + 
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 11),
    legend.text  = element_text(size = 10)
  )

p_adj$plot <- p_adj$plot + labs(title = "C. High genetic risk")

# KM only for the risk table
fit_km <- survfit(Survival.Obj ~ flavone, data = dietaryscorewithquartile)
km_plot <- ggsurvplot(
  fit_km, data = dietaryscorewithquartile,
  risk.table = TRUE,
  risk.table.type = "nrisk_cumevents",
  risk.table.title = "Participants at risk",
  risk.table.height = 0.30,
  risk.table.fontsize = 3.6,
  risk.table.y.text = TRUE,
  risk.table.y.text.col = FALSE,
  break.time.by = 2.5,
  conf.int = FALSE,
  legend = "none",
  xlab = "Time (years)", ylab = NULL,
  ggtheme = theme_classic(base_size = 12),
  tables.theme = theme_cleantable()
)

final_plot3 <- plot_grid(p_adj$plot, km_plot$table, ncol = 1, rel_heights = c(0.72, 0.28))
print(final_plot3)



library(cowplot)

combined_plot <- plot_grid(
  final_plot1, final_plot2, final_plot3,
  nrow = 3,           # 两列
  rel_widths = c(3,3,3) # 比例可调
)

combined_plot


# 1000 800

```



# model 1
```{r}
# Initialize an empty data frame to store the results
dietary.score.results <- data.frame()

# Define the survival object
polyphenolwithhealth$Survival.Obj <- with(polyphenolwithhealth, Surv(survival.time, event))

# Loop through columns 3 to 89 (assumed dietary scores)
for (i in c(3:8)) {
  
  # Run univariate Cox model
  model.uni <- coxph(Survival.Obj ~ polyphenolwithhealth[,i] + Sex + Age.group + Ethnic.background + multimorbidity + IMD.quartile + Qualification, data = polyphenolwithhealth)
  
  # Extract variable name
  x <- names(polyphenolwithhealth)[i]
  y <- "Survival.Obj"
  
  # Extract model statistics
  coefficients <- coef(model.uni)[1]
  se <- summary(model.uni)$coefficients[1, "se(coef)"]
  z.value <- summary(model.uni)$coefficients[1, "z"]
  p.value <- summary(model.uni)$coefficients[1, "Pr(>|z|)"]
  ci.lower <- exp(confint(model.uni)[1, 1])
  ci.upper <- exp(confint(model.uni)[1, 2])
  hr <- exp(coefficients)
  
  # Format HR and CI
  formatted.hr <- sprintf("%.3f", hr)
  formatted.ci.lower <- sprintf("%.3f", ci.lower)
  formatted.ci.upper <- sprintf("%.3f", ci.upper)
  CI <- paste0(formatted.hr, " (", formatted.ci.lower, "-", formatted.ci.upper, ")")
  
  # Number of non-missing observations
  n <- sum(!is.na(polyphenolwithhealth[, i]))
  
  # Calculate person-years
  person.years <- sum(polyphenolwithhealth$survival.time[!is.na(polyphenolwithhealth[, i])], na.rm = TRUE)
  
  # Calculate number of cases and incidence
  cases <- sum(polyphenolwithhealth$group == "psoriasis" & !is.na(polyphenolwithhealth[, i]))
  incidence <- cases / n * 100
  cases.total <- paste0(cases, "/", n, " (", sprintf("%.3f", incidence), ")")

  # Store the results
  results <- data.frame(
    Nutrient = x,
    case = cases,
    total = n,
    incidence = incidence,
    Case.Total = cases.total,
    Person.Years = round(person.years, 1),
    HR.95.CI = CI,
    P.value = signif(p.value, 3)
  )
  
  # Append to the main results data frame
  dietary.score.results <- rbind(dietary.score.results, results)
}

# Print the results
print(dietary.score.results)

# Save the results to a CSV file
write.csv(dietary.score.results, "diet quality output/flavonoid dose model 2.2.csv")
```

## add for quartiles
```{r}
dietaryscorewithquartile <- polyphenolwithhealth %>%
  mutate(across(3:8, ~ cut(., breaks = quantile(., probs = 0:4 / 4, na.rm = TRUE), 
                             include.lowest = TRUE, labels = FALSE), 
                .names = "quartile_{col}"))

dietaryscorewithquartile <- dietaryscorewithquartile[, c(1:2, 72:77, 9:71)]


# Initialize an empty data frame to store the results
dietary.score.results <- data.frame()

# Define the survival object
dietaryscorewithquartile$Survival.Obj <- with(dietaryscorewithquartile, Surv(survival.time, event))

# Loop through dietary score columns (quartile variables)
for (i in c(72:79)) {
  
  # Run Cox model with quartiles treated as factors (Q1 as reference)
  model.uni <- coxph(Survival.Obj ~ factor(dietaryscorewithquartile[, i]) + Sex + Age.group + multimorbidity + Qualification, data = dietaryscorewithquartile)
  
  # Extract variable name
  nutrient <- names(dietaryscorewithquartile)[i]
  response <- "Survival.Obj"
  
  # Loop through Q2–Q4 (compared to Q1)
  for (j in 2:4) {
    
    # Extract statistics
    coef_j <- coef(model.uni)[j - 1]
    se_j <- summary(model.uni)$coefficients[j - 1, "se(coef)"]
    z_j <- summary(model.uni)$coefficients[j - 1, "z"]
    p_j <- summary(model.uni)$coefficients[j - 1, "Pr(>|z|)"]
    ci_lower <- exp(confint(model.uni)[j - 1, 1])
    ci_upper <- exp(confint(model.uni)[j - 1, 2])
    hr <- exp(coef_j)
    
    # Format HR and CI
    formatted.hr <- sprintf("%.2f", hr)
    formatted.ci.lower <- sprintf("%.2f", ci_lower)
    formatted.ci.upper <- sprintf("%.2f", ci_upper)
    hr_ci <- paste0(formatted.hr, " (", formatted.ci.lower, "-", formatted.ci.upper, ")")
    
    # Subset data for current quartile level
    quartile_data <- dietaryscorewithquartile %>%
      filter(as.integer(dietaryscorewithquartile[, i]) == j)
    
    # Case count and person-years
    n <- sum(!is.na(quartile_data[, i]))
    person.years <- sum(quartile_data$survival.time, na.rm = TRUE)
    cases <- sum(quartile_data$group == "psoriasis")
    incidence <- cases / n * 100
    cases.total <- paste0(cases, "/", n, " (", sprintf("%.3f", incidence), ")")
    
    # Store the result row
    result_row <- data.frame(
      Nutrient = nutrient,
      Quartile = paste0("Q", j),
      case = cases,
      total = n,
      incidence = incidence,
      Case.total = cases.total,
      person.years = person.years,
      HR.95.CI = hr_ci,
      P.value = signif(p_j, 3)
    )
    
    # Append to results
    dietary.score.results <- rbind(dietary.score.results, result_row)
  }
}

# Print results
print(dietary.score.results)

# Save the results to a CSV file
write.csv(dietary.score.results, "diet quality output/flavonoid quartile model 2.2.csv", row.names = FALSE)
```

## add for trend
```{r}
# Initialize an empty data frame to store the results
dietary.score.results <- data.frame()

# Define the survival object
dietaryscorewithquartile$Survival.Obj <- with(dietaryscorewithquartile, Surv(survival.time, event))

# Loop through columns 3 to 89 (assumed dietary scores)
for (i in c(72:79)) {
  
  # Run univariate Cox model
  model.uni <- coxph(Survival.Obj ~ as.numeric(dietaryscorewithquartile[, i]) + Sex + Age.group + multimorbidity + IMD.quartile + Qualification, data = dietaryscorewithquartile)
  
  # Extract variable name
  x <- names(dietaryscorewithquartile)[i]
  y <- "Survival.Obj"
  
  # Extract model statistics
  coefficients <- coef(model.uni)[1]
  se <- summary(model.uni)$coefficients[1, "se(coef)"]
  z.value <- summary(model.uni)$coefficients[1, "z"]
  p.value <- summary(model.uni)$coefficients[1, "Pr(>|z|)"]
  ci.lower <- exp(confint(model.uni)[1, 1])
  ci.upper <- exp(confint(model.uni)[1, 2])
  hr <- exp(coefficients)
  
  # Format HR and CI
  formatted.hr <- sprintf("%.3f", hr)
  formatted.ci.lower <- sprintf("%.3f", ci.lower)
  formatted.ci.upper <- sprintf("%.3f", ci.upper)
  CI <- paste0(formatted.hr, " (", formatted.ci.lower, "-", formatted.ci.upper, ")")
  
  # Number of non-missing observations
  n <- sum(!is.na(dietaryscorewithquartile[, i]))
  
  # Calculate person-years
  person.years <- sum(dietaryscorewithquartile$survival.time[!is.na(dietaryscorewithquartile[, i])], na.rm = TRUE)
  
  # Calculate number of cases and incidence
  cases <- sum(dietaryscorewithquartile$group == "psoriasis" & !is.na(dietaryscorewithquartile[, i]))
  incidence <- cases / n * 100
  cases.total <- paste0(cases, "/", n, " (", sprintf("%.3f", incidence), ")")

  # Store the results
  results <- data.frame(
    Nutrient = x,
    Case.Total = cases.total,
    case = cases,
    total = n,
    incidence = incidence,
    Person.Years = round(person.years, 1),
    HR.95.CI = CI,
    P.value = signif(p.value, 3)
  )
  
  # Append to the main results data frame
  dietary.score.results <- rbind(dietary.score.results, results)
}

# Print the results
print(dietary.score.results)

# Save the results to a CSV file
write.csv(dietary.score.results, "diet quality output/flavonoid trend model 2.2.csv", row.names = FALSE)
```


# model 2
```{r}
# Initialize an empty data frame to store the results
dietary.score.results <- data.frame()

# Define the survival object
polyphenolwithhealth$Survival.Obj <- with(polyphenolwithhealth, Surv(survival.time, event))

# Loop through columns 3 to 89 (assumed dietary scores)
for (i in 3:8) {
  
  # Run univariate Cox model
  model.uni <- coxph(Survival.Obj ~ polyphenolwithhealth[,i] + Sex + Age.group + Ethnic.background + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Qualification, data = polyphenolwithhealth)
  
  # Extract variable name
  x <- names(polyphenolwithhealth)[i]
  y <- "Survival.Obj"
  
  # Extract model statistics
  coefficients <- coef(model.uni)[1]
  se <- summary(model.uni)$coefficients[1, "se(coef)"]
  z.value <- summary(model.uni)$coefficients[1, "z"]
  p.value <- summary(model.uni)$coefficients[1, "Pr(>|z|)"]
  ci.lower <- exp(confint(model.uni)[1, 1])
  ci.upper <- exp(confint(model.uni)[1, 2])
  hr <- exp(coefficients)
  
  # Format HR and CI
  formatted.hr <- sprintf("%.3f", hr)
  formatted.ci.lower <- sprintf("%.3f", ci.lower)
  formatted.ci.upper <- sprintf("%.3f", ci.upper)
  CI <- paste0(formatted.hr, " (", formatted.ci.lower, "-", formatted.ci.upper, ")")
  
  # Number of non-missing observations
  n <- sum(!is.na(polyphenolwithhealth[, i]))
  
  # Calculate person-years
  person.years <- sum(polyphenolwithhealth$survival.time[!is.na(polyphenolwithhealth[, i])], na.rm = TRUE)
  
  # Calculate number of cases and incidence
  cases <- sum(polyphenolwithhealth$group == "psoriasis" & !is.na(polyphenolwithhealth[, i]))
  incidence <- cases / n * 100
  cases.total <- paste0(cases, "/", n, " (", sprintf("%.3f", incidence), ")")

  # Store the results
  results <- data.frame(
    Nutrient = x,
    case = cases,
    total = n,
    incidence = incidence,
    Case.Total = cases.total,
    Person.Years = round(person.years, 1),
    HR.95.CI = CI,
    P.value = signif(p.value, 3)
  )
  
  # Append to the main results data frame
  dietary.score.results <- rbind(dietary.score.results, results)
}

# Print the results
print(dietary.score.results)

# Save the results to a CSV file
write.csv(dietary.score.results, "diet quality output/flavonoid dose model 3.2.csv")
```

## add for quartiles
```{r}
dietaryscorewithquartile <- polyphenolwithhealth %>%
  mutate(across(3:8, ~ cut(., breaks = quantile(., probs = 0:4 / 4, na.rm = TRUE), 
                             include.lowest = TRUE, labels = FALSE), 
                .names = "quartile_{col}"))

dietaryscorewithquartile <- dietaryscorewithquartile[, c(1:2, 72:77, 9:71)]


# Initialize an empty data frame to store the results
dietary.score.results <- data.frame()

# Define the survival object
dietaryscorewithquartile$Survival.Obj <- with(dietaryscorewithquartile, Surv(survival.time, event))

# Loop through dietary score columns (quartile variables)
for (i in c(72:79)) {
  
  # Run Cox model with quartiles treated as factors (Q1 as reference)
  model.uni <- coxph(Survival.Obj ~ factor(dietaryscorewithquartile[, i]) + Sex + Age.group + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Qualification, data = dietaryscorewithquartile)
  
  # Extract variable name
  nutrient <- names(dietaryscorewithquartile)[i]
  response <- "Survival.Obj"
  
  # Loop through Q2–Q4 (compared to Q1)
  for (j in 2:4) {
    
    # Extract statistics
    coef_j <- coef(model.uni)[j - 1]
    se_j <- summary(model.uni)$coefficients[j - 1, "se(coef)"]
    z_j <- summary(model.uni)$coefficients[j - 1, "z"]
    p_j <- summary(model.uni)$coefficients[j - 1, "Pr(>|z|)"]
    ci_lower <- exp(confint(model.uni)[j - 1, 1])
    ci_upper <- exp(confint(model.uni)[j - 1, 2])
    hr <- exp(coef_j)
    
    # Format HR and CI
    formatted.hr <- sprintf("%.2f", hr)
    formatted.ci.lower <- sprintf("%.2f", ci_lower)
    formatted.ci.upper <- sprintf("%.2f", ci_upper)
    hr_ci <- paste0(formatted.hr, " (", formatted.ci.lower, "-", formatted.ci.upper, ")")
    
    # Subset data for current quartile level
    quartile_data <- dietaryscorewithquartile %>%
      filter(as.integer(dietaryscorewithquartile[, i]) == j)
    
    # Case count and person-years
    n <- sum(!is.na(quartile_data[, i]))
    person.years <- sum(quartile_data$survival.time, na.rm = TRUE)
    cases <- sum(quartile_data$group == "psoriasis")
    incidence <- cases / n * 100
    cases.total <- paste0(cases, "/", n, " (", sprintf("%.2f", incidence), ")")
    
    # Store the result row
    result_row <- data.frame(
      Nutrient = nutrient,
      Quartile = paste0("Q", j),
      case = cases,
      total = n,
      incidence = incidence,
      Case.total = cases.total,
      person.years = person.years,
      HR.95.CI = hr_ci,
      P.value = signif(p_j, 3)
    )
    
    # Append to results
    dietary.score.results <- rbind(dietary.score.results, result_row)
  }
}

# Print results
print(dietary.score.results)

# Save the results to a CSV file
write.csv(dietary.score.results, "diet quality output/flavonoid quartile model 3.2.csv", row.names = FALSE)
```

## add for trend
```{r}
# Initialize an empty data frame to store the results
dietary.score.results <- data.frame()

# Define the survival object
dietaryscorewithquartile$Survival.Obj <- with(dietaryscorewithquartile, Surv(survival.time, event))

# Loop through columns 3 to 89 (assumed dietary scores)
for (i in c(72:79)) {
  
  # Run univariate Cox model
  model.uni <- coxph(Survival.Obj ~ as.numeric(dietaryscorewithquartile[, i]) + Sex + Age.group + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Qualification, data = dietaryscorewithquartile)
  
  # Extract variable name
  x <- names(dietaryscorewithquartile)[i]
  y <- "Survival.Obj"
  
  # Extract model statistics
  coefficients <- coef(model.uni)[1]
  se <- summary(model.uni)$coefficients[1, "se(coef)"]
  z.value <- summary(model.uni)$coefficients[1, "z"]
  p.value <- summary(model.uni)$coefficients[1, "Pr(>|z|)"]
  ci.lower <- exp(confint(model.uni)[1, 1])
  ci.upper <- exp(confint(model.uni)[1, 2])
  hr <- exp(coefficients)
  
  # Format HR and CI
  formatted.hr <- sprintf("%.3f", hr)
  formatted.ci.lower <- sprintf("%.3f", ci.lower)
  formatted.ci.upper <- sprintf("%.3f", ci.upper)
  CI <- paste0(formatted.hr, " (", formatted.ci.lower, "-", formatted.ci.upper, ")")
  
  # Number of non-missing observations
  n <- sum(!is.na(dietaryscorewithquartile[, i]))
  
  # Calculate person-years
  person.years <- sum(dietaryscorewithquartile$survival.time[!is.na(dietaryscorewithquartile[, i])], na.rm = TRUE)
  
  # Calculate number of cases and incidence
  cases <- sum(dietaryscorewithquartile$group == "psoriasis" & !is.na(dietaryscorewithquartile[, i]))
  incidence <- cases / n * 100
  cases.total <- paste0(cases, "/", n, " (", sprintf("%.3f", incidence), ")")

  # Store the results
  results <- data.frame(
    Nutrient = x,
    Case.Total = cases.total,
    case = cases,
    total = n,
    incidence = incidence,
    Person.Years = round(person.years, 1),
    HR.95.CI = CI,
    P.value = signif(p.value, 3)
  )
  
  # Append to the main results data frame
  dietary.score.results <- rbind(dietary.score.results, results)
}

# Print the results
print(dietary.score.results)

# Save the results to a CSV file
write.csv(dietary.score.results, "diet quality output/flavonoid trend model 3.2.csv", row.names = FALSE)
```

# model 3
```{r}
# Initialize an empty data frame to store the results
dietary.score.results <- data.frame()

# Define the survival object
polyphenolwithhealth$Survival.Obj <- with(polyphenolwithhealth, Surv(survival.time, event))

# Loop through columns 3 to 89 (assumed dietary scores)
for (i in c(3:8)) {

  # Run sunivariate Cox model
  model.uni <- coxph(Survival.Obj ~ polyphenolwithhealth[,i] + Sex + Age.group + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Qualification + Energy + Free.sugar + meat + wholegrain + BMI.Category, data = polyphenolwithhealth)
  
  # Extract variable name
  x <- names(polyphenolwithhealth)[i]
  y <- "Survival.Obj"
  
  # Extract model statistics
  coefficients <- coef(model.uni)[1]
  se <- summary(model.uni)$coefficients[1, "se(coef)"]
  z.value <- summary(model.uni)$coefficients[1, "z"]
  p.value <- summary(model.uni)$coefficients[1, "Pr(>|z|)"]
  ci.lower <- exp(confint(model.uni)[1, 1])
  ci.upper <- exp(confint(model.uni)[1, 2])
  hr <- exp(coefficients)
  
  # Format HR and CI
  formatted.hr <- sprintf("%.3f", hr)
  formatted.ci.lower <- sprintf("%.3f", ci.lower)
  formatted.ci.upper <- sprintf("%.3f", ci.upper)
  CI <- paste0(formatted.hr, " (", formatted.ci.lower, "-", formatted.ci.upper, ")")
  
  # Number of non-missing observations
  n <- sum(!is.na(polyphenolwithhealth[, i]))
  
  # Calculate person-years
  person.years <- sum(polyphenolwithhealth$survival.time[!is.na(polyphenolwithhealth[, i])], na.rm = TRUE)
  
  # Calculate number of cases and incidence
  cases <- sum(polyphenolwithhealth$group == "psoriasis" & !is.na(polyphenolwithhealth[, i]))
  incidence <- cases / n * 100
  cases.total <- paste0(cases, "/", n, " (", sprintf("%.3f", incidence), ")")

  # Store the results
  results <- data.frame(
    Nutrient = x,
    case = cases,
    total = n,
    incidence = incidence,
    Case.Total = cases.total,
    Person.Years = round(person.years, 1),
    HR.95.CI = CI,
    P.value = signif(p.value, 3)
  )
  
  # Append to the main results data frame
  dietary.score.results <- rbind(dietary.score.results, results)
}

# Print the results
print(dietary.score.results)

# Save the results to a CSV file
write.csv(dietary.score.results, "diet quality output/flavonoid dose model PRS.csv")
```
vars <- names(polyphenolwithhealth)[3:12]

quartile_summary <- list()

for (v in vars) {
  q <- quantile(polyphenolwithhealth[[v]], probs = c(0, 0.25, 0.5, 0.75, 1), na.rm = TRUE)
  m <- mean(polyphenolwithhealth[[v]], na.rm = TRUE)
  s <- sd(polyphenolwithhealth[[v]], na.rm = TRUE)
  
  quartile_summary[[v]] <- data.frame(
    Variable = v,
    Q1_range = paste0(round(q[1], 2), " - ", round(q[2], 2)),
    Q2_range = paste0(round(q[2], 2), " - ", round(q[3], 2)),
    Q3_range = paste0(round(q[3], 2), " - ", round(q[4], 2)),
    Q4_range = paste0(round(q[4], 2), " - ", round(q[5], 2)),
    Median = round(q[3], 2),
    Mean = round(m, 2),
    SD = round(s, 2)
  )
}

quartile_table <- do.call(rbind, quartile_summary)
rownames(quartile_table) <- NULL

print(quartile_table)
## add for quartiles
```{r}


dietaryscorewithquartile <- polyphenolwithhealth %>%
  mutate(across(3:8, ~ cut(., breaks = quantile(., probs = 0:4 / 4, na.rm = TRUE), 
                             include.lowest = TRUE, labels = FALSE), 
                .names = "quartile_{col}"))

dietaryscorewithquartile <- dietaryscorewithquartile[, c(1:2, 72:77, 9:71)]

# Initialize an empty data frame to store the results
dietary.score.results <- data.frame()

# Define the survival object
dietaryscorewithquartile$Survival.Obj <- with(dietaryscorewithquartile, Surv(survival.time, event))

# Loop through dietary score columns (quartile variables)
for (i in c(72:79)) {
  
  # Run Cox model with quartiles treated as factors (Q1 as reference)
  model.uni <- coxph(Survival.Obj ~ factor(dietaryscorewithquartile[, i]) + Sex + Age.group + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Qualification + Energy + Free.sugar + meat + wholegrain +BMI.Category, data = dietaryscorewithquartile)
  
  # Extract variable name
  nutrient <- names(dietaryscorewithquartile)[i]
  response <- "Survival.Obj"
  
  # Loop through Q2–Q4 (compared to Q1)
  for (j in 2:4) {
    
    # Extract statistics
    coef_j <- coef(model.uni)[j - 1]
    se_j <- summary(model.uni)$coefficients[j - 1, "se(coef)"]
    z_j <- summary(model.uni)$coefficients[j - 1, "z"]
    p_j <- summary(model.uni)$coefficients[j - 1, "Pr(>|z|)"]
    ci_lower <- exp(confint(model.uni)[j - 1, 1])
    ci_upper <- exp(confint(model.uni)[j - 1, 2])
    hr <- exp(coef_j)
    
    # Format HR and CI
    formatted.hr <- sprintf("%.2f", hr)
    formatted.ci.lower <- sprintf("%.2f", ci_lower)
    formatted.ci.upper <- sprintf("%.2f", ci_upper)
    hr_ci <- paste0(formatted.hr, " (", formatted.ci.lower, "-", formatted.ci.upper, ")")
    
    # Subset data for current quartile level
    quartile_data <- dietaryscorewithquartile %>%
      filter(as.integer(dietaryscorewithquartile[, i]) == j)
    
    # Case count and person-years
    n <- sum(!is.na(quartile_data[, i]))
    person.years <- sum(quartile_data$survival.time, na.rm = TRUE)
    cases <- sum(quartile_data$group == "psoriasis")
    incidence <- cases / n * 100
    cases.total <- paste0(cases, "/", n, " (", sprintf("%.2f", incidence), ")")
    
    # Store the result row
    result_row <- data.frame(
      Nutrient = nutrient,
      Quartile = paste0("Q", j),
      case = cases,
      total = n,
      incidence = incidence,
      Case.total = cases.total,
      person.years = person.years,
      HR.95.CI = hr_ci,
      P.value = signif(p_j, 3)
    )
    
    # Append to results
    dietary.score.results <- rbind(dietary.score.results, result_row)
  }
}

# Print results
print(dietary.score.results)

# Save the results to a CSV file
write.csv(dietary.score.results, "diet quality output/flavonoid quartile model PRS.csv", row.names = FALSE)
```


## add for trend
```{r}
# Initialize an empty data frame to store the results
dietary.score.results <- data.frame()

# Define the survival object
dietaryscorewithquartile$Survival.Obj <- with(dietaryscorewithquartile, Surv(survival.time, event))

# Loop through columns 3 to 89 (assumed dietary scores)
for (i in c(72:79)) {
  
  # Run univariate Cox model
  model.uni <- coxph(Survival.Obj ~ as.numeric(dietaryscorewithquartile[, i]) + Sex + Age.group + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Qualification + Energy + Free.sugar + meat + wholegrain + BMI.Category, data = dietaryscorewithquartile)
  
  # Extract variable name
  x <- names(dietaryscorewithquartile)[i]
  y <- "Survival.Obj"
  
  # Extract model statistics
  coefficients <- coef(model.uni)[1]
  se <- summary(model.uni)$coefficients[1, "se(coef)"]
  z.value <- summary(model.uni)$coefficients[1, "z"]
  p.value <- summary(model.uni)$coefficients[1, "Pr(>|z|)"]
  ci.lower <- exp(confint(model.uni)[1, 1])
  ci.upper <- exp(confint(model.uni)[1, 2])
  hr <- exp(coefficients)
  
  # Format HR and CI
  formatted.hr <- sprintf("%.3f", hr)
  formatted.ci.lower <- sprintf("%.3f", ci.lower)
  formatted.ci.upper <- sprintf("%.3f", ci.upper)
  CI <- paste0(formatted.hr, " (", formatted.ci.lower, "-", formatted.ci.upper, ")")
  
  # Number of non-missing observations
  n <- sum(!is.na(dietaryscorewithquartile[, i]))
  
  # Calculate person-years
  person.years <- sum(dietaryscorewithquartile$survival.time[!is.na(dietaryscorewithquartile[, i])], na.rm = TRUE)
  
  # Calculate number of cases and incidence
  cases <- sum(dietaryscorewithquartile$group == "psoriasis" & !is.na(dietaryscorewithquartile[, i]))
  incidence <- cases / n * 100
  cases.total <- paste0(cases, "/", n, " (", sprintf("%.3f", incidence), ")")

  # Store the results
  results <- data.frame(
    Nutrient = x,
    Case.Total = cases.total,
    case = cases,
    total = n,
    incidence = incidence,
    Person.Years = round(person.years, 1),
    HR.95.CI = CI,
    P.value = signif(p.value, 3)
  )
  
  # Append to the main results data frame
  dietary.score.results <- rbind(dietary.score.results, results)
}

# Print the results
print(dietary.score.results)

# Save the results to a CSV file
write.csv(dietary.score.results, "diet quality output/flavonoid trend model PRS.csv", row.names = FALSE)
```
# Table 1
```{r}
############## Show in table format ###################

# 定义需要用 Median (IQR) 显示的变量
nonnormal_vars <- c(
  "Free.sugar", "meat", "wholegrain",
  "anthocyanins", "flavanones", "flavonols",
  "flavones", "flavan.3.ols", "total.flavonoid"
)

# 创建 TableOne 对象
description.DQI <- CreateTableOne(
  data = polyphenolwithhealth,
  vars = c(
    "Ethnic.background", "Sex", "Age.at.recruitment",
    "Summed.MET.minutes.per.week.for.all.activity...Instance.0",
    "Smoking.status...Instance.0", "alcohol.category",
    "multimorbidity", "BMI", "PRS.tertile",
    "Free.sugar", "meat", "wholegrain",
    "anthocyanins", "flavanones", "flavonols",
    "flavones", "flavan.3.ols", "total.flavonoid",
    "Townsend.deprivation.index.at.recruitment",
    "Qualification", "Energy"
  ),
  
  factorVars = c(
    "Ethnic.background", "Sex", "Smoking.status...Instance.0",
    "Alcohol.drinker.status...Instance.0", "multimorbidity",
    "Qualification", "PRS.tertile"
  ),
  
  strata = "group"
)

# 打印 Table 1（Median (IQR) + 自动显示 P 值）
table1_output <- print(
  description.DQI,
  quote = FALSE,
  noSpaces = TRUE,
  nonnormal = nonnormal_vars,  # Median IQR
  test = TRUE                  # 自动给 P 值（Kruskal-Wallis）
)

# 显示结果
table1_output

# 导出 CSV
write.csv(table1_output, "Table1.csv")
```

# Interaction

```{r}
dietaryscorewithquartilek <- dietaryscorewithquartile %>% filter(PRS.tertile != "Missing" )
dietaryscorewithquartilek$PRS.tertile <- factor(droplevels(dietaryscorewithquartilek$PRS.tertile),
  levels = c("Low", "Medium", "High")
)

model.1 <- coxph(Survival.Obj ~ factor(flavones_ord4)* PRS.tertile + Sex + Age.group + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Qualification + Energy + Free.sugar + meat + wholegrain + BMI.Category + Genotype.measurement.batch + Genetic.principal.components...Array.1 + Genetic.principal.components...Array.2 + Genetic.principal.components...Array.3 + Genetic.principal.components...Array.4 + Genetic.principal.components...Array.5 + Genetic.principal.components...Array.6 + Genetic.principal.components...Array.7 + Genetic.principal.components...Array.8 + Genetic.principal.components...Array.9 + Genetic.principal.components...Array.10, data = dietaryscorewithquartile)

model.2 <- coxph(Survival.Obj ~ factor(flavones_ord4) + PRS.tertile + Sex + Age.group + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Qualification + Energy + Free.sugar + meat + wholegrain + BMI.Category + Genotype.measurement.batch + Genetic.principal.components...Array.1 + Genetic.principal.components...Array.2 + Genetic.principal.components...Array.3 + Genetic.principal.components...Array.4 + Genetic.principal.components...Array.5 + Genetic.principal.components...Array.6 + Genetic.principal.components...Array.7 + Genetic.principal.components...Array.8 + Genetic.principal.components...Array.9 + Genetic.principal.components...Array.10, data = dietaryscorewithquartile)

anova(model.2, model.1, test = "LRT")


# Print final table
print(interaction_results)

#0.5188
```


```{r}
# 创建生存对象
polyphenolwithhealth$Survival.Obj <- with(polyphenolwithhealth, Surv(survival.time, event))

# 拟合模型
model <- coxph(Survival.Obj ~ total.flavonoid * PRS.tertile + Sex + Age.group + Ethnic.background + MET.Quintiles + Smoking.status...Instance.0 + alcohol.category + multimorbidity + IMD.quartile + Energy + Free.sugar + meat + Sodium + AQI.Category + BMI.Category +  Genotype.measurement.batch + Genetic.principal.components...Array.1 + Genetic.principal.components...Array.2 + Genetic.principal.components...Array.3 + Genetic.principal.components...Array.4 + Genetic.principal.components...Array.5 + Genetic.principal.components...Array.6 + Genetic.principal.components...Array.7 + Genetic.principal.components...Array.8 + Genetic.principal.components...Array.9 + Genetic.principal.components...Array.10,
               data = polyphenolwithhealth)

# 提取第 1、56、57 项的 HR、CI 和 p 值
term_ids <- c(1, 158, 159)
coef_values <- coef(model)[term_ids]
ci_values <- confint(model)[term_ids, ]
hr_values <- exp(coef_values)
ci_exp <- exp(ci_values)
p_values <- summary(model)$coefficients[term_ids, "Pr(>|z|)"]

# 格式化输出
results <- data.frame(
  Term = c("total.flavonoid (Low PRS)", 
           "total.flavonoid:PRS.tertileMedium", 
           "total.flavonoid:PRS.tertileHigh"),
  HR = sprintf("%.3f", hr_values),
  CI = paste0("(", sprintf("%.3f", ci_exp[, 1]), "-", sprintf("%.3f", ci_exp[, 2]), ")"),
  P.value = signif(p_values, 3)
)

# 合并 HR 和 CI 成一列
results$HR.95.CI <- paste0(results$HR, " ", results$CI)
results <- results[, c("Term", "HR.95.CI", "P.value")]

# 输出
print(results)

# Save the results to a CSV file
write.csv(results, "coxph_interaction_with_incidence total.flavonoid.csv")
```